---
title: "Data analysis for 'Forecasting in the face of ecological complexity: number and strength of species interactions determine forecast skill in ecological communities'"

author: "Daugaard et al. (2022)"
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: true
    code_folding: hide
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note that several code chunks have the option "Eval=FALSE" which means that they are not run. This is because they take too long (the complete forecasting takes, days, up to weeks). Instead, the related results are loaded in later in the code (often in the subsequent code chunk). The data is saved in the folder "Data".


# Dependencies, functions and data

## Dependencies

```{r dependencies, include=FALSE}
library(readr)
library(tidyverse)
library(patchwork)
library(pracma)
library(data.table)
library(rEDM)
library(foreach)
library(parallel)
library(doParallel) 
library(kableExtra)
library(lme4)
library(lmerTest)
library(merTools)
library(ggfortify)
library(ggpubr)
library(ggtext)
library(RColorBrewer)
library(grid)
library(MARSS)
library(here)
library(elasticnet)
library(forecast)
library(caret)
library(tensorflow)
library(keras)
library(emmeans)
library(rsq)

options(dplyr.summarise.inform=F)
```

## Functions

```{r standard_theme, message=FALSE, warning=FALSE, }
# Standard theme function

standard_theme <- function(){ 
    theme_bw() %+replace%   
    theme(
      legend.position = "none",
      axis.title = element_text(size=13),
      axis.text = element_text(size=10),
      legend.text = element_text(size=11),
      strip.text = element_text(size=11, hjust = 0, vjust = 1),
      strip.background = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
    )
}

standard_theme2 <- function(){ 
    theme_bw() %+replace%   
    theme(
      legend.position = "none",
      axis.title = element_text(size=13),
      axis.text = element_text(size=10),
      legend.text = element_text(size=11),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
    )
}
```

```{r load_own_fcts, }
source(file = here("R/Functions/pe_code.R")) 
source(file = here("R/Functions/rq1_multiview_functions.R"))
source(file = here("R/Functions/rq2_smap_functions.R"))
source(file = here("R/Functions/other_functions.R"))
source(file = here("R/Functions/number_of_interaction_functions.R"))
```


## Data loading and data processing

```{r load_data_and_processing, message=FALSE, warning=FALSE, }
##############################################################
## Load data

dd <- read_csv(here("Data/Final_dataset_all_sources/complete_dataset.csv"), col_types = cols(X1 = col_skip())) 
taxa <- read_csv(here("Data/Final_dataset_all_sources/taxa_table.csv"))

dd <- dd[with(dd, order(variable, ID, day)),]

tag <- c("A","B","C","D","E","F","G","H","I","J","K","L","M","N")
label <- c(bacteria="Bacteria", chlamydomonas_reinhardtii="*Chlamydomonas reinhardtii*", 
					 colpidium_striatum="*Colpidium striatum*", dexiostomata_campylum="*Dexiostoma campylum*",
					 didinium_nasutum="*Didinium nasutum*", euglena_gracilis="*Euglena gracilis*", 
					 euplotes_daidaleos="*Euplotes daidaleos*", paramecium_caudatum="*Paramecium caudatum*",
					 rotifer_sp="*Rotifer* sp.", big_white_particle="Big and white flagellates",
					 small_white_particle="Small and white flagellates", 
					 green_white_particle="Green and white flagellates", temperature="Temperature",
					 dissolved_oxygen="Dissolved oxygen",spirostomum_sp="*Spirostomum* sp.")

##############################################################
## Interpolation

dd2 <- dd %>%
  dplyr::filter(variable %in% c("bacteria", "big_white_particle", "chlamydomonas_reinhardtii",
                         "colpidium_striatum", "dexiostomata_campylum", 
                         "didinium_nasutum", "dissolved_oxygen", "euglena_gracilis", 
                         "euplotes_daidaleos", "green_white_particle", 
                         "paramecium_caudatum", "rotifer_sp", "small_white_particle",
                         "spirostomum_sp", "temperature"))

nr.timepoints <- length(unique(dd2$day)) 

time.interp <- seq(min(dd2$day), max(dd2$day), length.out = nr.timepoints)

chi <- function(x,y){
  return(interp1(x, y, xi=time.interp, method="cubic")) 
}

dd2 <- setDT(dd2)[, list(day = time.interp,
                         response = chi(day, response),
                         date=date,
                         treat=treat,
                         treat2=treat2,
                         treat3=treat3,
                         incubator=incubator),
                  by = .(variable, ID)]

dd2$response <- ifelse(dd2$variable=="temperature" & dd2$treat=="const", 17.3, dd2$response)


##############################################################
## Coefficient of variation

targets <- c("bacteria","chlamydomonas_reinhardtii","colpidium_striatum",
             "dexiostomata_campylum","euglena_gracilis","euplotes_daidaleos",
             "paramecium_caudatum","rotifer_sp")

cv <- dd2 %>%
  dplyr::filter(variable %in% targets) %>%
  group_by(ID, variable) %>%
  summarize(cv = sd(response)/mean(response),
            sd = sd(response),
            mean = mean(response)) %>%
	rename(Target=variable)

##############################################################
## fourth root transformation
 
dd2$response <- (dd2$response)^(1/4)

##############################################################
## remove linear trend

dd2 <- setDT(dd2)[, list(day = day,
                         response = residuals(lm(response~day)),
                         date=date,
                         treat=treat,
                         treat2=treat2,
                         treat3=treat3,
                         incubator=incubator),
                  by = .(variable, ID)]

dd2 <- dd2 %>% na.omit()

##############################################################
## Standardization

dd2 <- dd2 %>%
  dplyr::filter(variable!="spirostomum_sp")%>%
  group_by(variable, ID, treat, treat2, treat3, incubator) %>%
  mutate(response = (response-mean(response, na.rm=T))/sd(response, na.rm = T))

dd2$response <-	ifelse(dd2$variable=="temperature" & dd2$treat=="const", 0, dd2$response)

##############################################################
## Calculation of permutation entropies

permutation_entropies <- dd2 %>% group_by(ID,variable,treat,treat2,treat3) %>%
  dplyr::filter(variable %in% targets) %>%
  summarize(PE = PE(x = response, weighted = T, word_length = 5, tau = 1,
                                tie_method = "noise", noise_amount = 10)) %>%
	rename(Target=variable)
 
##############################################################
## Wide format data
dd2_long <- dd2
dd2 <- dd2 %>%
  pivot_wider(names_from = variable,
              values_from = response)

rm(time.interp)
```

# Estimations and forecastings (main text)

## Species abudance forecasting

The following chunk is not run as it takes a long time to run (1-2 weeks). Instead the results are loaded in in the chunk afterwards.

```{r multiview_forecast_analysis, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
##############################################################
## Species forecasting 

# First some preparation:
ks <- unique(round(exp(seq(log(0.8),log(100.4),length.out = 33))))

possible_predictors <- c("bacteria","chlamydomonas_reinhardtii","colpidium_striatum",
                         "dexiostomata_campylum", "didinium_nasutum",
                         "euglena_gracilis","euplotes_daidaleos","paramecium_caudatum",
                         "rotifer_sp","big_white_particle","dissolved_oxygen",
                         "green_white_particle", "small_white_particle")
 
dd2 <- dd2 %>% ungroup()
set.seed(54)
which=c(1,2,3,4,6,8,10,13)
predictor_combinations <- predictor_combinator(possible_predictors, which=which)

ddrq1_list <- lapply(targets, function(target){
  df1 <- model_fitter_wrapper(whole.data = dd2, 
                              predictor_combinations =  predictor_combinations,
                              target = target,
                              num.clusters = detectCores() - 1, 
                              E = 3, max_lag = 3, k=ks)
})

ddrq1 <- do.call("rbind", ddrq1_list)

predictors <- c(possible_predictors,"temperature")
ddrq1$predictor_combination <- as.character(ddrq1$predictor_combination)
temp <- matrix(F, nrow = nrow(ddrq1), ncol = length(predictors))
colnames(temp) <- predictors
ddrq1 <- cbind(ddrq1,temp)

ddrq1 <- as.data.frame(t(apply(ddrq1, 1, function(row) { 
  str <- unlist(strsplit(row["predictor_combination"], " "))
  row[str] <- T
  row
})))

ddrq1$num_pred <- as.numeric(ddrq1$num_pred)
ddrq1$num_pred_without_temp <- as.numeric(ddrq1$num_pred_without_temp)
ddrq1$RMSE <- as.numeric(ddrq1$RMSE)
ddrq1$k <- as.numeric(ddrq1$k)
for(i in predictors){  ddrq1[,i] <- as.logical(ddrq1[,i])}

save(ddrq1, file = here("Data/Multiview_forecast_data/ddrq1_transf_resid_which_all.RData"))
```


```{r multiview_forecast_load, message=FALSE, warning=FALSE, cache=TRUE, }
ks <- unique(round(exp(seq(log(0.8),log(100.4),length.out = 33))))
load(here("Data/Multiview_forecast_data/ddrq1_transf_resid_which_all.RData"))  # done previously
ddrq1 <- ddrq1 %>% na.omit()
ddrq1_summarized <- ddrq1 %>%
  dplyr::group_by(Target, ID, num_pred, temperature_included, treat, treat2, treat3) %>%
  dplyr::summarise(median_rmse = median(RMSE),
                   mean_rmse = mean(RMSE),
                   min_rmse = min(RMSE))
```

### Number of models fitted

```{r model_table_calc, cache=TRUE, message=FALSE}
ks <- unique(round(exp(seq(log(0.8),log(100.4),length.out = 33))))
model.table <- data.frame(number_of_predictors=c(1,2,3,4,6,8,10,13))
model.table$choose_n_from_13 <- choose(13,model.table$number_of_predictors)
model.table$number_of_predictor_combos <- ifelse(model.table$choose_n_from_13>200,200,model.table$choose_n_from_13)
model.table$number_of_lagged_predictors_for_n_predictors <- choose(3*model.table$number_of_predictors,3)
model.table$number_of_different_k_values <- sapply(model.table$number_of_lagged_predictors_for_n_predictors, 
                                                   function(x){sum(ks<=x)})
model.table$number_of_predictor_combos_TIMES_number_of_different_k_values <- 
  model.table$number_of_predictor_combos*model.table$number_of_different_k_values
num_of_models <- sum(model.table$number_of_predictor_combos_TIMES_number_of_different_k_values)*8*18 
```



## Calculation of the number of interactions

The following code chunk is not run. Its results are loaded in in the chunk following it.

```{r determine_numb_interactions, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
##############################################################
## Number of interactions
interactors <- colnames(dd2[,-c(1:7)])
var_pairs <- expand.grid(target=targets, interactors=interactors)

dd2_dflist <- split(dd2, dd2$ID)

pairwise_ccm_df_list <- mclapply(dd2_dflist, function(df){
	dftemp <- df[,-c(1,3:7)]
	Best_E_df <- apply(var_pairs,1, function(c){
		best_E_fct(dftemp,c[1],c[2])
	})
	
	Best_E_df <- do.call("rbind",Best_E_df)
	Best_E_df$ID <- unique(df$ID)
	Best_E_df$treat <- unique(df$treat)
	Best_E_df$treat2 <- unique(df$treat2)
	Best_E_df$treat3 <- unique(df$treat3)
	
	rhos <- apply(Best_E_df, 1, function(r){
		ccm_out <- CCM(dataFrame = dftemp, target = r[1], column = r[2],
									 libSizes = "10 60 10", Tp = 0, E = as.numeric(r[3]), sample = 100)
		rho <- ccm_out[6,3]
		if(rho<0) return(data.frame(rho=rho,comment="negative"))
		slope <- lm(ccm_out[,3] ~ seq(10,60,by = 10))$coefficients[2]
		if(slope>=0) {return(data.frame(rho=rho,comment="converged"))
		} else {return(data.frame(rho=rho,comment="not converged"))}
	})
	
	Best_E_df <- cbind(Best_E_df,do.call("rbind",rhos))
	
	rho_df <- Best_E_df %>%
		dplyr::filter(target %in% targets, comment=="converged")
	
	significances <- apply(rho_df, 1, function(r){
		ts <- unlist(df[,as.character(r[2])])
		# target <- r[2]
		surr_interactor = SurrogateData(ts, method = "random_shuffle",
																		num_surr = 1000, alpha = 3)
		
		rho_surr <- data.frame(interactor_rho = numeric(1000))
		
		interactor_data = as.data.frame(cbind(df$day, ts, surr_interactor))
		names(interactor_data) = c("day", r[1], paste("T", as.character(seq(1, 1000)),	sep = ""))
		
		for (i in 1:1000) {
			targetCol = paste("T", i, sep = "") 
			ccm_out = CCM(dataFrame = interactor_data, E = as.numeric(r[3]), Tp = 0, columns = r[1],
										target = targetCol, libSizes = "60 60 10", sample = 1)
			col = paste(r[1], ":", targetCol, sep = "")
			rho_surr$interactor_rho[i] = ccm_out[1, col]
		}
		1 - ecdf(rho_surr$interactor_rho)(as.numeric(r["rho"]))
	})
	
	rho_df$significances <- significances
	pairwise_ccm_df <- full_join(Best_E_df,rho_df)
	pairwise_ccm_df
}, mc.cores = detectCores()-2)

save(pairwise_ccm_df_list, file = here("Data/CCM_analysis_data/pairwise_ccm_df_list_transf_resid.RData"))
```


## Estimations of interactions

```{r estimate_interactions, message=FALSE, warning=FALSE, cache=TRUE}
##############################################################
## Species interactions

# Load number of interactions
load(here("Data/CCM_analysis_data/pairwise_ccm_df_list_transf_resid.RData")) 
pairwise_ccm_df <- do.call("rbind",pairwise_ccm_df_list)

significant_pairwise_ccm_df <- pairwise_ccm_df %>%
	dplyr::filter(significances<0.05, rho >0)

# calculation of interactions 
list_smap <- lapply(targets, function(x){
  SMapInteractions(Target = x, num.clusters.target = 1, 
                   num.clusters.CV = NULL, method = "SMap", 
                   data = dd2, long_format = T, theta = 5, 
                   ccm_df = significant_pairwise_ccm_df)
})

dd_smap <- do.call("rbind", list_smap) %>%
  dplyr::filter(!(treat=="const" & interactor=="temperature"),
                Interaction!="C0")

significant_pairwise_ccm_df$Target2 <- label[significant_pairwise_ccm_df$target]

# Figure for number of interactions
num_int_plot <- significant_pairwise_ccm_df %>%
	na.omit() %>% 
	ggplot(aes(ID, fill=Target2)) +
	geom_bar(position = "identity")+
	facet_wrap(~Target2, ncol = 4)+
	standard_theme2() +
	scale_fill_brewer(palette="Dark2")+
	labs(x="Bottle ID", y="Number of interactions") +
	theme(strip.text = ggtext::element_markdown(),
				axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

rm(list_smap, pairwise_ccm_df_list)
```

# Regressions

## Relation between number of interactors, mean interaction strength and RMSE

```{r rq1_functions, message=FALSE, warning=FALSE, cache=TRUE}
# the following functions are needed because of the robustness analysis in the supplementary

rq1_model_fcts <- function(ddrq1_treat_14, iso=T, corr=T, count=T, mean_mean_abs=T, table=T){

	newdat <- NULL
	if(iso){
		m.iso <- lmer(RMSE~sum_mean_abs*treat + (1|ID), data = ddrq1_treat_14)
		newdat.iso <- expand.grid(sum_mean_abs = seq(min(ddrq1_treat_14$sum_mean_abs),
																								 max(ddrq1_treat_14$sum_mean_abs),length.out = 200),
															treat = unique(ddrq1_treat_14$treat))		
		newdat.iso$RMSE <- predict(m.iso, newdat.iso, re.form=NA)
		mm.iso <- model.matrix(terms(m.iso),newdat.iso)
		pvar1.iso <- diag(mm.iso %*% tcrossprod(vcov(m.iso),mm.iso))
		newdat.iso <- data.frame(newdat.iso,
														 lower.iso=newdat.iso$RMSE-cmult*sqrt(pvar1.iso),
														 upper.iso=newdat.iso$RMSE+cmult*sqrt(pvar1.iso))
		newdat.iso$model <- "iso"
		
		if(is.null(newdat)){
			newdat <- newdat.iso
		} else {
			newdat <- full_join(newdat,newdat.iso)
		}
	}
	
	if(count){
		m.count <- lmer(RMSE~count*treat + (1|ID), data = ddrq1_treat_14)
		newdat.count <- expand.grid(count = seq(min(ddrq1_treat_14$count),
																						max(ddrq1_treat_14$count),length.out = 200),
																treat = unique(ddrq1_treat_14$treat))
		newdat.count$RMSE <- predict(m.count, newdat.count, re.form=NA)
		mm.count <- model.matrix(terms(m.count),newdat.count)
		pvar1.count <- diag(mm.count %*% tcrossprod(vcov(m.count),mm.count))
		newdat.count <- data.frame(newdat.count,
															 lower.count=newdat.count$RMSE-cmult*sqrt(pvar1.count),
															 upper.count=newdat.count$RMSE+cmult*sqrt(pvar1.count))
		newdat.count$model <- "count"
		if(is.null(newdat)){
			newdat <- newdat.count
		} else {
			newdat <- full_join(newdat,newdat.count)
		}	
	}	
	
	if(mean_mean_abs){
		m.mean_mean_abs <- lmer(RMSE~mean_mean_abs*treat + (1|ID), data = ddrq1_treat_14)
		newdat.mean_mean_abs <- expand.grid(mean_mean_abs = seq(min(ddrq1_treat_14$mean_mean_abs),
																														max(ddrq1_treat_14$mean_mean_abs),length.out = 200),
																				treat = unique(ddrq1_treat_14$treat))
		newdat.mean_mean_abs$RMSE <- predict(m.mean_mean_abs, newdat.mean_mean_abs, re.form=NA)
		mm.mean_mean_abs <- model.matrix(terms(m.mean_mean_abs),newdat.mean_mean_abs)
		pvar1.mean_mean_abs <- diag(mm.mean_mean_abs %*% tcrossprod(vcov(m.mean_mean_abs),mm.mean_mean_abs))
		newdat.mean_mean_abs <- data.frame(newdat.mean_mean_abs, 
																			 lower.mean_mean_abs=newdat.mean_mean_abs$RMSE-cmult*sqrt(pvar1.mean_mean_abs),
																			 upper.mean_mean_abs=newdat.mean_mean_abs$RMSE+cmult*sqrt(pvar1.mean_mean_abs))
		newdat.mean_mean_abs$model <- "mean_mean_abs" 
		if(is.null(newdat)){
			newdat <- newdat.mean_mean_abs
		} else {
			newdat <- full_join(newdat,newdat.mean_mean_abs)
		}	
	}

	if(corr){
		m.corr <- lmer(mean_mean_abs~count*treat + (1|ID), data = ddrq1_treat_14)
		newdat.corr <- expand.grid(count = seq(min(ddrq1_treat_14$count),
																					 max(ddrq1_treat_14$count),length.out = 200),
															 treat = unique(ddrq1_treat_14$treat))
		newdat.corr$mean_mean_abs <- predict(m.corr, newdat.corr, re.form=NA)
		mm.corr <- model.matrix(terms(m.corr),newdat.corr)
		pvar1.corr <- diag(mm.corr %*% tcrossprod(vcov(m.corr),mm.corr))
		newdat.mean_mean_abs <- data.frame(newdat.mean_mean_abs, 
																			 lower.mean_mean_abs=newdat.mean_mean_abs$RMSE-cmult*sqrt(pvar1.mean_mean_abs),
																			 upper.mean_mean_abs=newdat.mean_mean_abs$RMSE+cmult*sqrt(pvar1.mean_mean_abs))
		newdat.corr <- data.frame(newdat.corr, 
															lower.corr=newdat.corr$mean_mean_abs-cmult*sqrt(pvar1.corr),
															upper.corr=newdat.corr$mean_mean_abs+cmult*sqrt(pvar1.corr))
		newdat.corr$model <-  "corr"
		if(is.null(newdat)){
			newdat <- newdat.corr
		} else {
			newdat <- full_join(newdat,newdat.corr)
		}	
	}	
	
	newdat$treat <- ifelse(newdat$treat %in% c("const","Constant"),"Constant","Fluctuating")

	if(table){
		# tab
		Covariates <- c("Fluctuating temperature","Interaction","Bottle ID")
		tab <- data.frame(Response = rep(c("RMSE\n ","RMSE","Mean\ninteraction\nstrength","RMSE"), each=5),
											Covariate = c("Intercept","Number of interactions",Covariates,
																		"Intercept","Mean interaction strength",Covariates,
																		"Intercept","Number of interactions",Covariates,
																		"Intercept","Sum of interaction stengths", Covariates),
											Type = rep(c("Fixed","Fixed","Fixed","Fixed","Std. Dev."), 4),
											Coefficient = c(fixef(m.count),as.data.frame(VarCorr(m.count))$sdcor[1],
																			fixef(m.mean_mean_abs),as.data.frame(VarCorr(m.mean_mean_abs))$sdcor[1],
																			fixef(m.corr),as.data.frame(VarCorr(m.corr))$sdcor[1],
																			fixef(m.iso),as.data.frame(VarCorr(m.iso))$sdcor[1]),
											Std.err = c(summary(m.count)$coef[, 2, drop = FALSE],NA,
																	summary(m.mean_mean_abs)$coef[, 2, drop = FALSE],NA,
																	summary(m.corr)$coef[, 2, drop = FALSE],NA,
																	summary(m.iso)$coef[, 2, drop = FALSE],NA),
											Test = c(rep("\\textit{t}",4),"$\\chi^2$",
															 rep("\\textit{t}",4),"$\\chi^2$",
															 rep("\\textit{t}",4),"$\\chi^2$",
															 rep("\\textit{t}",4),"$\\chi^2$"),
											Test.value = c(summary(m.count)$coef[, 4, drop = FALSE],lmerTest::rand(m.count)$LRT[2],
																		 summary(m.mean_mean_abs)$coef[, 4, drop = FALSE],lmerTest::rand(m.mean_mean_abs)$LRT[2],
																		 summary(m.corr)$coef[, 4, drop = FALSE],lmerTest::rand(m.corr)$LRT[2],
																		 summary(m.iso)$coef[, 4, drop = FALSE],lmerTest::rand(m.iso)$LRT[2]),
											p.value = c(summary(m.count)$coef[, 5, drop = FALSE],lmerTest::rand(m.count)$`Pr(>Chisq)`[2],
																	summary(m.mean_mean_abs)$coef[, 5, drop = FALSE],lmerTest::rand(m.mean_mean_abs)$`Pr(>Chisq)`[2],
																	summary(m.corr)$coef[, 5, drop = FALSE],lmerTest::rand(m.corr)$`Pr(>Chisq)`[2],
																	summary(m.iso)$coef[, 5, drop = FALSE],lmerTest::rand(m.iso)$`Pr(>Chisq)`[2]))
	} else {
		tab <- data.frame()
	}
	return(list(newdat, tab))
}


rq1_fct <- function(dd_smap, ddrq1, cv.dd=cv, permutation_entropies.dd=permutation_entropies, iso=T, corr=T, count=T, mean_mean_abs=T, table=T) {
	# first the dataset
	dd_smap_params_abs <- dd_smap %>%
		dplyr::filter(target!="temperature" & target!="dissolved_oxygen") %>%
		dplyr::group_by(ID,Interaction,treat,treat2,treat3,target,interactor) %>%
		summarize(mean = mean(Interaction_strength),
							mean.abs = mean(abs(Interaction_strength)),
							median = median(Interaction_strength),
							sd = sd(Interaction_strength),
							iqr = IQR(Interaction_strength),
							signal.to.noise = mean(Interaction_strength)/sd(Interaction_strength),
							signal.to.noise.abs = mean(abs(Interaction_strength))/sd(abs(Interaction_strength))) %>%
		group_by(target,treat,ID,treat2,treat3) %>%
		rename(Target=target) %>% 
		summarize(sum_abs_mu = sum(abs(mean)),
							sum_mean_abs = sum(mean.abs),
							count = n(),
							mean_abs_mean = mean(abs(mean)),
							mean_mean_abs = mean(mean.abs),
							median_mean_abs = median(mean.abs)) 
	
	ddrq1_treat_14 <- ddrq1 %>%
		dplyr::filter(num_pred==14) %>%
		group_by(Target,treat,ID,treat2,treat3) %>%
		full_join(dd_smap_params_abs)
	
	ddrq1_treat_14 <- full_join(ddrq1_treat_14, cv.dd)
	ddrq1_treat_14 <- full_join(ddrq1_treat_14, permutation_entropies.dd)
	
	ddrq1_treat_14$target <- ddrq1_treat_14$Target

	rq1_model_fcts_list <- rq1_model_fcts(ddrq1_treat_14, iso, corr, count, mean_mean_abs, table)
	
	
	return(c(list(ddrq1_treat_14), rq1_model_fcts_list, list(dd_smap_params_abs)))
}
```


```{r rmse_vs_numbInteraction_and_interStrength, warning=FALSE, cache=TRUE, message=FALSE}
cmult <- 1.96
rq1_list <- rq1_fct(dd_smap, ddrq1)
ddrq1_treat_14_theta5 <- ddrq1_treat_14 <- rq1_list[[1]]
newdat_theta5 <- newdat <- rq1_list[[2]]
tab.rq1.theta5 <- rq1_list[[3]]
dd_smap_params_abs <- rq1_list[[4]]
newdat_theta5$theta = 5
ddrq1_treat_14_theta5$theta = 5
tab.rq1.theta5 <- cbind(theta=5,tab.rq1.theta5)
```

```{r, fig.width=5, fig.height=3.5}
# dd_mean <- dd %>%
#   group_by(ID, variable) %>%
#   summarise(mean_abundance = mean(response),
#             abundance_unit = unique(unit)) %>%
#   dplyr::filter(variable %in% targets) %>%
#   rename(Target=variable)
# 
# tab <- full_join(dd_mean, ddrq1_treat_14) %>%
#   rename(bottle=ID) %>%
#   dplyr::select(bottle,Target,mean_abundance,abundance_unit,
#                 treat,treat3,RMSE,mean_mean_abs,median_mean_abs,mean_abs_mean) %>%
#   rename(Temperature = treat, TemperatureMoreDetailed = treat3) %>%
#   mutate(Temperature = ifelse(Temperature=="const","Constant","Fluctuating"))
# 
# # tab %>%
# #   ggplot(aes(log10(mean_abundance),mean_mean_abs, col=Target))+
# #   geom_point()+
# #   facet_wrap(~bottle, scales = "free")
# 
# tab %>%
#   ggplot(aes(log10(mean_abundance),mean_mean_abs, col=Target))+
#   geom_point()
# 
# write_csv(tab,"tab.csv")
```

## Forecast error vs. increasing number of predictors 


```{r increasing_predictors, cache=TRUE, fig.width=10, fig.height=6, message=FALSE, warning=FALSE}
cbbPalette <- c("#56B4E9", "#000000", "#E69F00", "#009E73")
ddrq1_summarized$interaction <- interaction(ddrq1_summarized$temperature_included, 	ddrq1_summarized$treat)
ddrq1_summarized$Target2 <- label[ddrq1_summarized$Target]

########################
# Big model

m.mv2 <- lmer(median_rmse ~ temperature_included*log10(num_pred) + 
						 	treat*log10(num_pred)  + treat*temperature_included +
						 	log10(num_pred)*Target + temperature_included*Target + 
						 	treat*Target + (1|Target:ID),
						 data = ddrq1_summarized)

newdat.mv <- with(ddrq1_summarized,
									expand.grid(temperature_included = unique(temperature_included),
															treat = unique(treat),
															num_pred = unique(num_pred),
															Target = unique(Target),
															median_rmse=0))

newdat.mv2 <- with(ddrq1_summarized,
									expand.grid(temperature_included = unique(temperature_included),
															treat = unique(treat),
															num_pred = unique(num_pred),
															Target = unique(Target),
															ID = unique(ID)))

newdat.mv2 <- cbind(newdat.mv2,
										predictInterval(m.mv2, newdata = newdat.mv2, which = "fixed", level=0.95, include.resid.var = F)) 

newdat.mv2 <- newdat.mv2 %>%
	dplyr::rename(lower=lwr, upper=upr, median_rmse=fit)
newdat.mv2$Target2 <- label[as.character(newdat.mv2$Target)]

cbbPalette <- c("#56B4E9", "#000000", "#E69F00", "#009E73")

plot2list <- split(ddrq1_summarized, ddrq1_summarized$Target)
plot2listnew <- list()
j <- 1
for(i in 1:length(plot2list)){
	df <- plot2list[[i]]
	nd <- newdat.mv2 %>% dplyr::filter(Target==unique(df$Target))
	a <- df %>% ggplot(aes(log10(num_pred), median_rmse,
												 group=interaction(ID,interaction),
												 col=interaction))+
		geom_line(size=0.5, alpha=0.35)+
		geom_point(na.rm = T, size=0.7, alpha=0.7)+
		standard_theme()+
		theme(legend.position = "none", axis.title = element_blank(),
					plot.margin = margin(r=-1, l=10), plot.subtitle = ggtext::element_markdown())+
		scale_color_manual(values = cbbPalette, aesthetics = c("col","fill"),
											 labels = c("Constant & Not a predictor","Constant & Predictor","Fluctuating & Not a predictor","Fluctuating & Predictor")) +
		scale_x_continuous(breaks = c(0,0.3,0.6,1))+
		labs(y="Median RMSE",x="log10(Number of predictors used)", col="Temperature", tag=tag[i], subtitle = unique(df$Target2)) +
		guides(col=guide_legend(nrow=2,byrow=TRUE))
	
	nd$Target2<- ""
	b <- nd %>%
		ggplot(aes(log10(num_pred), median_rmse, col=interaction(temperature_included,treat),
							 fill=interaction(temperature_included,treat)))+
		geom_ribbon(aes(ymin=lower,ymax=upper), alpha=0.2, size=0.1)+
		geom_line(size=1, alpha=0.5)+
		standard_theme()+
		theme(legend.position = "none", axis.title = element_blank(), axis.text.y = element_blank(), axis.ticks.y=element_blank(),
					plot.margin = margin(l=-1,r=3))+
		scale_color_manual(values = cbbPalette, aesthetics = c("col","fill"),
											 labels = c("Constant & Not a predictor","Constant & Predictor","Fluctuating & Not a predictor","Fluctuating & Predictor")) +
		labs(y="Median RMSE",x="log10(Number of predictors used)", col="Temperature", fill="Temperature") +
		scale_x_continuous(breaks = c(0,0.3,0.6,1))+
		guides(col=guide_legend(nrow=2,byrow=TRUE)) +
		ylim(ggplot_build(a)$layout$panel_scales_y[[1]]$range$range)
	
	if(i %in% 7:8) {
		a <- a + theme(plot.margin = margin(r=-1, l=10, b=10))
		b <- b + theme(plot.margin = margin(l=-1, r=3, b=10))
	}
	plot2listnew[[j]] <- a
	plot2listnew[[j+1]] <- b
	j <- j + 2
}

plot2leg <- ddrq1_summarized %>% ggplot(aes(log10(num_pred), median_rmse,
												 group=interaction(ID,interaction),
												 col=interaction))+
	geom_smooth(aes(fill=interaction), col=NA)+
	geom_line(size=0.5, alpha=1)+
	geom_point(na.rm = T, size=0.7, alpha=1)+
	standard_theme()+
	theme(legend.position = "bottom", axis.title = element_blank(),
				plot.margin = margin(r=-1, l=10), plot.subtitle = ggtext::element_markdown())+
	scale_color_manual(values = cbbPalette, aesthetics = c("col","fill"),
										 labels = c("Constant & Not a predictor","Constant & Predictor","Fluctuating & Not a predictor","Fluctuating & Predictor")) +
	scale_x_continuous(breaks = c(0,0.3,0.6,1))+
	labs(y="Median RMSE",x="log10(Number of predictors used)", col="Temperature", fill="Temperature", tag=tag[i], subtitle = unique(df$Target2)) +
	guides(col=guide_legend(nrow=2,byrow=TRUE))

plot2leg <- get_legend(plot2leg)

ylab <- ggplot(data.frame(l = "            Forecast error (median RMSE)", x = 1, y = 1)) +
	geom_text(aes(x, y, label = l), angle = 90, size=5) + 
	theme_void() +
	coord_cartesian(clip = "off")

xlab <- ggplot(data.frame(x = 1, y = 1)) +
	geom_text(aes(x, y), label = expression('log'[10]~"(Number of predictors used)"), size=5) + 
	theme_void() +
	coord_cartesian(clip = "off")

covariates.mv.t  <- c("(Intercept)","temperature_includedTRUE","log10(num_pred)","treattreat",
											"temperature_includedTRUE:log10(num_pred)","log10(num_pred):treattreat",
											"temperature_includedTRUE:treattreat")
index.mv.t <- which(names(fixef(m.mv2)) %in% covariates.mv.t)
covariates.mv.F <- rownames(anova(m.mv2))[c(4,8,9,10)]


mv.tab <- data.frame(Covariate = c("\\textbf{Intercept}","\\textbf{A: Temperature is predictor}","\\textbf{B: log10(nr. of predictors)}",
										 							"\\textbf{C: Fluctuating temperature}",
										 							"\\textit{C. reinhardtii}", "\\textit{C. striatum}", "\\textit{D. campylum}",
										 							"\\textit{E. gracilis}", "\\textit{E. daidaleos}", "\\textit{P. caudatum}", "\\textit{Rotifer} sp.",
										 							"\\textbf{Interaction: A:B}", "\\textbf{Interaction: B:C}", "\\textbf{Interaction: A:C}",
										 							"\\textit{C. reinhardtii}", "\\textit{C. striatum}", "\\textit{D. campylum}",
										 							"\\textit{E. gracilis}", "\\textit{E. daidaleos}", "\\textit{P. caudatum}", "\\textit{Rotifer} sp.",
										 							"\\textit{C. reinhardtii}", "\\textit{C. striatum}", "\\textit{D. campylum}",
										 							"\\textit{E. gracilis}", "\\textit{E. daidaleos}", "\\textit{P. caudatum}", "\\textit{Rotifer} sp.",
										 							"\\textit{C. reinhardtii}", "\\textit{C. striatum}", "\\textit{D. campylum}",
										 							"\\textit{E. gracilis}", "\\textit{E. daidaleos}", "\\textit{P. caudatum}", "\\textit{Rotifer} sp."),
										 Estimate_type = "Coefficient",
										 Estimate = c(fixef(m.mv2)),
										 DF= c(round(summary(m.mv2)$coef[,3,drop = FALSE],0)),
										 Std.err = c(summary(m.mv2)$coef[,2,drop = FALSE]),
										 Test = "\\textit{t}",
										 Test.value = c(summary(m.mv2)$coef[,4,drop = FALSE]),
										 p.value = c(summary(m.mv2)$coef[, 5, drop = FALSE]))



mv.tab.anova <- data.frame(Covariate = c("\\textbf{A: Temperature is predictor}","\\textbf{B: log10(nr. of predictors)}",
													 							"\\textbf{C: Fluctuating temperature}", "\\textbf{D: Target species}",
													 							"\\textbf{Interaction: A:B}", "\\textbf{Interaction: B:C}", "\\textbf{Interaction: A:C}", 
													 							"\\textbf{Interaction: B:D}", "\\textbf{Interaction: A:D}", "\\textbf{Interaction: C:D}"),
													 Estimate_type = "Sum of sq.",
													 Estimate = anova(m.mv2)[,1],
													 DF= paste(anova(m.mv2)[,3],round(anova(m.mv2)[,4],1), sep = ", "),
													 Std.err = NA,
													 Test = "\\textit{F}",
													 Test.value = anova(m.mv2)[,5],
													 p.value = anova(m.mv2)[,6])


mv.tab.rand <- data.frame(Covariate = "\\textbf{Bottle ID nested in Target}",
													Estimate_type = "Rand. effect",
													Estimate = as.data.frame(VarCorr(m.mv2))$sdcor[1],
													DF= lmerTest::rand(m.mv2)$Df[2],
													Std.err = NA,
													Test = "$\\chi^2$",
													Test.value = lmerTest::rand(m.mv2)$LRT[2],
													p.value = lmerTest::rand(m.mv2)$`Pr(>Chisq)`[2])
	


mv.tab <- rbind(mv.tab,mv.tab.anova,mv.tab.rand)
 
rm(a,b,df,plot2list,nd, newdat.mv)
```



## Number of predictors in best model vs number of interactors


The following chunk is not run. Its results are loaded in the successive chunk


```{r interactors_used_as_predictors, cache=TRUE, message=FALSE, eval=FALSE}
## using only the species that significantly interacted with the target as predictors in the forecasting

significant_pairwise_ccm_df_summarized <- significant_pairwise_ccm_df %>%
	group_by(treat, ID, target) %>%
	summarize(interactor_combination = paste(interactor, collapse = " "))

temp.list <- split(significant_pairwise_ccm_df_summarized, f = significant_pairwise_ccm_df_summarized$ID)

mvForecasts_interactorsAsPredictors <- mclapply(temp.list, function(sig_df){
	temp <- apply(sig_df, 1, function(row){
		df <- dd2 %>% dplyr::filter(ID==row["ID"])
		predictors <- strsplit(unlist(row["interactor_combination"]), " ")
		model_fitter(data = df, target = unname(row["target"]),
								 predictor_combinations = predictors, max_lag = 3,
								 E = 3, ID = row["ID"], k = ks)
	})
	do.call("rbind", temp)
}, mc.cores = detectCores()-1)

mvForecasts_interactorsAsPredictors_E2 <- mclapply(temp.list, function(sig_df){
	temp <- apply(sig_df, 1, function(row){
		df <- dd2 %>% dplyr::filter(ID==row["ID"])
		predictors <- strsplit(unlist(row["interactor_combination"]), " ")
		model_fitter(data = df, target = unname(row["target"]),
								 predictor_combinations = predictors, max_lag = 3,
								 E = 2, ID = row["ID"], k = ks)
	})
	do.call("rbind", temp)
}, mc.cores = detectCores()-1)

mvForecasts_interactorsAsPredictors_E4 <- mclapply(temp.list, function(sig_df){
	temp <- apply(sig_df, 1, function(row){
		df <- dd2 %>% dplyr::filter(ID==row["ID"])
		predictors <- strsplit(unlist(row["interactor_combination"]), " ")
		model_fitter(data = df, target = unname(row["target"]),
								 predictor_combinations = predictors, max_lag = 3,
								 E = 4, ID = row["ID"], k = ks)
	})
	do.call("rbind", temp)
}, mc.cores = detectCores()-1)

mvForecasts_interactorsAsPredictors <- 	do.call("rbind", mvForecasts_interactorsAsPredictors)
mvForecasts_interactorsAsPredictors_E2 <- 	do.call("rbind", mvForecasts_interactorsAsPredictors_E2)
mvForecasts_interactorsAsPredictors_E4 <- 	do.call("rbind", mvForecasts_interactorsAsPredictors_E4)

save(mvForecasts_interactorsAsPredictors, file = here("Data/Multiview_forecast_data/mvForecasts_interactorsAsPredictors.RData"))
save(mvForecasts_interactorsAsPredictors_E2, file = here("Data/Multiview_forecast_data/mvForecasts_interactorsAsPredictors_E2.RData"))
save(mvForecasts_interactorsAsPredictors_E4, file = here("Data/Multiview_forecast_data/mvForecasts_interactorsAsPredictors_E4.RData"))
```


```{r number_of_interactors_vs_number_of_predictors, cache=TRUE, fig.width=10, fig.height=6, message=FALSE}
load(here("Data/Multiview_forecast_data/mvForecasts_interactorsAsPredictors.RData")) # done previously

ddrq1$temperature_included <- as.logical(ddrq1$temperature_included)
ddrq1$target_excluded <- as.logical(ddrq1$target_excluded)
ddrq1 <- full_join(ddrq1, mvForecasts_interactorsAsPredictors)
ddrq1 <- ddrq1 %>%
	group_by(ID, treat, Target) %>%
	mutate(best_rmse_bool = RMSE==min(RMSE),
				 min_rmse = min(RMSE)) %>%
	mutate(RMSE_equi = case_when(abs(RMSE-min_rmse)/((RMSE+min_rmse)/2) <= 0.01 ~ T,
															 abs(RMSE-min_rmse)/((RMSE+min_rmse)/2) > 0.01 ~ F))

ddrq1_equi <- ddrq1

ddrq1_best <- ddrq1 %>% 
	dplyr::filter(RMSE_equi==T) %>%
	group_by(ID, treat, Target) %>%
	slice_min(num_pred,n=1) %>%
	slice_min(RMSE,n=1) %>% 
	sample_n(1)

ddrq1_best <- full_join(ddrq1_best, dd_smap_params_abs)

ddrq1_best$Treat <- ifelse(ddrq1_best$treat=="const",
														 "Constant temperature","Fluctuating temperature")
ddrq1_best$treat4 <- ifelse(ddrq1_best$treat=="const","Constant","Fluctuating")
ddrq1_best$Target <- label[ddrq1_best$Target]
ddrq1_best$log10_num_pred <- log10(ddrq1_best$num_pred)
ddrq1_best$sqrtsqrtcount <- sqrt(sqrt(ddrq1_best$count))
ddrq1_best$sqrtsqrt_num_pred <- sqrt(sqrt(ddrq1_best$num_pred))
m.numpred.numint <- lmer(log10_num_pred~count*treat + (1|ID), data = ddrq1_best)

newdat.numpred <- expand.grid(count = seq(min(ddrq1_best$count), max(ddrq1_best$count),length.out = 200),
                          treat = unique(ddrq1_best$treat))
newdat.numpred$log10_num_pred <- predict(m.numpred.numint, newdat.numpred, re.form=NA)
mm.numpred <- model.matrix(terms(m.numpred.numint),newdat.numpred)
pvar1.numpred <- diag(mm.numpred %*% tcrossprod(vcov(m.numpred.numint),mm.numpred))
newdat.numpred <- data.frame(newdat.numpred,
														 lower.numpred=newdat.numpred$log10_num_pred-cmult*sqrt(pvar1.numpred),
														 upper.numpred=newdat.numpred$log10_num_pred+cmult*sqrt(pvar1.numpred))


tab.num_vs_num <- data.frame(Covariate = c("Intercept","Number of interactions",
																					 "Fluctuating temperature","Interaction","Bottle ID"),
														 Var_Type = c("Fixed","Fixed","Fixed","Fixed","Std. Dev."),
														 Coefficient = c(fixef(m.numpred.numint),as.data.frame(VarCorr(m.numpred.numint))$sdcor[1]),
														 Std.err = c(summary(m.numpred.numint)$coef[, 2, drop = FALSE],NA),
														 Test = c(rep("\\textit{t}",4),"$\\chi^2$"),
														 Test.value = c(summary(m.numpred.numint)$coef[, 4, drop = FALSE],lmerTest::rand(m.numpred.numint)$LRT[2]),
														 p.value = c(summary(m.numpred.numint)$coef[, 5, drop = FALSE],lmerTest::rand(m.numpred.numint)$`Pr(>Chisq)`[2]))

rm(mvForecasts_interactorsAsPredictors, mm.numpred)
load(here("Data/Multiview_forecast_data/ddrq1_transf_resid_which_all.RData"))  # reloaded.. same as above
ddrq1 <- ddrq1 %>% na.omit()

ddrq1_best_suppl <- ddrq1_best
```


## Predictor importance vs interaction strength vs RMSE

```{r predictor_interactor, cache=TRUE, message=FALSE, warning=FALSE}
ddrq1_importance <- ddrq1 %>%
  dplyr::filter(num_pred==1) %>%
  full_join(dd_smap_params_abs)

ddrq1_importance$predictor_combination <- ifelse(ddrq1_importance$predictor_combination=="small-white_particle","small_white_particle",
																								 ifelse(ddrq1_importance$predictor_combination=="green-white_particle","green_white_particle",
																								 			 ddrq1_importance$predictor_combination))

ddrq1_importance$target <- ddrq1_importance$Target
ddrq1_importance$interactor <- ddrq1_importance$predictor_combination

dd_mean_is <- dd_smap %>%
  dplyr::filter(target!="temperature" & target!="dissolved_oxygen") %>%
  dplyr::group_by(ID,Interaction,treat,treat2,treat3,target,interactor) %>%
  summarize(mean = mean(Interaction_strength),
            mean.abs = mean(abs(Interaction_strength)),
            median = median(Interaction_strength),
            sd = sd(Interaction_strength),
            iqr = IQR(Interaction_strength),
  					signal.to.noise = mean(Interaction_strength)/sd(Interaction_strength),
  					signal.to.noise.abs = mean(abs(Interaction_strength))/sd(abs(Interaction_strength))) %>%
  mutate(sd.transformed = log10(sd),
         mean.transformed = abs(mean)^(1/4),
         mean.abs.transformed = (mean.abs)^(1/4),
         iqr.transformed = log10(iqr),
         median.transformed = abs(median)^(1/4))

ddrq1_importance <- inner_join(ddrq1_importance, dd_mean_is)

ddrq1_importance$log10.mean.abs <- log10(ddrq1_importance$mean.abs)
m.pred.imp <- lmer(RMSE~log10.mean.abs*treat*Target + (1|ID), data = ddrq1_importance)

temp <- split(ddrq1_importance, f = interaction(ddrq1_importance$Target,ddrq1_importance$treat))
 
newdat.m.pred.imp <- lapply(temp, function(df){
  expand.grid(log10.mean.abs = seq(min(df$log10.mean.abs, na.rm = T),max(df$log10.mean.abs, na.rm = T),length.out = 100),
              treat = unique(df$treat),
              Target = unique(df$Target))
})

newdat.m.pred.imp <- do.call("rbind", newdat.m.pred.imp)
newdat.m.pred.imp <- cbind(newdat.m.pred.imp,RMSE=predict(m.pred.imp, newdat.m.pred.imp, re.form=NA))

m.pred.imp.model.matrix <- model.matrix(terms(m.pred.imp),newdat.m.pred.imp)

pvar1.m.pred.imp <- diag(m.pred.imp.model.matrix %*% tcrossprod(vcov(m.pred.imp),m.pred.imp.model.matrix))

newdat.m.pred.imp <- data.frame(newdat.m.pred.imp,
                         lower=newdat.m.pred.imp$RMSE-cmult*sqrt(pvar1.m.pred.imp),
                         upper=newdat.m.pred.imp$RMSE+cmult*sqrt(pvar1.m.pred.imp))

newdat.m.pred.imp$treat <- ifelse(newdat.m.pred.imp$treat=="const","Constant","Fluctuating")
ddrq1_importance$treat <- ifelse(ddrq1_importance$treat=="const","Constant","Fluctuating")

order.interactors <- c("Bacteria","*Chlamydomonas reinhardtii*","*Colpidium striatum*",
											 "*Dexiostoma campylum*","*Didinium nasutum*","*Euglena gracilis*","*Euplotes daidaleos*",
											 "*Paramecium caudatum*","*Rotifer* sp.","Big and white flagellates","Green and white flagellates",
											 "Small and white flagellates","Dissolved oxygen","Temperature")

order.targets <- c("Bacteria","*Chlamydomonas reinhardtii*","*Colpidium striatum*",
									 "*Dexiostoma campylum*","*Euglena gracilis*","*Euplotes daidaleos*",
									 "*Paramecium caudatum*","*Rotifer* sp.")

ddrq1_importance$interactor <- factor(label[ddrq1_importance$interactor], levels = order.interactors)
ddrq1_importance$Target <- factor(label[ddrq1_importance$Target], levels = order.targets)
newdat.m.pred.imp$Target <- label[as.vector(newdat.m.pred.imp$Target)]

# palette <- colorRampPalette(brewer.pal(name="Paired", n = 12))(14)
palette2 <- c(brewer.pal(name="Paired", n = 12),"black","grey")
palette2[[11]] <- "#fafa00"


covariates.m.pred.imp  <- c("(Intercept)","log10.mean.abs","treattreat",
														"log10.mean.abs:treattreat")
index.m.pred.imp <- which(names(fixef(m.pred.imp)) %in% covariates.m.pred.imp)


mv.interactopredictor <- data.frame(Covariate = c("\\textbf{Intercept}","\\textbf{A: log10(mean int. strength)}",
																									"\\textbf{B: Fluctuating temperature}", 
																									# "C: Target species", 
																									"\\textit{C. reinhardtii}", "\\textit{C. striatum}", "\\textit{D. campylum}",
																									"\\textit{E. gracilis}", "\\textit{E. daidaleos}", "\\textit{P. caudatum}", "\\textit{Rotifer} sp.",
																									"\\textbf{Interaction: A:B}",
																									# "Interaction: A:C", 
																									"\\textit{C. reinhardtii}", "\\textit{C. striatum}", "\\textit{D. campylum}",
																									"\\textit{E. gracilis}", "\\textit{E. daidaleos}", "\\textit{P. caudatum}", "\\textit{Rotifer} sp.",
																									# "Interaction: B:C", 
																									"\\textit{C. reinhardtii}", "\\textit{C. striatum}", "\\textit{D. campylum}",
																									"\\textit{E. gracilis}", "\\textit{E. daidaleos}", "\\textit{P. caudatum}", "\\textit{Rotifer} sp.",																														# "Interaction: A:B:C", 
																									"\\textit{C. reinhardtii}", "\\textit{C. striatum}", "\\textit{D. campylum}",
																									"\\textit{E. gracilis}", "\\textit{E. daidaleos}", "\\textit{P. caudatum}", "\\textit{Rotifer} sp."),
																		Estimate_type = "Coefficient",
																		Estimate = c(fixef(m.pred.imp)),
																		DF= c(round(summary(m.pred.imp)$coef[,3,drop = FALSE],0)),
																		Std.err = c(summary(m.pred.imp)$coef[,2,drop = FALSE]),
																		Test = "\\textit{t}",
																		Test.value = c(summary(m.pred.imp)$coef[,4,drop = FALSE]),
																		p.value = c(summary(m.pred.imp)$coef[, 5, drop = FALSE]))


mv.interactopredictor.anova <- data.frame(Covariate = c("\\textbf{A: log10(mean int. strength))}","\\textbf{B: Fluctuating temperature}",
																												"\\textbf{C: Target species}",
																												"\\textbf{Interaction: A:B}", "\\textbf{Interaction: A:C}", "\\textbf{Interaction: B:C}", 
																												"\\textbf{Interaction: A:B:C}"),
																					Estimate_type = "Sum of sq.",
																					Estimate = anova(m.pred.imp)[,1],
																					DF= paste(anova(m.pred.imp)[,3],round(anova(m.pred.imp)[,4],1), sep = ", "),
																					Std.err = NA,
																					Test = "\\textit{F}",
																					Test.value = anova(m.pred.imp)[,5],
																					p.value = anova(m.pred.imp)[,6])


mv.interactopredictor.rand <- data.frame(Covariate = "\\textbf{Bottle ID}",
																					Estimate_type = "Rand. effect",
																					Estimate = as.data.frame(VarCorr(m.pred.imp))$sdcor[1],
																					DF= lmerTest::rand(m.pred.imp)$Df[2],
																					Std.err = NA,
																					Test = "$\\chi^2$",
																					Test.value = lmerTest::rand(m.pred.imp)$LRT[2],
																					p.value = lmerTest::rand(m.pred.imp)$`Pr(>Chisq)`[2])

mv.interactopredictor <- rbind(mv.interactopredictor, mv.interactopredictor.anova, mv.interactopredictor.rand)


rm(temp, covariates.m.pred.imp, covariates.mv.F, covariates.mv.t, i, j, index.m.pred.imp, index.mv.t, pvar1.m.pred.imp, pvar1.numpred)
```

# Results and figures (main text)

## Relation between number of interactions, mean interaction strength and forecast error

```{r mean_int_rmse_plot, fig.width=13, fig.height=6.5, out.width="95%", cache=TRUE, message=FALSE}
ddrq1_treat_14$treat <- ifelse(ddrq1_treat_14$treat=="const","Constant","Fluctuating")
ddrq1_treat_14$Target2 <- label[ddrq1_treat_14$Target]
plot_leg <-
	ddrq1_treat_14 %>%
	ggplot(aes(count,RMSE, group=treat, shape=treat, col=Target2, fill=Target2))+
	geom_point(size=2.5)+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	standard_theme()+
	theme(legend.position = "right", legend.box="vertical",
				legend.text = ggtext::element_markdown()) +
	labs(shape="Temperature", fill= "Target", col="Target") +
	guides(fill=guide_legend(nrow=8,byrow=TRUE), shape=guide_legend(nrow=2,byrow=TRUE))

plot1a <- ddrq1_treat_14 %>%
  ggplot(aes(count,RMSE, group=treat, shape=treat))+
  geom_line(data=newdat_theta5 %>% dplyr::filter(model=="count"))+
  geom_ribbon(data=newdat_theta5 %>% dplyr::filter(model=="count"), aes(ymax=lower.count,ymin=upper.count), alpha=0.2, col=NA) +
  geom_point(aes(fill=Target2),size=2.5,col="black")+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2")+
  standard_theme()+
  facet_wrap(~treat)+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	labs(x=expression("Number of interactions"~italic(N[T])), y="Forecast error (RMSE)", tag = "A")

plot1b <- ddrq1_treat_14 %>%
  ggplot(aes(mean_mean_abs,RMSE, group=treat, shape=treat))+
  geom_line(data=newdat_theta5 %>% dplyr::filter(model=="mean_mean_abs"))+
  geom_ribbon(data=newdat_theta5 %>% dplyr::filter(model=="mean_mean_abs"), aes(ymax=lower.mean_mean_abs,ymin=upper.mean_mean_abs), alpha=0.2, col=NA) +
  geom_point(aes(fill=Target2),size=2.5, col="black")+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2")+
  standard_theme()+
  facet_wrap(~treat)+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	labs(x=expression("Mean interaction strength"~italic(mu["T"])), y="Forecast error (RMSE)", tag = "B")

plot1c <- ddrq1_treat_14 %>%
  ggplot(aes(count, mean_mean_abs, group=treat, shape=treat))+
  geom_line(data=newdat_theta5 %>% dplyr::filter(model=="corr"))+
  geom_ribbon(data=newdat_theta5 %>% dplyr::filter(model=="corr"), aes(ymax=lower.corr,ymin=upper.corr), alpha=0.2, col=NA) +
  geom_point(aes(fill=Target2),size=2.5, col="black")+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2")+
	standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat) +
	labs(x=expression("Number of interactions"~italic(N[T])),
			 y=expression("Mean interaction strength"~italic(mu["T"])), tag = "C")

plot1d <- ddrq1_treat_14 %>%
  ggplot(aes(sum_mean_abs,RMSE, group=treat, shape=treat))+
  # geom_line(data=newdat_theta5 %>% dplyr::filter(model=="iso"))+
  # geom_ribbon(data=newdat_theta5 %>% dplyr::filter(model=="iso"), aes(ymax=lower.iso,ymin=upper.iso), alpha=0.2, col=NA) +
  geom_point(aes(fill=Target2),size=2.5, col="black")+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2")+
	standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat)+
	labs(x=expression("Sum of interaction strength"~Sigma[italic("T")]), y="Forecast error (RMSE)", tag = "D")

plot1_leg <- get_legend(plot_leg)

plot1 <- ((plot1a+plot1b+plot1c+plot1d + plot_layout(ncol = 2)) | plot1_leg ) + plot_layout(widths = c(3,1))
plot1
rm(plot1a, plot1b, plot1c, plot1d, plot_leg, plot1_leg)
```


## Forecast error as a function of number of predictors and temperature

```{r rmse_vs_numpred, fig.width=10, fig.height=10, out.width="95%", cache=TRUE, message=FALSE, warning=FALSE}
plot2 <- ((ylab + ((Reduce("+", plot2listnew) + plot_layout(ncol = 4)) / xlab + plot_layout(heights = c(50,1))) + plot_layout(widths = c(1,50)))) / plot2leg + plot_layout(heights = c(51,6)) 
plot2
```

```{r num_int_vs_numb_pred, fig.width=6, fig.height=7, out.width="47.5%", cache=TRUE, message=FALSE}
plot3_leg <-
	ddrq1_best %>%
	ggplot(aes(count,num_pred, group=treat4, col=Target, fill=Target))+
	geom_point(size=2, shape=21)+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	standard_theme()+
	labs(col="Target",fill="Target")+
	theme(legend.position = "right", legend.box="horizontal",
				legend.text = ggtext::element_markdown(size = 11),
				legend.title = element_text(size=12)) +
	guides(fill=guide_legend(nrow=3,byrow=TRUE), shape=guide_legend(nrow=2,byrow=TRUE))

newdat.numpred$Treat <- ifelse(newdat.numpred$treat=="const",
														 "Constant temperature","Fluctuating temperature")
newdat.numpred$treat4 <- ifelse(newdat.numpred$treat=="const","Constant","Fluctuating")

plot3a <-
	ddrq1_best %>%
	ggplot(aes(count,num_pred, group=treat4)) +
  geom_line(data=newdat.numpred, mapping = aes(count,10^log10_num_pred))+
  geom_ribbon(data=newdat.numpred, aes(y=10^log10_num_pred,  ymax=10^lower.numpred,ymin=10^upper.numpred), alpha=0.2, col=NA) +
	geom_point(aes(fill=Target),size=2.5,col="black", alpha=0.5, shape=21)+
	scale_fill_brewer(palette = "Dark2")+
	facet_wrap(~Treat) +
	standard_theme() +
	labs(x=expression("Number of interactions"~italic(N[T])), y="Number of predictors\nin best model",
			 tag="A")+
	theme(legend.position = "none", legend.box="vertical",
				axis.title = element_text(size=12),
				axis.text = element_text(size=11),
				strip.text = element_text(size=12, hjust = 0, vjust = 1.8, margin = margin(t = 2, r = 0, b = 0, l = 0, unit = "pt"))) + 
	scale_y_continuous(breaks = seq(2, 10, len = 5))

plot3b <- ddrq1_best %>%
	ggplot(aes(num_pred, fill=Target)) +
	geom_bar() +
	scale_fill_brewer(palette = "Dark2")+
	standard_theme()+
	facet_wrap(~Treat) +
	scale_x_continuous(breaks = seq(1,13,by = 2)) +
	labs(x="Number of predictors in best model", y="Count",
			 tag="B")+
	theme(legend.position = "none", legend.box="vertical",
				axis.title = element_text(size=12),
				axis.text = element_text(size=11),
				strip.text = element_text(size=12, hjust = 0, vjust = 1.8, margin = margin(t = 2, r = 0, b = 0, l = 0, unit = "pt")))

plot3_leg <- get_legend(plot3_leg)

plot3main <- plot3a/plot3b/plot3_leg + plot_layout(heights = c(3.5,3.5,1.7))
plot3main
```


## Interactor strength versus predictor importance

```{r pred_imp_plot, fig.width=13, fig.height=9, out.width="95%", cache=TRUE, message=FALSE, warning=FALSE}
ddrq1_importance_list <- split(ddrq1_importance, ddrq1_importance$Target)

ddrq1_importance_list <- lapply(1:length(ddrq1_importance_list), function(i){
	df <- ddrq1_importance_list[[i]]
	nd <- newdat.m.pred.imp %>% dplyr::filter(Target==unique(df$Target))
	plot <- df %>%
		ggplot(aes(log10.mean.abs, shape=treat, RMSE))+
		geom_point(aes(fill=interactor),size=2, col="black")+
		facet_wrap(~treat, ncol = 4) +
		labs(subtitle = unique(df$Target), tag=tag[i], x=expression('log'[10]~"(Mean interaction strength)")) +
		scale_shape_manual(values=c(21,23))+
		scale_color_manual(breaks = levels(ddrq1_importance$interactor),
											 values = palette2, aesthetics = c("fill","color"))+
		standard_theme() +
		theme(legend.position = "none",
					panel.spacing =  unit(0, "lines"),
					axis.title = element_blank(),
					strip.text.x = element_blank(),
					legend.text = ggtext::element_markdown(),
					plot.subtitle = ggtext::element_markdown()) +
    guides(col=guide_legend(ncol=2))
	
	if(unique(df$target) %in% c("chlamydomonas_reinhardtii","euglena_gracilis")){
		plot <- plot + 	
			geom_ribbon(data=nd, aes(ymin=lower, ymax=upper, y=RMSE), alpha=0.2, col=NA)+
			geom_line(data=nd, aes(log10.mean.abs,RMSE))
	}
	plot
})

m.pred.imp.plot.leg <- ddrq1_importance %>%
	ggplot(aes(log10.mean.abs,RMSE,shape=treat))+
	geom_point(aes(col=interactor,fill=interactor),size=2,)+
	facet_wrap(~treat, ncol = 4) +
	scale_color_manual(breaks = levels(ddrq1_importance$interactor),
										 values = palette2, aesthetics = c("fill","color"))+
	standard_theme() +
	scale_shape_manual(values=c(21,23))+
	theme(legend.position = "right",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				legend.text = ggtext::element_markdown(size = 11),
				plot.subtitle = ggtext::element_markdown()) +
	labs(shape="Temperature", fill= "Interactor/Predictor", col="Interactor/Predictor") +
	geom_smooth(method = "lm")+
	guides(col=guide_legend(ncol=2))

m.pred.imp.plot.leg <- get_legend(m.pred.imp.plot.leg)

ylab <- ggplot(data.frame(l = "    Forecast error (RMSE)", x = 1, y = 1)) +
	geom_text(aes(x, y, label = l), angle = 90, size=6) +
	theme_void() +
	coord_cartesian(clip = "off")

xlab <- ggplot(data.frame(x = 1, y = 1)) +
	geom_text(aes(x, y), label = expression('log'[10]~"(Mean interaction strength)"), size=6) +
	theme_void() +
	coord_cartesian(clip = "off")

plot4 <- ((ylab + ((Reduce("+", ddrq1_importance_list) + plot_layout(ncol = 2)) / xlab + plot_layout(heights = c(50,1))) + m.pred.imp.plot.leg + plot_layout(widths = c(2,80,20))))
plot4
```



# Supplementary material: Analyses

## Sensitivity analysis for the embedding dimension in the forecasts

The following two code chunks redo the multiview EDM forecasting, but with E=2 and E=3 respectively. They are not run here, but their results are loaded in afterwards.

```{r multiview_forecast_analysis_E2, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
##############################################################
## Species forecasting 

# First some preparation:
ks <- unique(round(exp(seq(log(0.8),log(100.4),length.out = 33))))

possible_predictors <- c("bacteria","chlamydomonas_reinhardtii","colpidium_striatum",
                         "dexiostomata_campylum", "didinium_nasutum",
                         "euglena_gracilis","euplotes_daidaleos","paramecium_caudatum",
                         "rotifer_sp","big_white_particle","dissolved_oxygen",
                         "green_white_particle", "small_white_particle")
 
dd2 <- dd2 %>% ungroup()
set.seed(54)
which=c(1,2,3,4,6,8,10,13)
predictor_combinations <- predictor_combinator(possible_predictors, which=which)

mvForecasts_list_E2 <- lapply(targets, function(target){
  print(target)
  df1 <- model_fitter_wrapper(whole.data = dd2, 
                              predictor_combinations = predictor_combinations,
                              target = target,
                              num.clusters = detectCores()-2, 
                              E = 2, max_lag = 3, k=ks)
})

mvForecasts_E2 <- do.call("rbind", mvForecasts_list_E2)

predictors <- c(possible_predictors,"temperature")
mvForecasts_E2$predictor_combination <- as.character(mvForecasts_E2$predictor_combination)
temp <- matrix(F, nrow = nrow(mvForecasts_E2), ncol = length(predictors))
colnames(temp) <- predictors
mvForecasts_E2 <- cbind(mvForecasts_E2,temp)

mvForecasts_E2 <- as.data.frame(t(apply(mvForecasts_E2, 1, function(row) { 
  str <- unlist(strsplit(row["predictor_combination"], " "))
  row[str] <- T
  row
})))

mvForecasts_E2$num_pred <- as.numeric(mvForecasts_E2$num_pred)
mvForecasts_E2$num_pred_without_temp <- as.numeric(mvForecasts_E2$num_pred_without_temp)
mvForecasts_E2$RMSE <- as.numeric(mvForecasts_E2$RMSE)
mvForecasts_E2$k <- as.numeric(mvForecasts_E2$k)
for(i in predictors){  mvForecasts_E2[,i] <- as.logical(mvForecasts_E2[,i])}

save(mvForecasts_E2, file = here("Data/Multiview_forecast_data/mvForecasts_E2.RData"))
```


```{r multiview_forecast_analysis_E4, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
##############################################################
## Species forecasting 

# First some preparation:
ks <- unique(round(exp(seq(log(0.8),log(100.4),length.out = 33))))

possible_predictors <- c("bacteria","chlamydomonas_reinhardtii","colpidium_striatum",
                         "dexiostomata_campylum", "didinium_nasutum",
                         "euglena_gracilis","euplotes_daidaleos","paramecium_caudatum",
                         "rotifer_sp","big_white_particle","dissolved_oxygen",
                         "green_white_particle", "small_white_particle")
 
dd2 <- dd2 %>% ungroup()
set.seed(54)
which=c(1,2,3,4,6,8,10,13)
predictor_combinations <- predictor_combinator(possible_predictors, which=which)

mvForecasts_list_E4 <- lapply(targets, function(target){
  df1 <- model_fitter_wrapper(whole.data = dd2, 
                              predictor_combinations = predictor_combinations,
                              target = target,
                              num.clusters = detectCores()-2, 
                              E = 4, max_lag = 3, k=ks)
})

mvForecasts_E4 <- do.call("rbind", mvForecasts_list_E4)

predictors <- c(possible_predictors,"temperature")
mvForecasts_E4$predictor_combination <- as.character(mvForecasts_E4$predictor_combination)
temp <- matrix(F, nrow = nrow(mvForecasts_E4), ncol = length(predictors))
colnames(temp) <- predictors
mvForecasts_E4 <- cbind(mvForecasts_E4,temp)

mvForecasts_E4 <- as.data.frame(t(apply(mvForecasts_E4, 1, function(row) { 
  str <- unlist(strsplit(row["predictor_combination"], " "))
  row[str] <- T
  row
})))

mvForecasts_E4$num_pred <- as.numeric(mvForecasts_E4$num_pred)
mvForecasts_E4$num_pred_without_temp <- as.numeric(mvForecasts_E4$num_pred_without_temp)
mvForecasts_E4$RMSE <- as.numeric(mvForecasts_E4$RMSE)
mvForecasts_E4$k <- as.numeric(mvForecasts_E4$k)
for(i in predictors){  mvForecasts_E4[,i] <- as.logical(mvForecasts_E4[,i])}

save(mvForecasts_E4, file = here("Data/Multiview_forecast_data/mvForecasts_E4.RData"))
```


```{r E_sensitivity_plot_prep, message=FALSE, cache=TRUE, warning=FALSE}
load(here("Data/Multiview_forecast_data/mvForecasts_E2.RData"))
load(here("Data/Multiview_forecast_data/mvForecasts_E4.RData"))

load(here("Data/Multiview_forecast_data/mvForecasts_interactorsAsPredictors_E2.RData")) # done previously
load(here("Data/Multiview_forecast_data/mvForecasts_interactorsAsPredictors_E4.RData")) # done previously

mvForecasts_interactorsAsPredictors_E2$E <- 2
mvForecasts_interactorsAsPredictors_E4$E <- 4


mvForecasts_E2$E <- 2
mvForecasts_E4$E <- 4

mvForecast <- full_join(mvForecasts_E2,mvForecasts_E4)

mvForecast$temperature_included <- as.logical(mvForecast$temperature_included)
mvForecast$target_excluded <- as.logical(mvForecast$target_excluded)
mvForecast <- full_join(mvForecast, mvForecasts_interactorsAsPredictors_E2)
mvForecast <- full_join(mvForecast, mvForecasts_interactorsAsPredictors_E4)
mvForecast <- mvForecast %>%
	na.omit() %>%
	group_by(ID, treat, Target,E) %>%
	mutate(best_rmse_bool = RMSE==min(RMSE),
				 min_rmse = min(RMSE)) %>%
	mutate(RMSE_equi = case_when(abs(RMSE-min_rmse)/((RMSE+min_rmse)/2) <= 0.01 ~ T,
															 abs(RMSE-min_rmse)/((RMSE+min_rmse)/2) > 0.01 ~ F))

mvForecast_best_allEs <- mvForecast %>% 
	dplyr::filter(RMSE_equi==T) %>%
	group_by(ID, treat, Target, E) %>%
	slice_min(num_pred,n=1) %>%
	slice_min(RMSE,n=1) %>% 
	sample_n(1)

mvForecast_best_allEs <- full_join(mvForecast_best_allEs, dd_smap_params_abs) 
mvForecast_best_allEs$Target <- label[mvForecast_best_allEs$Target]

mvForecast_best_allEs <- ddrq1_best_suppl %>%
	mutate(E=3) %>%
	full_join(mvForecast_best_allEs)



mvForecast_best_allEs$Treat <- ifelse(mvForecast_best_allEs$treat=="const",
														 "Constant temperature","Fluctuating temperature")

mvForecast_best_allEs$E_char <- paste("E =", mvForecast_best_allEs$E)


rm(mvForecasts_interactorsAsPredictors, mvForecasts_interactorsAsPredictors_E4, mvForecasts_interactorsAsPredictors_E2)

#--------------------------------------

rq1_list <- rq1_fct(dd_smap, mvForecasts_E2)
ddrq1_fig1_E2 <- rq1_list[[1]]
newdat_E2 <- rq1_list[[2]]
tab.rq1.E2 <- rq1_list[[3]]
newdat_E2$E = 2
ddrq1_fig1_E2$E = 2
tab.rq1.E2 <- cbind(E=2,tab.rq1.E2)

rq1_list <- rq1_fct(dd_smap, mvForecasts_E4)
ddrq1_fig1_E4 <- rq1_list[[1]]
newdat_E4 <-  rq1_list[[2]]
tab.rq1.E4 <- rq1_list[[3]]
newdat_E4$E = 4
ddrq1_fig1_E4$E = 4
tab.rq1.E4 <- cbind(E=4,tab.rq1.E4)

ddrq1_fig1_allEs <- full_join(full_join(ddrq1_fig1_E2,ddrq1_fig1_E4),ddrq1_treat_14_theta5)
ddrq1_fig1_allEs$E <- ifelse(is.na(ddrq1_fig1_allEs$E),3,ddrq1_fig1_allEs$E)
newdat_allEs <- full_join(full_join(newdat_E2,newdat_E4),newdat_theta5)
newdat_allEs$E <- ifelse(is.na(newdat_allEs$E),3,newdat_allEs$E)
```

```{r fig1_allEs_prep2, fig.width=13, fig.height=6.5, out.width="95%", cache=TRUE, message=FALSE}
ddrq1_fig1_allEs$treat <- ifelse(ddrq1_fig1_allEs$treat %in%  c("const","Constant"), "Constant","Fluctuating")
ddrq1_fig1_allEs$Target2 <- label[ddrq1_fig1_allEs$Target]

ddrq1_fig1_allEs$E_char <- paste("E =", ddrq1_fig1_allEs$E)
newdat_allEs$E_char <- paste("E =", newdat_allEs$E)

plot_leg_allEs <-
	ddrq1_fig1_allEs %>%
  ggplot(aes(count,RMSE, group=E_char, shape=treat, col=E_char, fill=E_char))+
  geom_point(size=2.5, alpha=0.33) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	standard_theme()+
	theme(legend.position = "right") +
	labs(shape="Temperature", fill= "", col="") 

plot1a_allEs <- ddrq1_fig1_allEs %>%
  ggplot(aes(count,RMSE, group=E_char, shape=treat, col=E_char, fill=E_char))+
  geom_line(data=newdat_allEs %>% dplyr::filter(model=="count"))+
  geom_ribbon(data=newdat_allEs %>% dplyr::filter(model=="count"), aes(ymax=lower.count,ymin=upper.count), alpha=0.2, col=NA) +
  geom_point(size=2.5, alpha=0.33) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
  standard_theme()+
  facet_wrap(~treat)+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank()) +
	labs(x=expression("Number of interactions"~italic(N[T])), y="Forecast error (RMSE)", tag = "A")

plot1b_allEs <- ddrq1_fig1_allEs %>%
  ggplot(aes(mean_mean_abs,RMSE, group=E_char, shape=treat, col=E_char, fill=E_char))+
  geom_line(data=newdat_allEs %>% dplyr::filter(model=="mean_mean_abs"))+
  geom_ribbon(data=newdat_allEs %>% dplyr::filter(model=="mean_mean_abs"), aes(ymax=lower.mean_mean_abs,ymin=upper.mean_mean_abs), alpha=0.2, col=NA) +
  geom_point(size=2.5, alpha=0.33) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
  standard_theme()+
  facet_wrap(~treat)+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank()) +
	labs(x=expression("Mean interaction strength"~italic(mu["T"])), y="Forecast error (RMSE)", tag = "B")

ddrq1_best_suppl$RMSE_E2 <- unlist(mvForecast_best_allEs[mvForecast_best_allEs$E==2,"RMSE"])
ddrq1_best_suppl$RMSE_E4 <- unlist(mvForecast_best_allEs[mvForecast_best_allEs$E==4,"RMSE"])

ddrq1_best_suppl_E234 <- ddrq1_best_suppl %>% pivot_longer(cols = c("RMSE_E2","RMSE_E4")) %>%
  mutate(name=ifelse(name=="RMSE_E2","Best multiview EDM with E=2","Best multiview EDM with E=4")) 
  
cols  <- brewer.pal(3,"Dark2")

plot1c_allEs <-
  ddrq1_best_suppl_E234 %>%
  ggplot(aes(RMSE, value, col=name, fill=name, shape=treat))+
  geom_abline(slope = 1, intercept = 0) +
  geom_point(size=2.5, alpha=0.33) +
  scale_fill_manual(values = cols[c(1,3)], aesthetics = c("fill","col"))+
	scale_shape_manual(values=c(21,23))+
  standard_theme()+
  facet_wrap(~treat) +
  theme(legend.position = "none",
        panel.spacing =  unit(0, "lines"),
        strip.text.x = element_blank()) +
	labs(x="Lowest RMSE of model with respective E", y="Lowest RMSE of model with E=3", tag = "C")
  

plot_leg_allEs <- get_legend(plot_leg_allEs)

plot1_allEs <- plot1a_allEs+plot1b_allEs+plot1c_allEs+ plot_leg_allEs + plot_layout(ncol = 2)
rm(plot1a_allEs, plot1b_allEs, plot1c_allEs, plot_leg_allEs)
```


## Species interactions robustness analyses

### Sensitivity analysis for $\theta$

```{r smap_models_sensitivity, message=FALSE, warning=FALSE, cache=TRUE}
load(here("Data/CCM_analysis_data/pairwise_ccm_df_list_transf_resid.RData")) # loaded again, same as above
pairwise_ccm_df <- do.call("rbind",pairwise_ccm_df_list)

significant_pairwise_ccm_df <- pairwise_ccm_df %>%
	dplyr::filter(significances<0.05, rho >0)
 
list_smap <- lapply(targets, function(x){
  SMapInteractions(Target = x, num.clusters.target = 1, 
                   num.clusters.CV = NULL, method = "SMap", 
                   data = dd2, long_format = T, theta = 3, 
                   ccm_df = significant_pairwise_ccm_df)
})

dd_smap3 <- do.call("rbind", list_smap) %>%
  dplyr::filter(!(treat=="const" & interactor=="temperature"),
                Interaction!="C0")

list_smap <- lapply(targets, function(x){
  SMapInteractions(Target = x, num.clusters.target = 1, 
                   num.clusters.CV = NULL, method = "SMap", 
                   data = dd2, long_format = T, theta = 7, 
                   ccm_df = significant_pairwise_ccm_df)
})

dd_smap7 <- do.call("rbind", list_smap) %>%
  dplyr::filter(!(treat=="const" & interactor=="temperature"),
                Interaction!="C0")

#### theta = 3
rq1_list_theta3 <- rq1_fct(dd_smap3, ddrq1)

ddrq1_treat_14_theta3 <- rq1_list_theta3[[1]]
newdat_theta3 <- rq1_list_theta3[[2]]
tab.rq1.theta3 <- rq1_list_theta3[[3]]
newdat_theta3$theta = 3
ddrq1_treat_14_theta3$theta = 3
tab.rq1.theta3 <- cbind(theta=3,tab.rq1.theta3)

#### theta = 7

rq1_list_theta7 <- rq1_fct(dd_smap7, ddrq1)

ddrq1_treat_14_theta7 <- rq1_list_theta7[[1]]
newdat_theta7 <- rq1_list_theta7[[2]]
tab.rq1.theta7 <- rq1_list_theta7[[3]]
newdat_theta7$theta = 7
ddrq1_treat_14_theta7$theta = 7
tab.rq1.theta7 <- cbind(theta=7,tab.rq1.theta7)

rm(dd_smap3, dd_smap7, list_smap, rq1_list_theta3, rq1_list_theta7)
```

```{r smap_models_sensitivity2, message=FALSE, warning=FALSE, cache=TRUE}
ddrq1_treat_14_thetas <- rbind(ddrq1_treat_14_theta3, ddrq1_treat_14_theta5, ddrq1_treat_14_theta7)
ddrq1_treat_14_thetas$theta <- as.factor(ddrq1_treat_14_thetas$theta)
ddrq1_treat_14_thetas$treat <- ifelse(ddrq1_treat_14_thetas$treat %in% c("const","Constant"),
																			"Constant","Fluctuating")

newdat_thetas <- rbind(newdat_theta3, newdat_theta5, newdat_theta7)
newdat_thetas$theta <- as.factor(newdat_thetas$theta)

ddrq1_treat_14_thetas$theta2 <- ifelse(ddrq1_treat_14_thetas$theta==3, "Theta = 3",
																			 ifelse(ddrq1_treat_14_thetas$theta==5, "Theta = 5","Theta = 7"))
newdat_thetas$theta2 <- ifelse(newdat_thetas$theta==3, "Theta = 3",
																			 ifelse(newdat_thetas$theta==5, "Theta = 5","Theta = 7"))

rm(ddrq1_treat_14_theta3, ddrq1_treat_14_theta7, newdat_theta3, newdat_theta5, newdat_theta7)

thetaplot1 <- ddrq1_treat_14_thetas %>%
  ggplot(aes(mean_mean_abs,RMSE, shape=treat, col=theta2, fill=theta2))+
  facet_wrap(~treat)+
  geom_line(data=newdat_thetas %>% dplyr::filter(model=="mean_mean_abs")) +
  geom_ribbon(data=newdat_thetas %>% dplyr::filter(model=="mean_mean_abs"),
  						aes(ymax=lower.mean_mean_abs,ymin=upper.mean_mean_abs), alpha=0.2, col=NA) +
  geom_point(size=1.2, alpha=0.33) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("col","fill"))+
  standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	labs(x="Mean interaction strength", y="RMSE", tag = "A")

thetaplot2 <- ddrq1_treat_14_thetas %>%
  ggplot(aes(count, mean_mean_abs, shape=treat, col=theta2, fill=theta2))+
  geom_line(data=newdat_thetas %>% dplyr::filter(model=="corr"))+
  geom_ribbon(data=newdat_thetas %>% dplyr::filter(model=="corr"), aes(ymax=lower.corr,ymin=upper.corr), alpha=0.2, col=NA) +
  geom_point(size=1.2, alpha=0.33) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("col","fill"))+
	standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat) + 
	labs(x="Number of interactions", y="Mean interaction strength", tag = "B")

thetaplot3 <- ddrq1_treat_14_thetas %>%
  ggplot(aes(sum_mean_abs,RMSE, shape=treat, col=theta2, fill=theta2))+
  geom_line(data=newdat_thetas %>% dplyr::filter(model=="iso"))+
  geom_ribbon(data=newdat_thetas %>% dplyr::filter(model=="iso"), aes(ymax=lower.iso,ymin=upper.iso), alpha=0.2, col=NA) +
  geom_point(size=1.2, alpha=0.33) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("col","fill"))+
	standard_theme()+
	theme(legend.position = "right",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat)+
	labs(x="Sum of interaction strengths", y="RMSE", tag = "C",
	     shape="Temperature", col="", fill="")
```


### Using Regularized S-map

The following code chunk is not run. The results are loaded in after it.

```{r RegSmap, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
##############################################################
## Species interactions

# Load number of interactions
load(here("Data/CCM_analysis_data/pairwise_ccm_df_list_transf_resid.RData")) 
pairwise_ccm_df <- do.call("rbind",pairwise_ccm_df_list)

significant_pairwise_ccm_df <- pairwise_ccm_df %>%
	dplyr::filter(significances<0.05, rho >0)


logspace <- function(d1, d2, n) exp(log(10)*seq(d1, d2, length.out=n)) 
thetas <- c(0.01, 0.1, 0.3, 0.5, 0.75, 1, 1.5, 2, 3, 4, 5, 6, 7, 8, 9)

### Tikhonov (alpha=1)

grid <- expand.grid(tht=thetas,
                    lambda=logspace(-3,0,30),
                    alpha=1)

# calculation of interactions 
list_Regsmap <- lapply(targets, function(x){
  SMapInteractions(Target = x, num.clusters.target = 1, 
                   num.clusters.CV = detectCores()-1, 
                   data = dd2, 
                   long_format = T, method = "RegSMap", 
                   grid = grid,
                   ccm_df = significant_pairwise_ccm_df, 
                   RegressionType = "ELNET_fit", 
                   Regression.Kernel = "Exponential.Kernel")
})

dd_Regsmap_tikhonov <- do.call("rbind", list_Regsmap) %>%
  dplyr::filter(!(treat=="const" & interactor=="temperature"),
                Interaction!="C0")

dd_Regsmap_tikhonov$method <- "tikhonov"

### ELNET with alpha=0.9

grid <- expand.grid(tht=thetas,
                    lambda=logspace(-3,0,30),
                    alpha=0.9)

# calculation of interactions 
list_Regsmap <- lapply(targets, function(x){
  SMapInteractions(Target = x, num.clusters.target = 1, 
                   num.clusters.CV = detectCores()-1, 
                   data = dd2, 
                   long_format = T, method = "RegSMap", 
                   grid = grid,
                   ccm_df = significant_pairwise_ccm_df, 
                   RegressionType = "ELNET_fit", 
                   Regression.Kernel = "Exponential.Kernel")
})

dd_Regsmap_ELNET0.9 <- do.call("rbind", list_Regsmap) %>%
  dplyr::filter(!(treat=="const" & interactor=="temperature"),
                Interaction!="C0")

dd_Regsmap_ELNET0.9$method <- "ELNET0.9"


### Ridge regression (no alpha)

grid <- expand.grid(tht=thetas,
                    lambda=logspace(-3,0,30),
                    alpha=1)

# calculation of interactions 
list_Regsmap <- lapply(targets, function(x){
  SMapInteractions(Target = x, num.clusters.target = 1, 
                   num.clusters.CV = detectCores()-1, 
                   data = dd2, 
                   long_format = T, method = "RegSMap", 
                   grid = grid,
                   ccm_df = significant_pairwise_ccm_df, 
                   RegressionType = "ridge_fit", 
                   Regression.Kernel = "Exponential.Kernel")
})

dd_Regsmap_ridge <- do.call("rbind", list_Regsmap) %>%
  dplyr::filter(!(treat=="const" & interactor=="temperature"),
                Interaction!="C0")

dd_Regsmap_ridge$method <- "ridge"


save(dd_Regsmap_tikhonov, file = here("Data/Smap_interaction_data/dd_Regsmap_tikhonov.RData"))
save(dd_Regsmap_ELNET0.9, file = here("Data/Smap_interaction_data/dd_Regsmap_ELNET0.9.RData"))
save(dd_Regsmap_ridge, file = here("Data/Smap_interaction_data/dd_Regsmap_ridge.RData"))
```

```{r fig1_with_regSmap, warning=FALSE, cache=TRUE, message=FALSE, fig.width=9, fig.height=6.5, out.width="95%"}
load(here("Data/Smap_interaction_data/dd_Regsmap_tikhonov.RData"))
load(here("Data/Smap_interaction_data/dd_Regsmap_ELNET0.9.RData"))
load(here("Data/Smap_interaction_data/dd_Regsmap_ridge.RData"))

cmult <- 1.96

## Reg: ridge regression
rq1_list_ridge <- rq1_fct(dd_Regsmap_ridge, ddrq1)
ddrq1_treat_14_ridge <- rq1_list_ridge[[1]]
newdat_ridge <- rq1_list_ridge[[2]]
tab.rq1.ridge <- rq1_list_ridge[[3]]
dd_smap_params_abs_ridge <- rq1_list_ridge[[4]] 
ddrq1_treat_14_ridge$regularization <- "Ridge regression"
newdat_ridge$regularization <- "Ridge regression"

## Reg: tikhonov
rq1_list_tikhonov <- rq1_fct(dd_Regsmap_tikhonov, ddrq1)
ddrq1_treat_14_tikhonov <- rq1_list_tikhonov[[1]]
newdat_tikhonov <- rq1_list_tikhonov[[2]]
tab.rq1.tikhonov <- rq1_list_tikhonov[[3]]
dd_smap_params_abs_tikhonov <- rq1_list_tikhonov[[4]]
ddrq1_treat_14_tikhonov$regularization <- "Tikhonov"
newdat_tikhonov$regularization <- "Tikhonov"

## Reg: elnet 0.9
rq1_list_ELNET0.9 <- rq1_fct(dd_Regsmap_ELNET0.9, ddrq1)
ddrq1_treat_14_ELNET0.9 <- rq1_list_ELNET0.9[[1]]
newdat_ELNET0.9 <- rq1_list_ELNET0.9[[2]]
tab.rq1.ELNET0.9 <- rq1_list_ELNET0.9[[3]]
dd_smap_params_abs_ELNET0.9 <- rq1_list_ELNET0.9[[4]]
ddrq1_treat_14_ELNET0.9$regularization <- "ELNET0.9"
newdat_ELNET0.9$regularization <- "ELNET0.9"

ddrq1_treat_14_regsmap <- rbind(ddrq1_treat_14_ELNET0.9,
                                ddrq1_treat_14_tikhonov,
                                ddrq1_treat_14_ridge)
newdat_regsmap <- rbind(newdat_ELNET0.9,
                        newdat_tikhonov,
                        newdat_ridge)

ddrq1_treat_14_regsmap$treat <- ifelse(ddrq1_treat_14_regsmap$treat=="const","Constant","Fluctuating")
ddrq1_treat_14_regsmap$Target2 <- label[ddrq1_treat_14_regsmap$Target]

plot_leg_regsmap <-
	ddrq1_treat_14_regsmap %>%
	ggplot(aes(mean_mean_abs,RMSE, group=treat, shape=treat, fill=regularization, col=regularization))+
	geom_point(size=2.5)+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	standard_theme()+
	theme(legend.position = "right", legend.box="vertical",
				legend.text = ggtext::element_markdown()) +
	labs(shape="Temperature", fill= "Regularization", col="Regularization") +
	guides(fill=guide_legend(nrow=8,byrow=TRUE), shape=guide_legend(nrow=2,byrow=TRUE))

plotregsmap1 <- ddrq1_treat_14_regsmap %>%
  ggplot(aes(mean_mean_abs,RMSE, shape=treat, fill=regularization, col=regularization))+
  geom_line(data=newdat_regsmap %>% dplyr::filter(model=="mean_mean_abs"))+
  geom_ribbon(data=newdat_regsmap %>% dplyr::filter(model=="mean_mean_abs"),
              aes(ymax=lower.mean_mean_abs,ymin=upper.mean_mean_abs), alpha=0.2, col=NA) +
  geom_point(size=2.5, alpha=0.33)+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
  standard_theme()+
  facet_wrap(~treat)+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	labs(x=expression("Mean interaction strength"~italic(mu["T"])), y="Forecast error (RMSE)", tag = "A")

plotregsmap2 <- ddrq1_treat_14_regsmap %>%
  ggplot(aes(count, mean_mean_abs, shape=treat, fill=regularization, col=regularization))+
  geom_line(data=newdat_regsmap %>% dplyr::filter(model=="corr"))+
  geom_ribbon(data=newdat_regsmap %>% dplyr::filter(model=="corr"), 
              aes(ymax=lower.corr,ymin=upper.corr), alpha=0.2, col=NA) +
  geom_point(size=2.5, alpha=0.33)+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat) +
	labs(x=expression("Number of interactions"~italic(N[T])),
			 y=expression("Mean interaction strength"~italic(mu["T"])), tag = "B")

plot_leg_regsmap <- get_legend(plot_leg_regsmap)
```

## General robustness analyses

### Excluding Euglena gracilis

```{r smap_models_euglena, message=FALSE, warning=FALSE, cache=TRUE}
load(here("Data/CCM_analysis_data/pairwise_ccm_df_list_transf_resid.RData")) # loaded again, see above
pairwise_ccm_df <- do.call("rbind",pairwise_ccm_df_list) %>%
	dplyr::filter(target!="euglena_gracilis")

significant_pairwise_ccm_df <- pairwise_ccm_df %>%
	dplyr::filter(significances<0.05, rho >0)
 
list_smap <- lapply(targets, function(x){
  SMapInteractions(Target = x, num.clusters.target = 1, 
                   num.clusters.CV = NULL, method = "SMap", 
                   data = dd2, long_format = T, theta = 5, 
                   ccm_df = significant_pairwise_ccm_df)
})

dd_smap_euglena <- do.call("rbind", list_smap) %>%
  dplyr::filter(!(treat=="const" & interactor=="temperature"),
                Interaction!="C0")


rq1_list_euglena <- rq1_fct(dd_smap = dd_smap_euglena %>% dplyr::filter(target!="euglena_gracilis"), 
														ddrq1 = ddrq1 %>% dplyr::filter(Target!="euglena_gracilis"),
														permutation_entropies.dd = permutation_entropies %>% dplyr::filter(Target!="euglena_gracilis"),
														cv.dd = cv %>% dplyr::filter(Target!="euglena_gracilis"))

ddrq1_treat_14_euglena <- rq1_list_euglena[[1]]
newdat_euglena <- rq1_list_euglena[[2]]
tab.rq1.euglena <- rq1_list_euglena[[3]]
ddrq1_treat_14_euglena$treat <- ifelse(ddrq1_treat_14_euglena$treat=="const","Constant","Fluctuating")
ddrq1_treat_14_euglena$Target2 <- label[ddrq1_treat_14_euglena$Target]
newdat_euglena$robust <- "Without euglena"
ddrq1_treat_14_euglena$robust <- "Without euglena"

tab.rq1.euglena <- tab.rq1.euglena[1:15,]

rm(dd_smap_euglena, list_smap, rq1_model_fcts_list)
```


### Estimating all possible species interactions

```{r smap_models_all_interactors, message=FALSE, warning=FALSE, cache=TRUE}
load(here("Data/CCM_analysis_data/pairwise_ccm_df_list_transf_resid.RData")) # loaded again, same as above
pairwise_ccm_df <- do.call("rbind",pairwise_ccm_df_list)

list_smap <- lapply(targets, function(x){
    SMapInteractions(Target = x, num.clusters.target = 1, 
                   num.clusters.CV = NULL, method = "SMap", 
                   data = dd2, long_format = T, theta = 5, 
                   ccm_df = pairwise_ccm_df)
})

dd_smap_all_interaction <- do.call("rbind", list_smap) %>%
  dplyr::filter(!(treat=="const" & interactor=="temperature"),
                Interaction!="C0")

rq1_list_all_interactions <- rq1_fct(dd_smap_all_interaction, ddrq1, count=F, table=F, corr=F)

ddrq1_treat_all_interactions  <- rq1_list_all_interactions[[1]]
newdat_all_interactions  <- rq1_list_all_interactions[[2]]

ddrq1_treat_all_interactions$treat <- ifelse(ddrq1_treat_all_interactions$treat=="const","Constant","Fluctuating")
ddrq1_treat_all_interactions$Target2 <- label[ddrq1_treat_all_interactions$Target]
newdat_all_interactions$robust <- "All interactions considered"
ddrq1_treat_all_interactions$robust <- "All interactions considered"

Covariates <- c("Fluctuating temperature","Interaction","Bottle ID")
m.mean_mean_abs <- lmer(RMSE~mean_mean_abs*treat + (1|ID), data = ddrq1_treat_all_interactions)
tab_all_interactions <- data.frame(Response = rep(c("RMSE"), each=5),
																	 Covariate = c("Intercept","Mean interaction strength",Covariates),
																	 Type = c("Fixed","Fixed","Fixed","Fixed","Std. Dev."),
																	 Coefficient = c(fixef(m.mean_mean_abs),as.data.frame(VarCorr(m.mean_mean_abs))$sdcor[1]),
																	 Std.err = c(summary(m.mean_mean_abs)$coef[, 2, drop = FALSE],NA),
																	 Test = c(rep("\\textit{t}",4),"$\\chi^2$"),
																	 Test.value = c(summary(m.mean_mean_abs)$coef[, 4, drop = FALSE],lmerTest::rand(m.mean_mean_abs)$LRT[2]),
																	 p.value = c(summary(m.mean_mean_abs)$coef[, 5, drop = FALSE],lmerTest::rand(m.mean_mean_abs)$`Pr(>Chisq)`[2]))
rownames(tab_all_interactions) <- 1:nrow(tab_all_interactions)

rm(dd_smap_all_interaction, list_smap, rq1_list_all_interactions)
```


### Partitioning the data for forecasts and species interactions

The following 2 code chunks are not run. Instead the results are loaded in the chunk after.

```{r multiview_forecast_analysis_partitioned, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
possible_predictors <- c("bacteria","chlamydomonas_reinhardtii","colpidium_striatum",
                         "dexiostomata_campylum", "didinium_nasutum",
                         "euglena_gracilis","euplotes_daidaleos","paramecium_caudatum",
                         "rotifer_sp","big_white_particle","dissolved_oxygen",
                         "green_white_particle", "small_white_particle")

predictor_combinations <- list(c(possible_predictors,"temperature"))

ks <- unique(round(exp(seq(log(0.8),log(100.4),length.out = 33))))
# ks <- 1:2

lib <- "1 33"
pred <- "34 66"

ddrq1_partitioned_list <- lapply(targets, function(target){
  df1 <- model_fitter_wrapper(whole.data = dd2, 
                              predictor_combinations =  predictor_combinations,
                              target = target,
                              num.clusters = detectCores() - 1, 
                              E = 3, max_lag = 3, k=ks, 
  														lib = lib, pred = pred)
})

ddrq1_partitioned <- do.call("rbind", ddrq1_partitioned_list)

predictors <- c(possible_predictors,"temperature")
ddrq1_partitioned$predictor_combination <- as.character(ddrq1_partitioned$predictor_combination)
temp <- matrix(F, nrow = nrow(ddrq1_partitioned), ncol = length(predictors))
colnames(temp) <- predictors
ddrq1_partitioned <- cbind(ddrq1_partitioned,temp)

ddrq1_partitioned <- as.data.frame(t(apply(ddrq1_partitioned, 1, function(row) { 
  str <- unlist(strsplit(row["predictor_combination"], " "))
  row[str] <- T
  row
})))

ddrq1_partitioned$num_pred <- as.numeric(ddrq1_partitioned$num_pred)
ddrq1_partitioned$num_pred_without_temp <- as.numeric(ddrq1_partitioned$num_pred_without_temp)
ddrq1_partitioned$RMSE <- as.numeric(ddrq1_partitioned$RMSE)
ddrq1_partitioned$k <- as.numeric(ddrq1_partitioned$k)
for(i in predictors){  ddrq1_partitioned[,i] <- as.logical(ddrq1_partitioned[,i])}

save(ddrq1_partitioned, file = here("Data/Multiview_forecast_data/ddrq1_transf_resid_partitioned.RData"))
```


```{r interactors_used_as_predictors_partitioned, cache=TRUE, message=FALSE, eval=FALSE}
##############################################################
### trim (for partition)

dd2_partitioned <- dd2 %>%
  dplyr::group_by(ID) %>%
  dplyr::slice(34:66)

interactors <- colnames(dd2_partitioned[,-c(1:7)])
var_pairs <- expand.grid(target=targets, interactors=interactors)

dd2_dflist <- split(dd2_partitioned, dd2_partitioned$ID)

pairwise_ccm_df_list <- mclapply(dd2_dflist, function(df){
	dftemp <- df[,-c(1,3:7)]
	Best_E_df <- apply(var_pairs,1, function(c){
		best_E_fct_trimmed(dftemp,c[1],c[2])
	})
	
	Best_E_df <- do.call("rbind",Best_E_df)
	Best_E_df$ID <- unique(df$ID)
	Best_E_df$treat <- unique(df$treat)
	Best_E_df$treat2 <- unique(df$treat2)
	Best_E_df$treat3 <- unique(df$treat3)
	
	rhos <- apply(Best_E_df, 1, function(r){
		ccm_out <- CCM(dataFrame = dftemp, target = r[1], column = r[2],
									 libSizes = "9 29 4", Tp = 0, E = as.numeric(r[3]), sample = 100)
		rho <- ccm_out[6,3]
		if(rho<0) return(data.frame(rho=rho,comment="negative"))
		slope <- lm(ccm_out[,3] ~ seq(9,29,by = 4))$coefficients[2]
		if(slope>=0) {return(data.frame(rho=rho,comment="converged"))
		} else {return(data.frame(rho=rho,comment="not converged"))}
	})
	
	Best_E_df <- cbind(Best_E_df,do.call("rbind",rhos))
	
	rho_df <- Best_E_df %>%
		dplyr::filter(target %in% targets, comment=="converged")
	
	significances <- apply(rho_df, 1, function(r){
		ts <- unlist(df[,as.character(r[2])])
		# target <- r[2]
		surr_interactor = SurrogateData(ts, method = "random_shuffle",
																		num_surr = 1000, alpha = 3)
		
		rho_surr <- data.frame(interactor_rho = numeric(1000))
		
		interactor_data = as.data.frame(cbind(df$day, ts, surr_interactor))
		names(interactor_data) = c("day", r[1], paste("T", as.character(seq(1, 1000)),	sep = ""))
		
		for (i in 1:1000) {
			targetCol = paste("T", i, sep = "") 
			ccm_out = CCM(dataFrame = interactor_data, E = as.numeric(r[3]), Tp = 0, columns = r[1],
										target = targetCol, libSizes = "29 29 10", sample = 1)
			col = paste(r[1], ":", targetCol, sep = "")
			rho_surr$interactor_rho[i] = ccm_out[1, col]
		}
		1 - ecdf(rho_surr$interactor_rho)(as.numeric(r["rho"]))
	})
	
	rho_df$significances <- significances
	pairwise_ccm_df <- full_join(Best_E_df,rho_df)
	pairwise_ccm_df
}, mc.cores = detectCores()-2)

save(pairwise_ccm_df_list, file = here("Data/CCM_analysis_data/pairwise_ccm_df_list_transf_resid_trimmed.RData"))
```


```{r multiview_forecast_analysis_partitioned_part2, message=FALSE, warning=FALSE, cache=TRUE}
load(here("Data/Multiview_forecast_data/ddrq1_transf_resid_partitioned.RData")) 
load(here("Data/CCM_analysis_data/pairwise_ccm_df_list_transf_resid_trimmed.RData")) 
pairwise_ccm_df_trimmed <- do.call("rbind",pairwise_ccm_df_list)

significant_pairwise_ccm_df_trimmed <- pairwise_ccm_df_trimmed %>%
	dplyr::filter(significances<0.05, rho >0)

# calculation of interactions 
list_smap <- lapply(targets, function(x){
      SMapInteractions(Target = x, num.clusters.target = 1, 
                   num.clusters.CV = NULL, method = "SMap", 
                   data = dd2, long_format = T, theta = 5, 
                   ccm_df = significant_pairwise_ccm_df_trimmed)
})

dd_smap_trimmed <- do.call("rbind", list_smap) %>%
  dplyr::filter(!(treat=="const" & interactor=="temperature"),
                Interaction!="C0")

significant_pairwise_ccm_df_trimmed$Target2 <- label[significant_pairwise_ccm_df_trimmed$target]

num_int_plot2 <- significant_pairwise_ccm_df_trimmed %>%
	na.omit() %>% 
	ggplot(aes(ID, fill=Target2)) +
	geom_bar(position = "identity")+
	facet_wrap(~Target2, ncol = 4)+
	standard_theme2() +
	scale_fill_brewer(palette="Dark2")+
	labs(x="Bottle ID", y="Number of interactions") +
	theme(strip.text = ggtext::element_markdown(),
				axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

rq1_list_trimmed <- rq1_fct(dd_smap_trimmed, ddrq1_partitioned)
ddrq1_treat_14_partitioned <- rq1_list_trimmed[[1]]
newdat_partitioned <- rq1_list_trimmed[[2]]
tab.rq1.partitioned <- rq1_list_trimmed[[3]]
tab.rq1.partitioned <- tab.rq1.partitioned[1:15,]

newdat_partitioned$robust <- "Partitioned data"
ddrq1_treat_14_partitioned$robust <- "Partitioned data"
ddrq1_treat_14_partitioned$treat <- ifelse(ddrq1_treat_14_partitioned$treat=="const","Constant","Fluctuating")

rm(rq1_list_all_interactions, rq1_list_all_interactions, list_smap)
```


### Taking the mean of the absolute values of the mean interaction strengths

```{r mean_abs_mean, message=FALSE, warning=FALSE, cache=TRUE}
ddrq1_treat_14_theta5_mean_abs_mean <- ddrq1_treat_14_theta5
ddrq1_treat_14_theta5_mean_abs_mean$mean_mean_abs <- ddrq1_treat_14_theta5_mean_abs_mean$mean_abs_mean

rq1_list_mean_abs_mean <- rq1_model_fcts(ddrq1_treat_14_theta5_mean_abs_mean)
newdat_mean_abs_mean  <- rq1_list_mean_abs_mean[[1]]
tab_mean_abs_mean <- rq1_list_mean_abs_mean[[2]]
tab_mean_abs_mean <- tab_mean_abs_mean[6:10,]
tab_mean_abs_mean[2,2] <- "Mean(abs(mean(IS)))"

ddrq1_treat_14_theta5_mean_abs_mean$treat <- ifelse(ddrq1_treat_14_theta5_mean_abs_mean$treat=="const","Constant","Fluctuating")
ddrq1_treat_14_theta5_mean_abs_mean$Target2 <- label[ddrq1_treat_14_theta5_mean_abs_mean$Target]
newdat_mean_abs_mean$robust <- "Mean(abs(mean(interaction TS)))"
ddrq1_treat_14_theta5_mean_abs_mean$robust <- "Mean(abs(mean(interaction TS)))"

rm(rq1_list_mean_abs_mean)
```


### Robustness analyses taken together

```{r robust_plot_calc, message=FALSE, warning=FALSE, cache=TRUE}
newdat_robust <- full_join(newdat_euglena, 
                           full_join(newdat_all_interactions, 
													 										full_join(newdat_partitioned, newdat_mean_abs_mean)))

ddrq1_treat_14_euglena$temperature_included <- as.logical(ddrq1_treat_14_euglena$temperature_included)
ddrq1_treat_14_euglena$target_excluded <- as.logical(ddrq1_treat_14_euglena$target_excluded)
ddrq1_treat_all_interactions$temperature_included <- as.logical(ddrq1_treat_all_interactions$temperature_included)
ddrq1_treat_all_interactions$target_excluded <- as.logical(ddrq1_treat_all_interactions$target_excluded)
ddrq1_treat_14_partitioned$temperature_included <- as.logical(ddrq1_treat_14_partitioned$temperature_included)
ddrq1_treat_14_partitioned$target_excluded <- as.logical(ddrq1_treat_14_partitioned$target_excluded)
ddrq1_treat_14_theta5_mean_abs_mean$temperature_included <- as.logical(ddrq1_treat_14_theta5_mean_abs_mean$temperature_included)
ddrq1_treat_14_theta5_mean_abs_mean$target_excluded <- as.logical(ddrq1_treat_14_theta5_mean_abs_mean$target_excluded)
ddrq1_treat_14_robust <- rbind(ddrq1_treat_14_euglena, ddrq1_treat_all_interactions, ddrq1_treat_14_partitioned,ddrq1_treat_14_theta5_mean_abs_mean)

rm(newdat_euglena,newdat_all_interactions,newdat_partitioned,newdat_mean_abs_mean,
	 ddrq1_treat_14_euglena,ddrq1_treat_all_interactions,ddrq1_treat_14_partitioned,ddrq1_treat_14_theta5_mean_abs_mean)

ddrq1_treat_14_robust$robust <- as.factor(ddrq1_treat_14_robust$robust)
newdat_robust$robust <- as.factor(newdat_robust$robust)
robust_levels <- levels(ddrq1_treat_14_robust$robust)
# names(robust_levels) <- c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00')
names(robust_levels) <- brewer.pal(4,"Dark2")

tab_mean_abs_mean <- cbind(Robust="Mean(abs(mean(IS)))",tab_mean_abs_mean)
tab.rq1.partitioned <- cbind(Robust="Partitioned data",tab.rq1.partitioned)
tab_all_interactions <- cbind(Robust="All interactions",tab_all_interactions)
tab_all_interactions$Response <- "RMSE\n"
tab.rq1.euglena <- cbind(Robust="Without Euglena",tab.rq1.euglena)

tab.robust <- rbind(tab.rq1.euglena,tab_all_interactions,tab_mean_abs_mean,tab.rq1.partitioned)

plot.robust1 <- ddrq1_treat_14_robust %>%
	dplyr::filter(robust %in% c("Partitioned data","Without euglena")) %>%
  ggplot(aes(count,RMSE, shape=treat, col=robust, fill=robust))+
  facet_wrap(~treat)+
  geom_ribbon(data=newdat_robust %>% dplyr::filter(model=="count",
  																								 robust %in% c("Partitioned data","Without euglena")),
  						aes(ymax=lower.count,ymin=upper.count), alpha=0.2, col=NA) +
  geom_point(size=1.2, alpha=0.33) +
  geom_line(data=newdat_robust %>% dplyr::filter(model=="count",
  																							 robust %in% c("Partitioned data","Without euglena")), 
            size=1.2) +	
	scale_shape_manual(values=c(21,23))+
	scale_fill_manual(values = names(robust_levels), 
										breaks = robust_levels, 
										aesthetics = c("col","fill")) +  
  standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	labs(x="Number of interactions", y="RMSE", tag = "A")


plot.robust2 <- ddrq1_treat_14_robust %>%
  ggplot(aes(mean_mean_abs,RMSE, shape=treat, col=robust, fill=robust))+
  facet_wrap(~treat)+
  geom_ribbon(data=newdat_robust %>% dplyr::filter(model=="mean_mean_abs"),
  						aes(ymax=lower.mean_mean_abs,ymin=upper.mean_mean_abs), alpha=0.2, col=NA) +
  geom_point(size=1.2, alpha=0.33) +
  geom_line(data=newdat_robust %>% dplyr::filter(model=="mean_mean_abs"), size=1.2) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_manual(values = names(robust_levels), 
										breaks = robust_levels, 
										aesthetics = c("col","fill")) +  
	standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	labs(x="Mean interaction strength", y="RMSE", tag = "B")

plot.robust3 <- ddrq1_treat_14_robust %>%
	dplyr::filter(robust != "All interactions considered") %>%
  ggplot(aes(count, mean_mean_abs, shape=treat, col=robust, fill=robust))+
  geom_ribbon(data=newdat_robust %>% dplyr::filter(model=="corr",robust != "All interactions considered"),
  						aes(ymax=lower.corr,ymin=upper.corr), alpha=0.2, col=NA) +
  geom_point(size=1.2, alpha=0.33) +
  geom_line(data=newdat_robust %>% dplyr::filter(model=="corr",robust != "All interactions considered"),
  					size=1.2)+
	scale_shape_manual(values=c(21,23))+
	scale_fill_manual(values = names(robust_levels), 
										breaks = robust_levels, 
										aesthetics = c("col","fill")) +  
	standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat) + 
	labs(x="Number of interactions", y="Mean interaction strength", tag = "C")

plot.robust.leg <- ddrq1_treat_14_robust %>%
  ggplot(aes(count, mean_mean_abs, shape=treat, col=robust, fill=robust))+
  geom_line(data=newdat_robust %>% dplyr::filter(model=="corr"))+
  geom_ribbon(data=newdat_robust %>% dplyr::filter(model=="corr"), aes(ymax=lower.corr,ymin=upper.corr), alpha=0.2, col=NA) +
  geom_point(size=2, alpha=1) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_manual(values = names(robust_levels), 
										breaks = robust_levels, 
										aesthetics = c("col","fill")) +  
	standard_theme()+
	theme(legend.position = "right",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat) + 
	labs(x="Number of interactions", y="Mean interaction strength", tag = "C", 
			 shape="Temperature", col="", fill="")

plot.robust.leg <- get_legend(plot.robust.leg)
```


### Effects of measurement methods

```{r measurement_method_calc, message=FALSE, warning=FALSE, cache=TRUE}
ddrq1_treat_14_methods <- ddrq1_treat_14_thetas %>%
	dplyr::filter(theta==5) %>%
	dplyr::mutate(Species=target) %>%
	full_join(taxa, by = "Species")

ddrq1_treat_14_methods <- ddrq1_treat_14_methods[1:144,]
ddrq1_treat_14_methods$Target2 <- label[ddrq1_treat_14_methods$Target]

boxplot1 <- ddrq1_treat_14_methods %>%
	ggplot(aes(Measured_with, RMSE)) +
	geom_boxplot() +
	geom_point(aes(col=Target2,fill=Target2, shape=treat), size=2, alpha=0.6) +
	scale_shape_manual(values=c(21,23))+
  facet_wrap(~treat)+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("col","fill")) +
  standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				legend.text = ggtext::element_markdown()) + 
	labs(x="Measurement method", y="RMSE", tag = "A", 
			 shape="Temperature", col="Target", fill="Target") +
	coord_flip()

boxplot2 <- ddrq1_treat_14_methods %>%
	ggplot(aes(Measured_with, count)) +
	geom_boxplot() +
	geom_point(aes(col=Target2,fill=Target2, shape=treat), size=2, alpha=0.6) +
	scale_shape_manual(values=c(21,23))+
  facet_wrap(~treat)+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("col","fill")) +
  standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				legend.text = ggtext::element_markdown())  + 
	labs(x="Measurement method", y="Number of interactions", tag = "B", 
			 shape="Temperature", col="Target", fill="Target")+
	coord_flip()

boxplot3 <- ddrq1_treat_14_methods %>%
	ggplot(aes(Measured_with, mean_mean_abs)) +
	geom_boxplot() +
	geom_point(aes(col=Target2,fill=Target2, shape=treat), size=2, alpha=0.6) +
	scale_shape_manual(values=c(21,23))+
  facet_wrap(~treat)+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("col","fill")) +
  standard_theme()+
	theme(legend.position = "right",
				panel.spacing =  unit(0, "lines"),
				legend.box = "horizontal",
				strip.text.x = element_blank(),
				legend.text = ggtext::element_markdown()) + 
	labs(x="Measurement method", y="Mean interaction strength", tag = "C", 
			 shape="Temperature", col="Target", fill="Target")+
	coord_flip()

boxplot_legend <- get_legend(boxplot3)
boxplot3 <- boxplot3 + theme(legend.position = "none")

ddrq1_treat_14_methods_meas <- ddrq1_treat_14_methods %>%
	group_by(Measured_with,treat) %>%
	summarize(min_count=min(count),
						max_count=max(count),
						min_is=min(mean_mean_abs),
						max_is=max(mean_mean_abs))



newdata.meas <- apply(ddrq1_treat_14_methods_meas, 1, function(row){
	data.frame(count=seq(row["min_count"],row["max_count"],length.out = 100),
						 mean_mean_abs=seq(row["min_is"],row["max_is"],length.out = 100),
						 Measured_with=row["Measured_with"],
						 treat=row["treat"])
})

newdata.meas <- do.call("rbind",newdata.meas)

m.count.meas <- lmer(RMSE~Measured_with*count*treat + (1|ID), data = ddrq1_treat_14_methods)
newdata.meas.count <- newdata.meas
newdata.meas.count$RMSE <- predict(m.count.meas, newdata.meas.count, re.form=NA)
mm.meas.count <- model.matrix(terms(m.count.meas),newdata.meas.count)
pvar1.meas.count <- diag(mm.meas.count %*% tcrossprod(vcov(m.count.meas),mm.meas.count))
newdata.meas.count <- data.frame(newdata.meas.count,
																lower=newdata.meas.count$RMSE-cmult*sqrt(pvar1.meas.count),
																upper=newdata.meas.count$RMSE+cmult*sqrt(pvar1.meas.count))
newdata.meas.count$model <- "count"


meas.plot1 <- ddrq1_treat_14_methods %>%
  ggplot(aes(count,RMSE, shape=treat, col=Measured_with, fill=Measured_with))+
  facet_wrap(~treat)+
  geom_line(data=newdata.meas.count)+
  geom_ribbon(data=newdata.meas.count, aes(ymax=upper,ymin=lower),
  						alpha=0.2, col=NA) +
	geom_point(size=2, alpha=0.6) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("col","fill"))+
  standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown())  + 
	labs(y="RMSE", x="Number of interactions", tag = "A", 
			 shape="Temperature", col="Measured with", fill="Measured with") 


m.is.meas <- lmer(RMSE~Measured_with*mean_mean_abs*treat + (1|ID), data = ddrq1_treat_14_methods)
newdata.meas.is <- newdata.meas
newdata.meas.is$RMSE <- predict(m.is.meas, newdata.meas.is, re.form=NA)
mm.meas.is <- model.matrix(terms(m.is.meas),newdata.meas.is)
pvar1.meas.is <- diag(mm.meas.is %*% tcrossprod(vcov(m.is.meas),mm.meas.is))
newdata.meas.is <- data.frame(newdata.meas.is,
															lower=newdata.meas.is$RMSE-cmult*sqrt(pvar1.meas.is),
															upper=newdata.meas.is$RMSE+cmult*sqrt(pvar1.meas.is))
newdata.meas.is$model <- "is"

meas.plot2 <- ddrq1_treat_14_methods %>%
  ggplot(aes(mean_mean_abs,RMSE, shape=treat, col=Measured_with, fill=Measured_with))+
  facet_wrap(~treat)+
  geom_line(data=newdata.meas.is)+
  geom_ribbon(data=newdata.meas.is, aes(ymax=upper,ymin=lower),
  						alpha=0.2, col=NA) +
	geom_point(size=2, alpha=0.6) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("col","fill"))+
  standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown())  + 
	labs(y="RMSE", x="Mean interaction strength", tag = "B", 
			 shape="Temperature", col="Measured with", fill="Measured with") 


m.is.count.meas <- lmer(mean_mean_abs~Measured_with*count*treat + (1|ID), data = ddrq1_treat_14_methods)
newdata.meas.is.count <- newdata.meas
newdata.meas.is.count$mean_mean_abs <- NULL
newdata.meas.is.count$mean_mean_abs <- predict(m.is.count.meas, newdata.meas.is.count, re.form=NA)
mm.meas.is.count <- model.matrix(terms(m.is.count.meas),newdata.meas.is.count)
pvar1.meas.is.count <- diag(mm.meas.is.count %*% tcrossprod(vcov(m.is.count.meas),mm.meas.is.count))
newdata.meas.is.count <- data.frame(newdata.meas.is.count,
																		lower=newdata.meas.is.count$mean_mean_abs-cmult*sqrt(pvar1.meas.is.count),
																		upper=newdata.meas.is.count$mean_mean_abs+cmult*sqrt(pvar1.meas.is.count))
newdata.meas.is.count$model <- "is.count"

meas.plot3 <- ddrq1_treat_14_methods %>%
  ggplot(aes(count, mean_mean_abs, shape=treat, col=Measured_with, fill=Measured_with))+
  facet_wrap(~treat)+
  geom_line(data=newdata.meas.is.count)+
  geom_ribbon(data=newdata.meas.is.count, aes(ymax=upper,ymin=lower),
  						alpha=0.2, col=NA) +
	geom_point(size=2, alpha=0.6) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("col","fill"))+
  standard_theme()+
	theme(legend.position = "right",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown())  + 
	labs(y="Mean interaction strength", x="Number of interactions", tag = "C", 
			 shape="Temperature", col="Measured with", fill="Measured with")

rm(m.count.meas,newdata.meas.count,mm.meas.count,pvar1.meas.count,
	 m.is.meas,newdata.meas.is,mm.meas.is,pvar1.meas.is,
	 m.is.count.meas,newdata.meas.is.count,mm.meas.is.count,pvar1.meas.is.count)
```


### Variation in the recorded data

```{r rq1_cv, cache=TRUE, warning=FALSE, message=FALSE}
ddrq1_treat_14_theta5 <- ddrq1_treat_14_thetas %>% dplyr::filter(theta==5)
ddrq1_treat_14_theta5$Target2 <- label[ddrq1_treat_14_theta5$Target]


m.cv.rmse <- lmer(RMSE~cv*treat + (1|ID), data = ddrq1_treat_14_theta5)
newdat.cv.rmse <- expand.grid(cv = seq(min(ddrq1_treat_14_theta5$cv),
																			 max(ddrq1_treat_14_theta5$cv),length.out = 200),
															treat = unique(ddrq1_treat_14_theta5$treat))		
newdat.cv.rmse$RMSE <- predict(m.cv.rmse, newdat.cv.rmse, re.form=NA)
mm.cv.rmse <- model.matrix(terms(m.cv.rmse),newdat.cv.rmse)
pvar1.cv.rmse <- diag(mm.cv.rmse %*% tcrossprod(vcov(m.cv.rmse),mm.cv.rmse))
newdat.cv.rmse <- data.frame(newdat.cv.rmse,
														 lower.iso=newdat.cv.rmse$RMSE-cmult*sqrt(pvar1.cv.rmse),
														 upper.iso=newdat.cv.rmse$RMSE+cmult*sqrt(pvar1.cv.rmse))
newdat.cv.rmse$model <- "cv.rmse"

m.cv.count <- lmer(count~cv*treat + (1|ID), data = ddrq1_treat_14_theta5)
newdat.cv.count <- expand.grid(cv = seq(min(ddrq1_treat_14_theta5$cv),
																						 max(ddrq1_treat_14_theta5$cv),length.out = 200),
													treat = unique(ddrq1_treat_14_theta5$treat))		
newdat.cv.count$count <- predict(m.cv.count, newdat.cv.count, re.form=NA)
mm.cv.count <- model.matrix(terms(m.cv.count),newdat.cv.count)
pvar1.cv.count <- diag(mm.cv.count %*% tcrossprod(vcov(m.cv.count),mm.cv.count))
newdat.cv.count <- data.frame(newdat.cv.count,
															lower.iso=newdat.cv.count$count-cmult*sqrt(pvar1.cv.count),
															upper.iso=newdat.cv.count$count+cmult*sqrt(pvar1.cv.count))
newdat.cv.count$model <- "cv.count"

m.cv.mean_mean_abs <- lmer(mean_mean_abs~cv*treat + (1|ID), data = ddrq1_treat_14_theta5)
newdat.cv.mean_mean_abs <- expand.grid(cv = seq(min(ddrq1_treat_14_theta5$cv),
																								max(ddrq1_treat_14_theta5$cv),length.out = 200),
																			 treat = unique(ddrq1_treat_14_theta5$treat))		
newdat.cv.mean_mean_abs$mean_mean_abs <- predict(m.cv.mean_mean_abs, newdat.cv.mean_mean_abs, re.form=NA)
mm.cv.mean_mean_abs <- model.matrix(terms(m.cv.mean_mean_abs),newdat.cv.mean_mean_abs)
pvar1.cv.mean_mean_abs <- diag(mm.cv.mean_mean_abs %*% tcrossprod(vcov(m.cv.mean_mean_abs),mm.cv.mean_mean_abs))
newdat.cv.mean_mean_abs <- data.frame(newdat.cv.mean_mean_abs,
															lower.iso=newdat.cv.mean_mean_abs$mean_mean_abs-cmult*sqrt(pvar1.cv.mean_mean_abs),
															upper.iso=newdat.cv.mean_mean_abs$mean_mean_abs+cmult*sqrt(pvar1.cv.mean_mean_abs))
newdat.cv.mean_mean_abs$model <- "cv.mean_mean_abs"

plot1aCV <-
	ddrq1_treat_14_theta5 %>%
  ggplot(aes(x=cv, y=RMSE, group=treat, shape=treat))+
  geom_line(data=newdat.cv.rmse)+
  geom_ribbon(data=newdat.cv.rmse, aes(ymax=lower.iso,ymin=upper.iso), alpha=0.2, col=NA) +
	geom_point(size=2, alpha=0.5, fill="black")+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat)+
	labs(x="Coefficient of variation", y="RMSE", tag = "A")

plot1bCV <-
	ddrq1_treat_14_theta5 %>%
  ggplot(aes(y=count, x=cv, group=treat, shape=treat))+
  geom_line(data=newdat.cv.count)+
  geom_ribbon(data=newdat.cv.count, aes(ymax=lower.iso,ymin=upper.iso), alpha=0.2, col=NA) +
	geom_point(size=2, alpha=0.5, fill="black")+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat)+
	labs(y="Number of interactions", x="Coefficient of variation", tag = "B")

plot1cCV <- ddrq1_treat_14_theta5 %>%
  ggplot(aes(y=mean_mean_abs, x=cv, group=treat, shape=treat))+
  geom_line(data=newdat.cv.mean_mean_abs)+
  geom_ribbon(data=newdat.cv.mean_mean_abs, aes(ymax=lower.iso,ymin=upper.iso),
              alpha=0.2, col=NA) +
	geom_point(size=2, alpha=0.5, fill="black")+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	standard_theme()+
	theme(legend.position = "right",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat)+
	labs(y="Mean interaction strength", x="Coefficient of variation", tag = "C")

rm(m.cv.rmse,newdat.cv.rmse,mm.cv.rmse,pvar1.cv.rmse,
	 m.cv.count,newdat.cv.count,mm.cv.count,pvar1.cv.count,
	 m.cv.mean_mean_abs,newdat.cv.mean_mean_abs,mm.cv.mean_mean_abs,pvar1.cv.mean_mean_abs)
```

## Forecasting robustness analyses 

### Using the best multiview models

```{r mean_int_rmse_plot_with_best_model_calc_, fig.width=13, fig.height=6, out.width="95%", cache=TRUE, message=FALSE, warning=FALSE}
ddrq1_best <- ddrq1_equi %>% 
	dplyr::filter(RMSE_equi==T) %>%
	group_by(ID, treat, Target) %>%
	slice_min(num_pred,n=1) %>%
	slice_min(RMSE,n=1) %>% 
	sample_n(1) %>%
	full_join(dd_smap_params_abs)

ddrq1_best <- full_join(ddrq1_best, cv)
ddrq1_best <- full_join(ddrq1_best, permutation_entropies)
ddrq1_best$target <- ddrq1_best$Target
ddrq1_best <- ddrq1_best %>% dplyr::select(-best_rmse_bool,-min_rmse,-RMSE_equi)
ddrq1_best$treat <- ifelse(ddrq1_best$treat=="const","Constant","Fluctuating")
ddrq1_best$Target2 <- label[ddrq1_best$Target]
ddrq1_best$robust <- "Best multiview EDM model"

rq1_model_fcts_list <- rq1_model_fcts(ddrq1_best)
newdat_robust_best <- rq1_model_fcts_list[[1]]
tab.rq1.best <- rq1_model_fcts_list[[2]]

tab.rq1.best <- tab.rq1.best[1:15,]
newdat_robust_best$robust <- "Best multiview EDM model"

rm(rq1_model_fcts_list)
```

### Univariate simplex with optimal E

```{r univariatesimplex, message=FALSE, warning=FALSE, cache=TRUE}
dd_simplex <- lapply(targets, function(target){
  simplexForecasting(dd2, target, num.clusters = 1, maxE = 7)
})
dd_simplex <- do.call("rbind", dd_simplex)

dd_simplex <- full_join(dd_simplex, dd_smap_params_abs)

rq1_model_fcts_list <- rq1_model_fcts(dd_simplex)
newdat_simplex <- rq1_model_fcts_list[[1]]
tab.rq1.simplex <- rq1_model_fcts_list[[2]]

tab.rq1.simplex <- tab.rq1.simplex[1:15,]
newdat_simplex$robust <- "Univariate simplex EDM"
```


### Merging results

```{r univariatesimplex_merging, message=FALSE, warning=FALSE, cache=TRUE}
dd_forecasts_merge <- dd_simplex
dd_forecasts_merge$RMSE_mv <- ddrq1_treat_14$RMSE

dd_forecasts_merge$Treat <- ifelse(dd_forecasts_merge$treat=="const",
														 "Constant temperature","Fluctuating temperature")
dd_forecasts_merge$treat4 <- ifelse(dd_forecasts_merge$treat=="const","Constant","Fluctuating")
dd_forecasts_merge$Target <- label[dd_forecasts_merge$Target]

ddrq1_best_suppl$RMSEbest <- ddrq1_best_suppl$RMSE
dd_forecasts_merge <- full_join(dd_forecasts_merge, ddrq1_best_suppl[,c("Target","ID","RMSEbest")])

dd_forecasts_merge_long <- dd_forecasts_merge %>% pivot_longer(cols = c("RMSE","RMSE_mv","RMSEbest")) %>%
  mutate(name=ifelse(name=="RMSE","Univariate\nsimplex EDM",
                     ifelse(name=="RMSE_mv","Full multiview\nEDM model","Best multiview\nEDM model")))
dd_forecasts_merge_long2 <- dd_forecasts_merge %>% pivot_longer(cols = c("RMSE","RMSEbest")) %>%
  mutate(name=ifelse(name=="RMSE","Univariate simplex EDM","Best multiview EDM model"))

forecast_boxplot <- dd_forecasts_merge_long %>%
  ggplot(aes(name,value,col=name,shape=treat))+
  facet_wrap(~treat)+
  geom_boxplot() +
  geom_point(aes(fill=name),size=1.2, alpha=0.3)+
  scale_color_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	scale_shape_manual(values=c(21,23))+
  standard_theme()+
  theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank())+
	labs(x="", y="RMSE", tag = "A",col="",fill="")

cols <- brewer.pal(3,"Dark2")

forecast_corr <- dd_forecasts_merge_long2 %>%
  ggplot(aes(value,RMSE_mv,fill=name,col=name,shape=treat))+
  geom_abline(slope = 1, intercept = 0)+
  facet_wrap(~treat)+
  geom_point(size=1.2, alpha=0.6) +
  standard_theme2() +
	scale_shape_manual(values=c(21,23))+
  theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank())+
  scale_fill_manual(values = cols[c(1,3)], aesthetics = c("fill","col"))+
	labs(x="RMSE of respective model", y="RMSE of full\nmultiview EDM model", tag = "B",col="",fill="")

####

newdat_forecast <- full_join(newdat_simplex, 
                           full_join(newdat_robust_best,newdat_thetas %>% dplyr::filter(theta==5)))

ddrq1_best$temperature_included <- as.logical(ddrq1_best$temperature_included)
ddrq1_treat_14$temperature_included <- as.logical(ddrq1_treat_14$temperature_included)
ddrq1_best$target_excluded <- as.logical(ddrq1_best$target_excluded)
ddrq1_treat_14$target_excluded <- as.logical(ddrq1_treat_14$target_excluded)

dd_simplex$robust <- "Univariate simplex EDM"
ddrq1_treat_14$robust <- "Full multiview EDM model"
ddrq1_best$robust <- "Best multiview EDM model"
dd_forecast <- full_join(full_join(dd_simplex, ddrq1_best),ddrq1_treat_14)

tab.rq1.best <- cbind(Model="Best multiview EDM model",tab.rq1.best)
tab.rq1.simplex<- cbind(Model="Univariate simplex EDM",tab.rq1.simplex)
tab.model <- rbind(tab.rq1.best,tab.rq1.simplex)

dd_forecast$treat <- ifelse(dd_forecast$treat %in% c("const","Constant"),"Constant","Fluctuating")
newdat_forecast$robust <- ifelse(is.na(newdat_forecast$robust),"Full multiview EDM model",newdat_forecast$robust)

plot.simplexbest1 <- dd_forecast %>%
  ggplot(aes(count,RMSE, shape=treat, col=robust, fill=robust))+
  facet_wrap(~treat)+
  geom_ribbon(data=newdat_forecast %>% dplyr::filter(model=="count"),
  						aes(ymax=lower.count,ymin=upper.count), alpha=0.2, col=NA) +
  geom_point(size=1.2, alpha=0.33) +
  geom_line(data=newdat_forecast %>% dplyr::filter(model=="count"), 
            size=1.2) +	
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2",aesthetics = c("col","fill")) +  
  standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	labs(x="Number of interactions", y="RMSE", tag = "C")


plot.simplexbest2 <- dd_forecast %>%
  ggplot(aes(mean_mean_abs,RMSE, shape=treat, col=robust, fill=robust))+
  facet_wrap(~treat)+
  geom_ribbon(data=newdat_forecast %>% dplyr::filter(model=="mean_mean_abs"),
  						aes(ymax=lower.mean_mean_abs,ymin=upper.mean_mean_abs), alpha=0.2, col=NA) +
  geom_point(size=1.2, alpha=0.33) +
  geom_line(data=newdat_forecast %>% dplyr::filter(model=="mean_mean_abs"), size=1.2) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2",aesthetics = c("col","fill")) +  
	standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	labs(x="Mean interaction strength", y="RMSE", tag = "D")

plot.simplexbest.leg <- dd_forecast %>%
  ggplot(aes(count, mean_mean_abs, shape=treat, col=robust, fill=robust))+
  geom_line(data=newdat_forecast %>% dplyr::filter(model=="corr"))+
  geom_ribbon(data=newdat_forecast %>% dplyr::filter(model=="corr"), aes(ymax=lower.corr,ymin=upper.corr), alpha=0.2, col=NA) +
  geom_point(size=2, alpha=1) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2",aesthetics = c("col","fill")) +  
	standard_theme()+
	theme(legend.position = "right",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat) + 
	labs(x="Number of interactions", y="Mean interaction strength", tag = "C", 
			 shape="Temperature", col="Forecast model", fill="Forecast model")

plot.simplexbest.leg <- get_legend(plot.simplexbest.leg)
```

## Forecasting: using other methods

### ARIMA

```{r arima_forecast, message=FALSE, warning=FALSE, cache=TRUE}
dd2.list <- split(dd2, f=dd2$ID)

arima.forecast.rmse <- lapply(dd2.list, function(df){
  ID <- unique(df$ID)
  treat <- unique(df$treat)
  treat2 <- unique(df$treat2)
  treat3 <- unique(df$treat3)
  
  df <- df %>%
    ungroup() %>%
    dplyr::select(-ID, -treat, -treat2, -treat3, -date, -incubator)
  
  lib <- 1:floor(NROW(df)*2/3)
  pred <- (floor(NROW(df)*2/3) + 1):NROW(df)
  
  b.train <- df[lib,]
  b.forecast <- df[pred,]
  
  covariates <- colnames(df)[-1]
  
  b.temp <- lapply(targets, function(target){
    
    idx <- which(target==covariates)
    predictors <- covariates[-idx]
    m <- auto.arima(b.train[target], d=0) #xreg = as.matrix(b.train[,predictors])
    # checkresiduals(m)
    forecast <- fitted(Arima(df[,target],model=m))[pred] #xreg = as.matrix(b.forecast[,predictors])
    
    rmse <- sqrt(mean((unlist(b.forecast[target])-forecast)^2, na.rm = T))
    
    data.frame(Target=target, ID=ID, RMSE=rmse, treat=treat, treat2=treat2, treat=treat3)
  })
  
  do.call("rbind", b.temp)
})

arima.forecast.rmse <- do.call("rbind", arima.forecast.rmse)

arima.forecast.rmse <- full_join(arima.forecast.rmse, dd_smap_params_abs)

rq1_model_fcts_list <- rq1_model_fcts(arima.forecast.rmse)
newdat_arima <- rq1_model_fcts_list[[1]]
tab.rq1.arima <- rq1_model_fcts_list[[2]]

tab.rq1.arima <- tab.rq1.arima[1:10,]
newdat_arima$robust <- "ARIMA"

arima.forecast.rmse$treat <- ifelse(arima.forecast.rmse$treat=="const","Constant","Fluctuating")
arima.forecast.rmse$Target2 <- label[arima.forecast.rmse$Target]
```

### Recurrent neural networks

The following code-chunk is not run. Its result are loaded in later.
```{r RNN_forecast, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
# set some parameters for our model
batch_size <- 64 # number of sequences to look at at one time during training
total_epochs <- 30 # how many times we'll look @ the whole dataset while training our model

# set a random seed for reproducability
set.seed(123)

possible_predictors <- c("bacteria","chlamydomonas_reinhardtii","colpidium_striatum",
                         "dexiostomata_campylum", "didinium_nasutum",
                         "euglena_gracilis","euplotes_daidaleos","paramecium_caudatum",
                         "rotifer_sp","big_white_particle","dissolved_oxygen",
                         "green_white_particle", "small_white_particle",
                         "temperature")

dd2.list <- split(dd2, f=dd2$ID)

RNN.forecast.rmse <- mclapply(dd2.list, function(df){
  ID <- unique(df$ID)
  treat <- unique(df$treat)
  treat2 <- unique(df$treat2)
  treat3 <- unique(df$treat3)
  
  df <- df %>%
    ungroup() %>%
    dplyr::select(-ID, -treat, -treat2, -treat3, -date, -incubator)
  
  lib <- 1:floor(NROW(df)*2/3)
  pred <- (floor(NROW(df)*2/3) + 1):NROW(df)

  X_train <- as.matrix(df[lib[-length(lib)], possible_predictors])
  X_test <- as.matrix(df[pred[-length(pred)], possible_predictors])
    
  b.temp <- lapply(targets, function(target){
    
    y_train <- as.matrix(df[lib[-1], target])
    y_test <- as.matrix(df[pred[-1], target])
    
    # initialize our model
    # install_keras()
    model <- keras_model_sequential() %>%
      layer_dense(units = 6, activation = 'relu', input_shape = length(possible_predictors), 
                  kernel_initializer=initializer_random_uniform(seed = 43)) %>% 
      layer_dense(units = 36, activation = 'relu',
                  kernel_initializer=initializer_random_uniform(seed = 23)) %>%
      layer_dense(units = 1, activation = 'linear',
                  kernel_initializer=initializer_random_uniform(seed = 55))
    
    model %>% compile(
      loss = 'mean_squared_error',
      optimizer = 'adam',
      metrics = c('mae')
    )
    
    # Actually train our model! This step will take a while
    trained_model <- model %>% fit(
      x = X_train, # sequence we're using for prediction 
      y = y_train, # sequence we're predicting
      batch_size = batch_size, # how many samples to pass to our model at a time
      epochs = total_epochs, # how many times we'll look @ the whole dataset
      verbose=0,
      validation_split = 0.1) # how much data to hold out for testing as we go along
    
    forecast <- data.frame(y = predict(model, x=X_test))
    
    rmse <- sqrt(mean(unlist(y_test-forecast)^2, na.rm = T))
    
    data.frame(Target=target, ID=ID, RMSE=rmse, treat=treat, treat2=treat2, treat=treat3)
  })
  
  do.call("rbind", b.temp)
}, mc.cores=detectCores()-2)

RNN.forecast.rmse <- do.call("rbind", RNN.forecast.rmse)
save(RNN.forecast.rmse, file = here("Data/Multiview_forecast_data/RNN_forecast_rmse.RData"))
```


### ARIMA and RNN put together

```{r ARIMA_RNN_merging, message=FALSE, warning=FALSE, cache=TRUE}
load(here("Data/Multiview_forecast_data/RNN_forecast_rmse.RData"))
RNN.forecast.rmse <- full_join(RNN.forecast.rmse, dd_smap_params_abs)

rq1_model_fcts_list <- rq1_model_fcts(RNN.forecast.rmse)
newdat_rnn <- rq1_model_fcts_list[[1]]
tab.rq1.rnn <- rq1_model_fcts_list[[2]]

tab.rq1.rnn <- tab.rq1.rnn[1:10,]
newdat_rnn$robust <- "RNN"

RNN.forecast.rmse$treat <- ifelse(RNN.forecast.rmse$treat=="const","Constant","Fluctuating")
RNN.forecast.rmse$Target <- label[RNN.forecast.rmse$Target]

dd_forecasts_merge2 <- RNN.forecast.rmse
dd_forecasts_merge2$RMSE_arima <- arima.forecast.rmse$RMSE

dd_forecasts_merge2 <- full_join(dd_forecasts_merge2, ddrq1_best_suppl[,c("Target","ID","RMSEbest")])

dd_forecasts_merge2_long <- dd_forecasts_merge2 %>% pivot_longer(cols = c("RMSE","RMSE_arima","RMSEbest")) %>%
  mutate(name=ifelse(name=="RMSE","RNN",
                     ifelse(name=="RMSE_arima","ARIMA","Best EDM")))
dd_forecasts_merge2_long2 <- dd_forecasts_merge2 %>% pivot_longer(cols = c("RMSE","RMSE_arima")) %>%
  mutate(name=ifelse(name=="RMSE","RNN","ARIMA"))

forecast_boxplot2 <- dd_forecasts_merge2_long %>%
  ggplot(aes(name,value,col=name,shape=treat))+
  facet_wrap(~treat)+
  geom_boxplot() +
  geom_point(aes(fill=name),size=1.2, alpha=0.3)+
  scale_color_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	scale_shape_manual(values=c(21,23))+
  standard_theme()+
  theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank())+
	labs(x="", y="RMSE", tag = "A",col="",fill="")

cols <- names(robust_levels) <- brewer.pal(3,"Dark2")

forecast_corr2 <- dd_forecasts_merge2_long2 %>%
  ggplot(aes(value,RMSEbest,fill=name,col=name,shape=treat))+
  geom_abline(slope = 1, intercept = 0)+
  facet_wrap(~treat, scales="free_x")+
  geom_point(size=1.2, alpha=0.6) +
  standard_theme2() +
	scale_shape_manual(values=c(21,23))+
  theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank())+
  scale_fill_manual(values = cols[c(1,3)], aesthetics = c("fill","col"))+
	labs(x="RMSE of respective model", y="RMSE of best\nmultiview EDM model", tag = "B",col="",fill="")

####
newdat_robust_best$robust <- "Best EDM"
newdat_forecast2 <- full_join(newdat_rnn, 
                           full_join(newdat_robust_best,newdat_arima))

# ddrq1_best$temperature_included <- as.logical(ddrq1_best$temperature_included)
# ddrq1_treat_14$temperature_included <- as.logical(ddrq1_treat_14$temperature_included)
# ddrq1_best$target_excluded <- as.logical(ddrq1_best$target_excluded)
# ddrq1_treat_14$target_excluded <- as.logical(ddrq1_treat_14$target_excluded)

RNN.forecast.rmse$robust <- "RNN"
arima.forecast.rmse$robust <- "ARIMA"
ddrq1_best$robust <- "Best EDM"
dd_forecast2 <- full_join(full_join(RNN.forecast.rmse, arima.forecast.rmse), ddrq1_best)

tab.rq1.arima <- cbind(Model="ARIMA",tab.rq1.best)
tab.rq1.rnn<- cbind(Model="RNN",tab.rq1.simplex)
tab.model2 <- rbind(tab.rq1.arima,tab.rq1.rnn)

dd_forecast2$treat <- ifelse(dd_forecast2$treat %in% c("const","Constant"),"Constant","Fluctuating")
# newdat_forecast2$robust <- ifelse(is.na(newdat_forecast2$robust),"Full multiview EDM model",newdat_forecast2$robust)

plot.ARIMARNN1 <- dd_forecast2 %>%
  ggplot(aes(count,RMSE, shape=treat, col=robust, fill=robust))+
  facet_wrap(~treat)+
  geom_ribbon(data=newdat_forecast2 %>% dplyr::filter(model=="count"),
  						aes(ymax=lower.count,ymin=upper.count), alpha=0.2, col=NA) +
  geom_point(size=1.2, alpha=0.33) +
  geom_line(data=newdat_forecast2 %>% dplyr::filter(model=="count"), 
            size=1.2) +	
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2",aesthetics = c("col","fill")) +  
  standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	labs(x="Number of interactions", y="RMSE", tag = "C")


plot.ARIMARNN2 <- dd_forecast2 %>%
  ggplot(aes(mean_mean_abs,RMSE, shape=treat, col=robust, fill=robust))+
  facet_wrap(~treat)+
  geom_ribbon(data=newdat_forecast2 %>% dplyr::filter(model=="mean_mean_abs"),
  						aes(ymax=lower.mean_mean_abs,ymin=upper.mean_mean_abs), alpha=0.2, col=NA) +
  geom_point(size=1.2, alpha=0.33) +
  geom_line(data=newdat_forecast2 %>% dplyr::filter(model=="mean_mean_abs"), size=1.2) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2",aesthetics = c("col","fill")) +  
	standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	labs(x="Mean interaction strength", y="RMSE", tag = "D")

plot.ARIMARNN.leg <- dd_forecast2 %>%
  ggplot(aes(count, mean_mean_abs, shape=treat, col=robust, fill=robust))+
  geom_line(data=newdat_forecast2 %>% dplyr::filter(model=="corr"))+
  geom_ribbon(data=newdat_forecast2 %>% dplyr::filter(model=="corr"), aes(ymax=lower.corr,ymin=upper.corr), alpha=0.2, col=NA) +
  geom_point(size=2, alpha=1) +
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2",aesthetics = c("col","fill")) +  
	standard_theme()+
	theme(legend.position = "right",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat) + 
	labs(x="Number of interactions", y="Mean interaction strength", tag = "C", 
			 shape="Temperature", col="Forecast model", fill="Forecast model")

plot.ARIMARNN.leg <- get_legend(plot.ARIMARNN.leg)

```

### Permutation entropy

```{r pe_va, cache=TRUE, warning=FALSE, message=FALSE}
ddrq1_treat_14_theta5$pe.transf <- ddrq1_treat_14_theta5$PE^4
m.pe.rmse <- lmer(RMSE~pe.transf*treat + (1|ID), data = ddrq1_treat_14_theta5)
newdat.pe.rmse <- expand.grid(pe.transf = seq(min(ddrq1_treat_14_theta5$pe.transf),
																								max(ddrq1_treat_14_theta5$pe.transf),length.out = 200),
																			 treat = unique(ddrq1_treat_14_theta5$treat))		
newdat.pe.rmse$RMSE <- predict(m.pe.rmse, newdat.pe.rmse, re.form=NA)
mm.pe.rmse <- model.matrix(terms(m.pe.rmse),newdat.pe.rmse)
pvar1.pe.rmse <- diag(mm.pe.rmse %*% tcrossprod(vcov(m.pe.rmse),mm.pe.rmse))
newdat.pe.rmse <- data.frame(newdat.pe.rmse,
															lower.iso=newdat.pe.rmse$RMSE-cmult*sqrt(pvar1.pe.rmse),
															upper.iso=newdat.pe.rmse$RMSE+cmult*sqrt(pvar1.pe.rmse))
newdat.pe.rmse$model <- "pe.rmse"


plot1aPE <- ddrq1_treat_14_theta5 %>%
  ggplot(aes(x=pe.transf, y=RMSE, group=treat, shape=treat))+
  geom_line(data=newdat.pe.rmse)+
  geom_ribbon(data=newdat.pe.rmse, aes(ymax=lower.iso,ymin=upper.iso), alpha=0.2, col=NA) +
	geom_point(size=2, alpha=0.5, fill="black")+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat)+
	labs(x="(Permutation entropy)^4", y="RMSE", tag = "A")


m.pe.count <- lmer(pe.transf~count*treat + (1|ID), data = ddrq1_treat_14_theta5)
newdat.pe.count <- expand.grid(count = seq(min(ddrq1_treat_14_theta5$count),
																								max(ddrq1_treat_14_theta5$count),length.out = 200),
																			 treat = unique(ddrq1_treat_14_theta5$treat))		
newdat.pe.count$pe.transf <- predict(m.pe.count, newdat.pe.count, re.form=NA)
mm.pe.count <- model.matrix(terms(m.pe.count),newdat.pe.count)
pvar1.pe.count <- diag(mm.pe.count %*% tcrossprod(vcov(m.pe.count),mm.pe.count))
newdat.pe.count <- data.frame(newdat.pe.count,
															lower.iso=newdat.pe.count$pe.transf-cmult*sqrt(pvar1.pe.count),
															upper.iso=newdat.pe.count$pe.transf+cmult*sqrt(pvar1.pe.count))
newdat.pe.count$model <- "pe.count"

plot1bPE <- ddrq1_treat_14_theta5 %>%
  ggplot(aes(x=count, y=pe.transf, group=treat, shape=treat))+
  geom_line(data=newdat.pe.count)+
  geom_ribbon(data=newdat.pe.count, aes(ymax=lower.iso,ymin=upper.iso), alpha=0.2, col=NA) +
	geom_point(size=2, alpha=0.5, fill="black")+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	standard_theme()+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat)+
	labs(x="Number of interactions", y="(Permutation entropy)^4", tag = "B")


m.pe.is <- lmer(pe.transf~mean_mean_abs*treat + (1|ID), data = ddrq1_treat_14_theta5)
newdat.pe.is <- expand.grid(mean_mean_abs = seq(min(ddrq1_treat_14_theta5$mean_mean_abs),
																								max(ddrq1_treat_14_theta5$mean_mean_abs),length.out = 200),
																			 treat = unique(ddrq1_treat_14_theta5$treat))		
newdat.pe.is$pe.transf <- predict(m.pe.is, newdat.pe.is, re.form=NA)
mm.pe.is <- model.matrix(terms(m.pe.is),newdat.pe.is)
pvar1.pe.is <- diag(mm.pe.is %*% tcrossprod(vcov(m.pe.is),mm.pe.is))
newdat.pe.is <- data.frame(newdat.pe.is,
															lower.iso=newdat.pe.is$pe.transf-cmult*sqrt(pvar1.pe.is),
															upper.iso=newdat.pe.is$pe.transf+cmult*sqrt(pvar1.pe.is))
newdat.pe.is$model <- "pe.is"


plot1cPE <- ddrq1_treat_14_theta5 %>%
  ggplot(aes(x=mean_mean_abs, y=pe.transf, group=treat, shape=treat))+
  geom_line(data=newdat.pe.is)+
  geom_ribbon(data=newdat.pe.is, aes(ymax=lower.iso,ymin=upper.iso), alpha=0.2, col=NA) +
	geom_point(size=2, alpha=0.5, fill="black")+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
	standard_theme()+
	theme(legend.position = "right",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	facet_wrap(~treat)+
	labs(x="Mean interaction strength", y="(Permutation entropy)^4", tag = "C", shape="Temperature")

rm(m.pe.rmse,newdat.pe.rmse,mm.pe.rmse,pvar1.pe.rmse,
	 m.pe.count,newdat.pe.count,mm.pe.count,pvar1.pe.count,
	 m.pe.is,newdat.pe.is,mm.pe.is,pvar1.pe.is)
```


## MARSS: Species interaction estimation

The code in the following chunk is not executed. Instead the results are then loaded in afterwards

```{r multiview_forecast_analysis_nontarget, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
interactors <- colnames(dd2[,-c(1:7)])
nontargets <- interactors[!is.element(interactors,targets)]
nontargets <- nontargets[c(1,3,4,5)]
var_pairs <- expand.grid(target=nontargets, interactors=interactors)

dd2_dflist <- split(dd2, dd2$ID)

pairwise_ccm_df_list <- mclapply(dd2_dflist, function(df){
	dftemp <- df[,-c(1,3:7)]
	Best_E_df <- apply(var_pairs,1, function(c){
		best_E_fct(dftemp,c[1],c[2])
	})
	
	Best_E_df <- do.call("rbind",Best_E_df)
	Best_E_df$ID <- unique(df$ID)
	Best_E_df$treat <- unique(df$treat)
	Best_E_df$treat2 <- unique(df$treat2)
	Best_E_df$treat3 <- unique(df$treat3)
	
	rhos <- apply(Best_E_df, 1, function(r){
		ccm_out <- CCM(dataFrame = dftemp, target = r[1], column = r[2],
									 libSizes = "10 60 10", Tp = 0, E = as.numeric(r[3]), sample = 100)
		rho <- ccm_out[6,3]
		if(rho<0) return(data.frame(rho=rho,comment="negative"))
		slope <- lm(ccm_out[,3] ~ seq(10,60,by = 10))$coefficients[2]
		if(slope>=0) {return(data.frame(rho=rho,comment="converged"))
		} else {return(data.frame(rho=rho,comment="not converged"))}
	})
	
	Best_E_df <- cbind(Best_E_df,do.call("rbind",rhos))
	
	rho_df <- Best_E_df %>%
		dplyr::filter(target %in% nontargets, comment=="converged")
	
	significances <- apply(rho_df, 1, function(r){
		ts <- unlist(df[,as.character(r[2])])
		# target <- r[2]
		surr_interactor = SurrogateData(ts, method = "random_shuffle",
																		num_surr = 1000, alpha = 3)
		
		rho_surr <- data.frame(interactor_rho = numeric(1000))
		
		interactor_data = as.data.frame(cbind(df$day, ts, surr_interactor))
		names(interactor_data) = c("day", r[1], paste("T", as.character(seq(1, 1000)),	sep = ""))
		
		for (i in 1:1000) {
			targetCol = paste("T", i, sep = "") 
			ccm_out = CCM(dataFrame = interactor_data, E = as.numeric(r[3]), Tp = 0, columns = r[1],
										target = targetCol, libSizes = "60 60 10", sample = 1)
			col = paste(r[1], ":", targetCol, sep = "")
			rho_surr$interactor_rho[i] = ccm_out[1, col]
		}
		1 - ecdf(rho_surr$interactor_rho)(as.numeric(r["rho"]))
	})
	
	rho_df$significances <- significances
	pairwise_ccm_df <- full_join(Best_E_df,rho_df)
	pairwise_ccm_df
}, mc.cores = detectCores()-2)

pairwise_ccm_df_list_nontargets <- pairwise_ccm_df_list
save(pairwise_ccm_df_list_nontargets, file = here("Data/CCM_analysis_data/pairwise_ccm_df_list_transf_resid_nontargets.RData"))
```


```{r MARSS_prep, cache=TRUE, message=FALSE, warning=FALSE}
load(here("Data/CCM_analysis_data/pairwise_ccm_df_list_transf_resid.RData")) # loaded again, same as above
pairwise_ccm_df <- do.call("rbind",pairwise_ccm_df_list)
pairwise_ccm_df$interaction <- ifelse(pairwise_ccm_df$significances<0.05 & pairwise_ccm_df$rho>0,T,F)
pairwise_ccm_df$interaction <- ifelse(pairwise_ccm_df$comment=="not converged",F,pairwise_ccm_df$interaction)

load(here("Data/CCM_analysis_data/pairwise_ccm_df_list_transf_resid_nontargets.RData"))
pairwise_ccm_df_nontargets <- do.call("rbind",pairwise_ccm_df_list_nontargets)
pairwise_ccm_df_nontargets$interaction <- ifelse(pairwise_ccm_df_nontargets$significances<0.05 & pairwise_ccm_df_nontargets$rho>0,T,F)
pairwise_ccm_df_nontargets$interaction <- ifelse(pairwise_ccm_df_nontargets$comment=="not converged",F,pairwise_ccm_df_nontargets$interaction)

pairwise_ccm_df_merged <- rbind(pairwise_ccm_df, pairwise_ccm_df_nontargets)

interaction_matrix_constructor <- function(pairwise, bottle_ID){
	names <- c(unique(pairwise$target))
	names_long <- names
	names <- substr(names, 1, 4)
	
	B <- matrix(list(0), length(names), length(names))
	diag(B) <- names
	rownames(B) <- colnames(B) <- names
	
	bottle <- pairwise %>% dplyr::filter(ID==bottle_ID)

	for(tar in names_long) {
		for(int in names_long){
			tar_short <- substr(tar, 1, 4) 
			int_short <- substr(int, 1, 4)
			if(tar %in% c("didinium_nasutum","temperature")){
				B[tar_short,int_short] <- 0
			} else {
				interaction <- bottle[bottle$target==tar & bottle$interactor==int,"interaction"]
				B[tar_short,int_short] <- ifelse(interaction==T,paste(int_short,tar_short,sep = "->"),0)	
			}
		}
	}
	return(B)
}

interaction_matrix_constructor_unconstrained <- function(pairwise, bottle_ID){
  names <- c(unique(pairwise$target))
  names_long <- names
  names <- substr(names, 1, 4)
  
  B <- matrix(list(0), length(names), length(names))
  diag(B) <- names
  rownames(B) <- colnames(B) <- names
  
  bottle <- pairwise %>% dplyr::filter(ID==bottle_ID)
  
  for(tar in names_long) {
    for(int in names_long){
      tar_short <- substr(tar, 1, 4) 
      int_short <- substr(int, 1, 4)
      if(tar %in% c("didinium_nasutum","temperature")){
        B[tar_short,int_short] <- 0
      } else {
        # interaction <- bottle[bottle$target==tar & bottle$interactor==int,"interaction"]
        B[tar_short,int_short] <- paste(int_short,tar_short,sep = "->")	
      }
    }
  }
  return(B)
}

names <- c(unique(pairwise_ccm_df_merged$target))
names_long <- names
names <- substr(names, 1, 4)
names_length <- length(names)

R <- matrix(list(0), length(names), length(names))
diag(R) <- c("flowcyto","flowcam","video","flowcam","flowcam","video","video","manual","flowcam","oxygen","flowcam","flowcam")

Q <- matrix(list(0), names_length, names_length)
Q[1:(names_length), 1:(names_length)] <- paste(rep(1:(names_length), times = names_length), 
																									 rep(1:(names_length), each = names_length), sep = "_")
Q[lower.tri(Q)] <- t(Q)[lower.tri(Q)]
```

The following chunk is not run. Results loaded in after it.

```{r MARSS, cache=TRUE, message=FALSE, warning=FALSE, eval=FALSE}
marss.list.Rmeasspecific.Bunconstrained <- mclapply(unique(pairwise_ccm_df_merged$ID), function(id){
  B <- interaction_matrix_constructor_unconstrained(pairwise = pairwise_ccm_df_merged, bottle_ID = id)
  
  marss.model.0 <- list(
    B = B, U = "zero", Q = Q,
    Z = "identity", A = "zero", R = R,
    x0 = "unequal", tinitx = 1
  )
  
  marss_dd <- dd2 %>%
    dplyr::filter(ID==id) %>%
    ungroup() %>%
    dplyr::select(all_of(names_long))
  
  colnames(marss_dd) <- names
  marss_dd <- t(marss_dd)
  
  MARSS(marss_dd, model = marss.model.0)
  
}, mc.cores = detectCores())

save(marss.list.Rmeasspecific.Bunconstrained, file = here("Data/MARSS_analysis_data/marss.list.Rmeasspecific.Bunconstrained.RData"))


marss.list.Rmeasspecific.Bconstrained <- mclapply(unique(pairwise_ccm_df_merged$ID), function(id){
  B <- interaction_matrix_constructor(pairwise = pairwise_ccm_df_merged, bottle_ID = id)

  marss.model.0 <- list(
    B = B, U = "zero", Q = Q,
    Z = "identity", A = "zero", R = R,
    x0 = "unequal", tinitx = 1
  )
  
  marss_dd <- dd2 %>%
    dplyr::filter(ID==id) %>%
    ungroup() %>%
    dplyr::select(all_of(names_long))
  
  colnames(marss_dd) <- names
  marss_dd <- t(marss_dd)
  
  MARSS(marss_dd, model = marss.model.0)
  
}, mc.cores = detectCores())

save(marss.list.Rmeasspecific.Bconstrained, file = here("Data/MARSS_analysis_data/marss.list.Rmeasspecific.Bconstrained.RData"))
```

```{r MARSS2, cache=TRUE, message=FALSE, warning=FALSE}
load(here("Data/MARSS_analysis_data/marss.list.Rmeasspecific.Bconstrained.RData")) # B constrained, R based on measurement method, did and temp excluded
load(here("Data/MARSS_analysis_data/marss.list.Rmeasspecific.Bunconstrained.RData")) # B completely unconstrained, R based on measurement method, did and temp excluded

Bs <- lapply(marss.list.Rmeasspecific.Bconstrained, function(m){
	B<- coef(m, type = "matrix")$B
	rownames(B) <- colnames(B) <- names
	B 
})

Bs.Rmeasspecific.Bunconstrained <- lapply(marss.list.Rmeasspecific.Bunconstrained, function(m){
	B<- coef(m, type = "matrix")$B
	rownames(B) <- colnames(B) <- names
	B
})

ddrq1_treat_marss_list <- split(ddrq1_treat_14_theta5, ddrq1_treat_14_theta5$ID)

for(i in 1:18){
	B <- Bs[[i]]
	ddrq1_treat_marss_list[[i]]$marss <- rowSums(abs(B))[1:8]
	ddrq1_treat_marss_list[[i]]$marss <- ddrq1_treat_marss_list[[i]]$marss/ddrq1_treat_marss_list[[i]]$count

	B <- Bs.Rmeasspecific.Bunconstrained[[i]]
	ddrq1_treat_marss_list[[i]]$marss.Rmeasspecific.Bunconstrained <- rowSums(abs(B))[1:8]/nrow(B)
}

ddrq1_treat_marss <- do.call("rbind",ddrq1_treat_marss_list) %>%
  mutate(treat = ifelse(treat %in% c("const","Constant"),"Constant","Fluctuating"),
         Target2 = label[Target],
         smap = mean_mean_abs)

ddrq1_treat_marss_long <- ddrq1_treat_marss %>%
	pivot_longer(cols = c("marss","marss.Rmeasspecific.Bunconstrained","mean_mean_abs"), 
	             names_to = "Method", values_to = "interaction_estimate") %>%
  mutate(Method = ifelse(Method=="marss",
                         "MARSS based on CCM interactions",
                         ifelse(Method=="marss.Rmeasspecific.Bunconstrained",
                                "MARSS based on all interactions",
                                "S-map based on CCM interactions")))

m.mars.smap.1 <- lmer(marss~smap*treat + (1|ID), data = ddrq1_treat_marss)
newdat.mars.smap.1 <- expand.grid(smap = seq(min(ddrq1_treat_marss$smap),
                                             max(ddrq1_treat_marss$smap),length.out = 200),
                                  treat = unique(ddrq1_treat_marss$treat))		
newdat.mars.smap.1$marss <- predict(m.mars.smap.1, newdat.mars.smap.1, re.form=NA)
mm.mars.smap.1 <- model.matrix(terms(m.mars.smap.1),newdat.mars.smap.1)
pvar1.mars.smap.1 <- diag(mm.mars.smap.1 %*% tcrossprod(vcov(m.mars.smap.1),mm.mars.smap.1))
newdat.mars.smap.1 <- data.frame(newdat.mars.smap.1,
                                 lower=newdat.mars.smap.1$marss-cmult*sqrt(pvar1.mars.smap.1),
                                 upper=newdat.mars.smap.1$marss+cmult*sqrt(pvar1.mars.smap.1))

m.mars.smap.2 <- lmer(marss.Rmeasspecific.Bunconstrained~smap*treat + (1|ID), data = ddrq1_treat_marss)
newdat.mars.smap.2 <- expand.grid(smap = seq(min(ddrq1_treat_marss$smap),
																			 max(ddrq1_treat_marss$smap),length.out = 200),
														treat = unique(ddrq1_treat_marss$treat))		
newdat.mars.smap.2$marss.Rmeasspecific.Bunconstrained <- predict(m.mars.smap.2, newdat.mars.smap.2, re.form=NA)
mm.mars.smap.2 <- model.matrix(terms(m.mars.smap.2),newdat.mars.smap.2)
pvar1.mars.smap.2 <- diag(mm.mars.smap.2 %*% tcrossprod(vcov(m.mars.smap.2),mm.mars.smap.2))
newdat.mars.smap.2 <- data.frame(newdat.mars.smap.2,
															lower=newdat.mars.smap.2$marss.Rmeasspecific.Bunconstrained-cmult*sqrt(pvar1.mars.smap.2),
															upper=newdat.mars.smap.2$marss.Rmeasspecific.Bunconstrained+cmult*sqrt(pvar1.mars.smap.2))

newdat.mars.smap <- full_join(newdat.mars.smap.1,newdat.mars.smap.2)

newdat.mars.smap <- newdat.mars.smap %>%
	pivot_longer(cols = c("marss","marss.Rmeasspecific.Bunconstrained"), 
	             names_to = "Method", values_to = "interaction_estimate") %>%
	na.omit()

newdat.mars.smap$Method <- ifelse(newdat.mars.smap$Method=="marss",
																	"MARSS based on CCM interactions",
																	"MARSS based on all interactions")

marsplot1 <- ddrq1_treat_marss_long %>%
	dplyr::filter(Method != "S-map based on CCM interactions") %>%
  ggplot(aes(smap, interaction_estimate, group=treat, shape=treat, fill=Method, col=Method))+
	geom_abline(slope = 1, intercept = 0) +
  geom_point(size=2, alpha=0.33)+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
  standard_theme()+
  geom_line(aes(group=Method),data=newdat.mars.smap)+
  geom_ribbon(data=newdat.mars.smap, aes(ymax=upper,ymin=lower, group=Method), 
  						alpha=0.2, col=NA) +
	facet_wrap(~treat)+
	theme(legend.position = "none",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	labs(x="s-map", y="marss")  + 
	labs(y="MARSS interaction strength", x="S-map interaction strength", tag = "D", 
			 shape="Temperature", col="Estimation method", fill="Estimation method")


m.mars.rmse.1 <- lmer(RMSE~marss*treat + (1|ID), data = ddrq1_treat_marss)
newdat.mars.rmse.1 <- expand.grid(marss = seq(min(ddrq1_treat_marss$marss),
																							max(ddrq1_treat_marss$marss),length.out = 200),
																	treat = unique(ddrq1_treat_marss$treat))		
newdat.mars.rmse.1$RMSE <- predict(m.mars.rmse.1, newdat.mars.rmse.1, re.form=NA)
mm.mars.rmse.1 <- model.matrix(terms(m.mars.rmse.1),newdat.mars.rmse.1)
pvar1.mars.rmse.1 <- diag(mm.mars.rmse.1 %*% tcrossprod(vcov(m.mars.rmse.1),mm.mars.rmse.1))
newdat.mars.rmse.1 <- data.frame(newdat.mars.rmse.1,
																 lower=newdat.mars.rmse.1$RMSE-cmult*sqrt(pvar1.mars.rmse.1),
																 upper=newdat.mars.rmse.1$RMSE+cmult*sqrt(pvar1.mars.rmse.1))

m.mars.rmse.2 <- lmer(RMSE~marss.Rmeasspecific.Bunconstrained*treat + (1|ID), data = ddrq1_treat_marss)
newdat.mars.rmse.2 <- expand.grid(marss.Rmeasspecific.Bunconstrained = seq(min(ddrq1_treat_marss$marss.Rmeasspecific.Bunconstrained),
																																					 max(ddrq1_treat_marss$marss.Rmeasspecific.Bunconstrained),length.out = 200),
																	treat = unique(ddrq1_treat_marss$treat))		
newdat.mars.rmse.2$RMSE <- predict(m.mars.rmse.2, newdat.mars.rmse.2, re.form=NA)
mm.mars.rmse.2 <- model.matrix(terms(m.mars.rmse.2),newdat.mars.rmse.2)
pvar1.mars.rmse.2 <- diag(mm.mars.rmse.2 %*% tcrossprod(vcov(m.mars.rmse.2),mm.mars.rmse.2))
newdat.mars.rmse.2 <- data.frame(newdat.mars.rmse.2,
																 lower=newdat.mars.rmse.2$RMSE-cmult*sqrt(pvar1.mars.rmse.2),
																 upper=newdat.mars.rmse.2$RMSE+cmult*sqrt(pvar1.mars.rmse.2))

newdat.mars.rmse <- full_join(newdat.mars.rmse.1,newdat.mars.rmse.2)

newdat.mars.rmse <- newdat.mars.rmse %>%
	pivot_longer(cols = c("marss","marss.Rmeasspecific.Bunconstrained"),
	             names_to = "Method", values_to = "interaction_estimate") %>%
	na.omit()

newdat.mars.rmse$Method <- ifelse(newdat.mars.rmse$Method=="marss",
																	"MARSS based on CCM interactions",
																	"MARSS based on all interactions")

newdat_theta5 <- newdat_thetas %>% dplyr::filter(theta==5) %>%
	dplyr::select(treat, RMSE, lower.mean_mean_abs, upper.mean_mean_abs,mean_mean_abs) %>%
	dplyr::rename(lower=lower.mean_mean_abs, upper=upper.mean_mean_abs, interaction_estimate=mean_mean_abs) %>%
	na.omit()
newdat_theta5$Method <- "S-map based on CCM interactions"

newdat.mars.rmse <- full_join(newdat.mars.rmse,newdat_theta5)

marsplot2 <- ddrq1_treat_marss_long %>%
  ggplot(aes(interaction_estimate,RMSE, group=treat, shape=treat, fill=Method, col=Method))+
  geom_line(aes(group=Method),data=newdat.mars.rmse)+
  geom_ribbon(data=newdat.mars.rmse, aes(ymax=upper,ymin=lower, group=Method), 
  						alpha=0.2, col=NA) +
	geom_point(size=2, alpha=0.33)+
	scale_shape_manual(values=c(21,23))+
	scale_fill_brewer(palette = "Dark2", aesthetics = c("fill","col"))+
  standard_theme()+
  facet_wrap(~treat)+
	theme(legend.position = "right",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				plot.subtitle = ggtext::element_markdown()) +
	labs(x="Mean interaction strength (MARSS)", y="RMSE", tag="E",
			 shape="Temperature", col="Estimation method", fill="Estimation method")

rm(m.mars.smap.1,newdat.mars.smap.1,mm.mars.smap.1,pvar1.mars.smap.1,
	 m.mars.smap.2,newdat.mars.smap.2,mm.mars.smap.2,pvar1.mars.smap.2,newdat.mars.smap,
	 m.mars.rmse.1,newdat.mars.rmse.1,mm.mars.rmse.1,pvar1.mars.rmse.1,
	 m.mars.rmse.2,newdat.mars.rmse.2,mm.mars.rmse.2,pvar1.mars.rmse.2,newdat.mars.rmse)
```

## Other 

### Forecast skill across bottles

```{r bottle_forecasts, cache=TRUE, message=FALSE, warning=FALSE}
ranef.mv2 <- ranef(m.mv2, condVar=TRUE)[[1]]

ranef.mv2 <- data.frame(Target.ID=rownames(ranef.mv2),
                  int=unname(ranef.mv2),
                  se=sqrt(c(attr(ranef.mv2,"postVar"))))

Target.ID <- strsplit(rownames(ranef.mv2),":")
ranef.mv2$Target <- unlist(map(Target.ID, 1))
ranef.mv2$ID <- unlist(map(Target.ID, 2))
ranef.mv2 <- transform(ranef.mv2,ID=reorder(ID,int))
ranef.mv2$Target2 <- label[as.character(ranef.mv2$Target)]

ranef.plot.list <- lapply(unique(ranef.mv2$Target), function(tar){
	ranef.mv2 %>%
		dplyr::filter(Target==tar) %>%
		mutate(ID=reorder(ID,int)) %>%
		ggplot(aes(ID,int,ymin=int-1.96*se,ymax=int+1.96*se)) +
		geom_hline(yintercept = 0) +
		geom_pointrange() +
		standard_theme2() +
		theme(strip.text = ggtext::element_markdown()) +
		facet_wrap(~Target2)+
		ylim(-.4,.4) +
		coord_flip()+
		labs(y="Intercept", x="Bottle ID") 
})

ranef.mv2 <- ranef.mv2 %>%
	group_by(Target) %>%
	mutate(rank = factor(rank(int), ordered = T, levels = 1:18))

ranef.mv2 <- ranef.mv2 %>%
	ungroup() %>%
	group_by(ID) %>%
	mutate(mean_rank=mean(as.numeric(rank)))

ranef.mv2_summarized <- ranef.mv2 %>%
	group_by(ID) %>%
	summarise(mean_intercept = mean(int),
						sd_intercept = sd(int))

ranef.mv2_summarized$facet <- "Across all targets"
bottle.mean.plot <- ranef.mv2_summarized %>% 
  ggplot(aes(ID, mean_intercept, ymin=mean_intercept-sd_intercept,
             ymax=mean_intercept+sd_intercept)) +
  geom_pointrange() +
	geom_hline(yintercept = 0) +
	coord_flip() +
	facet_wrap(~facet) +
	labs(y="Intercept", x="Bottle ID") +
	standard_theme2()
```

### Choosing k 

The following chunk is not run, results are loaded in later on.

```{r choose_k, cache=TRUE, message=FALSE, warning=FALSE, eval=FALSE}
possible_predictors <- c("bacteria","chlamydomonas_reinhardtii","colpidium_striatum",
                         "dexiostomata_campylum", "euglena_gracilis", "euplotes_daidaleos",
                         "paramecium_caudatum", "rotifer_sp")
ids <- c("B01","B04","B07","B10","B13","B16")
output <- data.frame(target=character(),k=numeric(),rmse=numeric(),ID=character())
set.seed(32)
k <- seq(5,200,by = 5)
cl <- makeCluster(detectCores()-1)
registerDoParallel(cl = cl)
for(i in possible_predictors){
  for(j in ids){
    predictors <- sample(possible_predictors[possible_predictors!=i], 4, replace = F)
    predictors <- c(i,predictors)
    ddtest <- dd2 %>% ungroup() %>% dplyr::filter(ID == j) %>% select(predictors)
    columns <- paste(predictors, collapse = " ")

    test_list <- foreach(x = seq(5,200,by = 5), .packages = loadedNamespaces(),
                         .export = ls(globalenv())) %dopar% {
      mv_wrapper(data = ddtest, k = x, columns = columns, target = i, E = 3,
                 max_lag = 3, excludeTarget = F)}
    test_list2 <- lapply(test_list, "[[", 2)
    rmse <- sapply(test_list2,
                   function(x) sqrt(mean((x$Observations-x$Predictions)^2,
                                         na.rm = T)))
    output <- rbind(output,data.frame(target=i,k=k,rmse=rmse,ID=j))
  }
}
stopCluster(cl)

output$target <- as.character(output$target)

dd_choose_k <- output %>%
  group_by(target,ID) %>%
  mutate(perc_change = lag(100*(rmse-lead(rmse))/rmse))

save(dd_choose_k, file = here("Data/Multiview_forecast_data/dd_choose_k.Rdata"))
```


### Predictor importance for targets Euglena and Chlamydomonas

```{r}
m.pred.imp.eug <- lmer(RMSE~log10.mean.abs*treat + (1|ID),
                       data = ddrq1_importance %>% dplyr::filter(target=="euglena_gracilis"))
m.pred.imp.chl <- lmer(RMSE~log10.mean.abs*treat + (1|ID), 
                       data = ddrq1_importance %>% dplyr::filter(target=="chlamydomonas_reinhardtii"))
# summary(m.pred.imp.eug)
# summary(m.pred.imp.chl)


predimport.eug.chla.tab <- data.frame(Target=c(rep("\\textit{E. gracilis}",5),rep("\\textit{C. reinhardtii}",5)),
                                      Covariate = c("Intercept","A: log10(mean int. strength)",
                                                    "B: Fluctuating temperature", "Interaction: A:B","Bottle ID",
                                                    "Intercept}","A: log10(mean int. strength)",
                                                    "B: Fluctuating temperature}", "Interaction: A:B","Bottle ID"),
                                      Type = rep(c(rep("Fixed",4),"Std. Dev."),2),
                                      Coefficient = c(fixef(m.pred.imp.eug),as.data.frame(VarCorr(m.pred.imp.eug))$sdcor[1],
                                                      fixef(m.pred.imp.chl),as.data.frame(VarCorr(m.pred.imp.chl))$sdcor[1]),
                                      Std.err = c(summary(m.pred.imp.eug)$coef[,2,drop = FALSE],NA,
                                                  summary(m.pred.imp.chl)$coef[,2,drop = FALSE],NA),
                                      Test = rep(c(rep("\\textit{t}",4),"$\\chi^2$"),2),
                                      Test.value = c(summary(m.pred.imp.eug)$coef[,4,drop = FALSE],lmerTest::rand(m.pred.imp.eug)$LRT[2],
                                                     summary(m.pred.imp.chl)$coef[,4,drop = FALSE],lmerTest::rand(m.pred.imp.chl)$LRT[2]),
                                      p.value = c(summary(m.pred.imp.eug)$coef[, 5, drop = FALSE],lmerTest::rand(m.pred.imp.eug)$`Pr(>Chisq)`[2],
                                                  summary(m.pred.imp.chl)$coef[, 5, drop = FALSE],lmerTest::rand(m.pred.imp.chl)$`Pr(>Chisq)`[2]))
```


### Alternative analysis of predictor importance 1

```{r multiview_forecast_analysis_13, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
possible_predictors <- c("bacteria","chlamydomonas_reinhardtii","colpidium_striatum",
                         "dexiostomata_campylum", "didinium_nasutum",
                         "euglena_gracilis","euplotes_daidaleos","paramecium_caudatum",
                         "rotifer_sp","big_white_particle","dissolved_oxygen",
                         "green_white_particle", "small_white_particle",
                         "temperature")

predictor_combinations <- predictor_combinator(possible_predictors, which=13, rmTfrompred = F, temperature.included = F)

ks <- unique(round(exp(seq(log(0.8),log(100.4),length.out = 33))))

dd2 <- dd2 %>% ungroup()
set.seed(98)

dd_forecast13 <- lapply(targets, function(target){
  df1 <- model_fitter_wrapper(whole.data = dd2, 
                              predictor_combinations = predictor_combinations,
                              target = target,
                              num.clusters = detectCores() - 1, 
                              E = 3, max_lag = 3, k=ks)
})

dd_forecast13 <- do.call("rbind", dd_forecast13)

dd_forecast13$predictor_combination <- as.character(dd_forecast13$predictor_combination)
temp <- matrix(F, nrow = nrow(dd_forecast13), ncol = length(possible_predictors))
colnames(temp) <- possible_predictors
dd_forecast13 <- cbind(dd_forecast13,temp)

dd_forecast13 <- as.data.frame(t(apply(dd_forecast13, 1, function(row) { 
  str <- unlist(strsplit(row["predictor_combination"], " "))
  row[str] <- T
  row
})))

dd_forecast13$num_pred <- as.numeric(dd_forecast13$num_pred)
dd_forecast13$num_pred_without_temp <- as.numeric(dd_forecast13$num_pred_without_temp)
dd_forecast13$RMSE <- as.numeric(dd_forecast13$RMSE)
dd_forecast13$k <- as.numeric(dd_forecast13$k)
for(i in possible_predictors){  dd_forecast13[,i] <- as.logical(dd_forecast13[,i])}

save(dd_forecast13, file = here("Data/Multiview_forecast_data/dd_forecast13.RData"))
```

```{r multiview_forecast_analysis_13_2, message=FALSE, warning=FALSE, cache=TRUE}
load(here("Data/Multiview_forecast_data/dd_forecast13.RData"))

possible_predictors <- c("bacteria","chlamydomonas_reinhardtii","colpidium_striatum",
                         "dexiostomata_campylum", "didinium_nasutum",
                         "euglena_gracilis","euplotes_daidaleos","paramecium_caudatum",
                         "rotifer_sp","big_white_particle","dissolved_oxygen",
                         "green_white_particle", "small_white_particle",
                         "temperature")

dd_forecast13$excluded_predictor <- apply(dd_forecast13, 1, function(row){
  s <- unlist(strsplit(row["predictor_combination"]," "))
  idx <- which(possible_predictors %in% s)
  possible_predictors[-idx]
})


# rmse.full <- ddrq1[ddrq1$num_pred==14, "RMSE"]

dd_forecast13$RMSE_dif <- NA
dd_forecast13.split <- split(dd_forecast13, f=dd_forecast13$ID)
dd_forecast13.split <- lapply(dd_forecast13.split, function(df){
  bottle <- unique(df$ID)
  df <- apply(df, 1, function(row){
    tar <- row["Target"]
    rmse.full <- ddrq1[ddrq1$num_pred==14 & ddrq1$ID==bottle & ddrq1$Target==tar, "RMSE"]
    row["RMSE_dif"] <- as.numeric(row["RMSE"]) - rmse.full
    row
  })
  df <- as.data.frame(t(df))
  df
})
dd_forecast13 <- do.call("rbind", dd_forecast13.split)
dd_forecast13$RMSE_dif <- as.numeric(dd_forecast13$RMSE_dif)
dd_forecast13$target <- dd_forecast13$Target
dd_forecast13$interactor <- dd_forecast13$excluded_predictor
dd_forecast13 <- inner_join(dd_forecast13, dd_mean_is)
dd_forecast13$log10.mean.abs <- log10(dd_forecast13$mean.abs)
dd_forecast13$treat <- ifelse(dd_forecast13$treat=="const","Constant","Fluctuating")
dd_forecast13$interactor <- factor(label[dd_forecast13$interactor], levels = order.interactors)
dd_forecast13$Target <- factor(label[dd_forecast13$Target], levels = order.targets)
```

### CCM vs mean interaction strength

```{r ccm.int.strength, fig.width=13, fig.height=4, out.width="95%", cache=TRUE, message=FALSE}
significant_pairwise_ccm_df <- pairwise_ccm_df %>%
	dplyr::filter(significances<0.05, rho >0)

ddrq1_importance2 <- significant_pairwise_ccm_df %>%
	dplyr::mutate(Target=as.factor(label[target]),
								interactor=as.factor(label[interactor])) %>%
	dplyr::select(Target,ID,rho,interactor)

ddrq1_importance2 <- dplyr::full_join(ddrq1_importance,ddrq1_importance2)

ccm.int.strength.list <- split(ddrq1_importance2, ddrq1_importance2$Target)

ccm.int.strength.list <- lapply(1:length(ccm.int.strength.list), function(i){
	df <- ccm.int.strength.list[[i]]
	nd <- newdat.m.pred.imp %>% dplyr::filter(Target==unique(df$Target))
	plot <- df %>%
		ggplot(aes(rho,log10.mean.abs, shape=treat))+
		geom_point(aes(fill=interactor),size=2, col="black")+
		facet_wrap(~treat, ncol = 4) +
		geom_smooth() +
		labs(subtitle = unique(df$Target), tag=tag[i], x=expression('log'[10]~"(Mean interaction strength)")) +
		scale_shape_manual(values=c(21,23))+
		scale_color_manual(breaks = levels(ddrq1_importance2$interactor),
											 values = palette2, aesthetics = c("fill","color"))+
		standard_theme() +
		theme(legend.position = "none",
					panel.spacing =  unit(0, "lines"),
					axis.title = element_blank(),
					strip.text.x = element_blank(),
					legend.text = ggtext::element_markdown(),
					plot.subtitle = ggtext::element_markdown()) +
    guides(col=guide_legend(ncol=2))
	
	# if(unique(df$target) %in% c("chlamydomonas_reinhardtii","euglena_gracilis")){
	# 	plot <- plot + 	
	# 		geom_ribbon(data=nd, aes(ymin=lower, ymax=upper, y=RMSE), alpha=0.2, col=NA)+
	# 		geom_line(data=nd, aes(log10.mean.abs,RMSE))
	# }
	plot
})

ccm.int.strengthleg <- ddrq1_importance2 %>%
	ggplot(aes(rho, log10.mean.abs,shape=treat))+
	geom_point(aes(col=interactor,fill=interactor),size=2,)+
	facet_wrap(~treat, ncol = 4) +
	scale_color_manual(breaks = levels(ddrq1_importance2$interactor),
										 values = palette2, aesthetics = c("fill","color"))+
	standard_theme() +
	scale_shape_manual(values=c(21,23))+
	theme(legend.position = "right",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				legend.text = ggtext::element_markdown(size = 11),
				plot.subtitle = ggtext::element_markdown()) +
	labs(shape="Temperature", fill= "Interactor/Predictor", col="Interactor/Predictor") +
	geom_smooth(method = "lm")+
	guides(col=guide_legend(ncol=2))

ccm.int.strengthleg <- get_legend(ccm.int.strengthleg)

ylab <- ggplot(data.frame(x = 1, y = 1)) +
	geom_text(aes(x, y), label = expression('    log'[10]~"(Mean interaction strength)"), angle = 90, size=6) +
	theme_void() +
	coord_cartesian(clip = "off")

xlab <- ggplot(data.frame(x = 1, y = 1)) +
	geom_text(aes(x, y), label = "Cross mapping skill (CCM)", size=6) +
	theme_void() +
	coord_cartesian(clip = "off")

ccm.int.strength.plot <- ((ylab + ((Reduce("+", ccm.int.strength.list) + plot_layout(ncol = 2)) / xlab + plot_layout(heights = c(50,1))) + ccm.int.strengthleg + plot_layout(widths = c(2,80,20))))
```



# Supplementary material: Figures and tables

General note on tables: their code was written for latex, meaning that some properties will not be displayed correctly in markdown.

## Regression and anova tables of the main text

```{r rq1tab, cache=TRUE}
tab.rq1.theta5$p.value <- ifelse(tab.rq1.theta5$p.value<0.001, "<0.001",
																 sprintf("%.3f", round(tab.rq1.theta5$p.value,3)))
options(knitr.kable.NA = '-')
tab.rq1.theta5 %>%
	dplyr::select(-theta) %>%
	mutate_all(linebreak, align="l") %>%
	kable(booktabs = T, digits = 3,
				col.names = c("Response", "Covariate" ,"Type", "Coefficient", "Std. Err.", "Test", "Value", "\\textit{p}-value"),
				caption = "The main regression table for the four models fitted respectively for the relation between the forecast RMSE and the number of interactions, between the forecast RMSE and the mean interaction strength, between the mean interaction strength and the number of interactions as well as between the forecast RMSE and the sum of interaction strengths.",
				align = c("lllrrlrr"), escape = F,
				label = "rq1tab") %>%
	collapse_rows(columns = 1, latex_hline ='custom', custom_latex_hline = 1,
								valign = "middle")%>%
	kable_styling(font_size = 7,latex_options = "hold_position")
```


```{r mv.tab, cache = TRUE}
mv.tab$p.value <- ifelse(mv.tab$p.value<0.001, "<0.001",
												 sprintf("%.3f", round(mv.tab$p.value,3)))
options(knitr.kable.NA = '-')
rownames(mv.tab) <- NULL 
kable(mv.tab,
			booktabs = T, digits = 3,
			col.names = c("Covariate","Type","Estimate","DF","Std. Err.", "Test", "Value", "\\textit{p}-value"),
			caption = "Regression and anova combination table for the mixed effects model of forecast skill as a function of the number of predictors, temperature regime and whether temperature was used as a predictor or not.", align = c("llrrrcrr"), escape = F,
			label = "rqtab1")%>% 
	kable_styling(font_size = 7) %>%
	pack_rows("D: Target species", 5, 11, bold = T) %>%
	pack_rows("Interaction: B:D", 15, 21, bold = T) %>%
	pack_rows("Interaction: A:D", 22, 28, bold = T) %>%
	pack_rows("Interaction: C:D", 29, 35, bold = T) %>%
	row_spec(35, hline_after = T) %>%
	row_spec(45, hline_after = T) 
```

```{r tab.num_vs_num, cache = TRUE}
tab.num_vs_num$p.value <- ifelse(tab.num_vs_num$p.value<0.001, "<0.001",
												 sprintf("%.3f", round(tab.num_vs_num$p.value,3)))
rownames(tab.num_vs_num) <- NULL
options(knitr.kable.NA = '-')

kable(tab.num_vs_num,
			booktabs = T, digits = 3,
			col.names = c("Covariate","Variable type","Coefficient","Std. Err.", "Test", "Value", "\\textit{p}-value"),
			caption = "The regression table for the mixed model with the number of predictors in the best focast model as the repsonse variable and the number of interaction as the explanatory variable.", align = c("llrrcrr"), escape = F,
			label = "num_vs_num")%>%
	kable_styling(font_size = 7)
```

```{r mv.interactopredictor, cache = TRUE}
mv.interactopredictor$p.value <- ifelse(mv.interactopredictor$p.value<0.001, "<0.001",
												 sprintf("%.3f", round(mv.interactopredictor$p.value,3)))
rownames(mv.interactopredictor) <- NULL
options(knitr.kable.NA = '-')

kable(mv.interactopredictor,
			booktabs = T, digits = 3,
			col.names = c("Covariate","Type","Estimate","DF","Std. Err.", "Test", "Value", "\\textit{p}-value"),
			caption = "Regression and anova combination table for the mixed effects that assessed whether species that interacted strongly witha a target species also were good predictors of said target species.", align = c("llrcrr"), escape = F,
			label = "predictor_interactor")%>%
	kable_styling(font_size = 7)  %>%
	pack_rows("C: Target species", 4, 10, bold = T) %>%
	pack_rows("Interaction: A:C", 12, 18, bold = T) %>%
	pack_rows("Interaction: B:C", 19, 25, bold = T) %>%
	pack_rows("Interaction: A:B:C", 26, 32, bold = T) %>%
	row_spec(32, hline_after = T) %>%
	row_spec(39, hline_after = T) 
```

## Experiment supplementary information

### Temperature time series

```{r temperature_plot, fig.width=8, fig.height=2.5, out.width="95%"}
temperature.df <- dd %>%
	dplyr::filter(variable=="temperature", 
								ID %in% c("B01","B10","B13","B16")) %>%
	dplyr::mutate(response = case_when(treat=="treat" ~ response,
																		 treat!="treat" ~ 17.3))

temperature.df$ID <- ifelse(temperature.df$ID=="B01", "Constant temperature",
                ifelse(temperature.df$ID=="B16", "Fluctuating temperature\ntime series 1 (original)",
                       ifelse(temperature.df$ID=="B13","Fluctuating temperature\ntime series 2 (synthetic)",
                              "Fluctuating temperature\ntime series 3 (synthetic)")))

temperature.df %>%
  ggplot(aes(day,response)) +
  geom_line()+
  facet_wrap(~ID, ncol = 4) +
  theme_bw() +
  theme(legend.position = "none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black"),
        strip.text = element_text(size=10)) +
  labs(y="Temperature (C)",x="Time (days)")
```

### Recorded time series

```{r plot_original_ts, fig.width=11, fig.height=13, out.width="95%", cache=TRUE}
vars <- c("bacteria", "chlamydomonas_reinhardtii", "colpidium_striatum", "dexiostomata_campylum",
					"didinium_nasutum", "euglena_gracilis", "euplotes_daidaleos", "paramecium_caudatum",
					"rotifer_sp", "big_white_particle", "small_white_particle", "green_white_particle",
					"spirostomum_sp","dissolved_oxygen")

dd_plot <- dd %>%
	dplyr::filter(variable %in% vars) %>%
	mutate(treat2 = case_when(treat2 == "constant_1" ~ "Constant 1",
                            treat2 == "constant_2" ~ "Constant 2",
                            treat2 == "constant_3" ~ "Constant 3",
                            treat2 == "fluctuating_1" ~ "Fluctuating 1",
                            treat2 == "fluctuating_2" ~ "Fluctuating 2",
                            treat2 == "fluctuating_3" ~ "Fluctuating 3"))

dd_plot$order <- factor(dd_plot$variable, levels = vars) 
dd_plot <- dd_plot[order(dd_plot$order),] 
dd_plot_list <- split(dd_plot, dd_plot$order)

dd_plot_list <- lapply(1:length(dd_plot_list), function(i){
  df <- dd_plot_list[[i]]
  df <- df %>%
    ggplot(aes(day, response, col=treat2, group=ID))+
    geom_line()+
    facet_wrap(~treat) +
    labs(x="Time (days)", subtitle = label[unique(df$variable)], y="Density\n(cells/ml)",
    		 col="Temperature", tag = tag[i]) +
    theme_bw() +
    standard_theme() +
    scale_color_brewer(palette = "Dark2")+
    theme(legend.position = "none",
          panel.spacing =  unit(0, "lines"),
          strip.text.x = element_blank(),
    			plot.subtitle = ggtext::element_markdown()) +
    guides(col=guide_legend(ncol=2))

  if(i %in% c(2,4,6,8,10,12)){
    df <- df + theme(axis.title = element_blank(), axis.text.x = element_blank(), axis.ticks.x=element_blank())
  }
  if(i == 14){
    df <- df + theme(axis.title.y = element_blank(),
                     legend.position = "bottom")
  }
  if(i %in% c(1,3,5,7,9,11)){
    df <- df + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x=element_blank())
  }
  df
})

plot_original_leg <- get_legend(dd_plot_list[[14]])
dd_plot_list[[14]] <- dd_plot_list[[14]] + theme(legend.position = "none")

(Reduce("+", dd_plot_list) + plot_layout(ncol = 2))/(plot_original_leg) + plot_layout(heights = c(11,1))
```

Transformed time series

```{r plot_original_ts_transf, fig.width=11, fig.height=13, out.width="95%", cache=TRUE, warning=FALSE, message=FALSE}
vars <- c("bacteria", "chlamydomonas_reinhardtii", "colpidium_striatum", "dexiostomata_campylum",
					"didinium_nasutum", "euglena_gracilis", "euplotes_daidaleos", "paramecium_caudatum",
					"rotifer_sp", "big_white_particle", "small_white_particle", "green_white_particle",
					"temperature","dissolved_oxygen")
 
dd_plot <- dd2_long %>% 
	dplyr::filter(variable %in% vars) %>%
	mutate(treat2 = case_when(treat2 == "constant_1" ~ "Constant 1",
                            treat2 == "constant_2" ~ "Constant 2",
                            treat2 == "constant_3" ~ "Constant 3",
                            treat2 == "fluctuating_1" ~ "Fluctuating 1",
                            treat2 == "fluctuating_2" ~ "Fluctuating 2",
                            treat2 == "fluctuating_3" ~ "Fluctuating 3"))

dd_plot$order <- factor(dd_plot$variable, levels = vars)
dd_plot <- dd_plot[order(dd_plot$order),]


dd_plot_list <- split(dd_plot, dd_plot$order)

dd_plot_list <- lapply(1:length(dd_plot_list), function(i){
  df <- dd_plot_list[[i]]
  df <- df %>%
    ggplot(aes(day, response, col=treat2, group=ID))+
    geom_line()+
    facet_wrap(~treat) +
    labs(x="Time (days)", subtitle = label[unique(df$variable)], y="Density\n(cells/ml)",
    		 col="Temperature", tag = tag[i]) +
    theme_bw() +
    standard_theme() +
    scale_color_brewer(palette = "Dark2")+
    theme(legend.position = "none",
          panel.spacing =  unit(0, "lines"),
          strip.text.x = element_blank(),
    			plot.subtitle = ggtext::element_markdown()) +
    guides(col=guide_legend(ncol=2))

  if(i %in% c(2,4,6,8,10,12)){
    df <- df + theme(axis.title = element_blank(), axis.text.x = element_blank(), axis.ticks.x=element_blank())
  }
  if(i == 14){
    df <- df + theme(axis.title.y = element_blank(),
                     legend.position = "bottom")
  }
  if(i %in% c(1,3,5,7,9,11)){
    df <- df + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x=element_blank())
  }
  df
})

plot_original_leg <- get_legend(dd_plot_list[[14]])
dd_plot_list[[14]] <- dd_plot_list[[14]] + theme(legend.position = "none")

(Reduce("+", dd_plot_list) + plot_layout(ncol = 2))/(plot_original_leg) + plot_layout(heights = c(11,1))
```

## Multiview EDM related figures

### Figure for choosing k

```{r choose_k_plot, fig.width=11, fig.height=6, out.width="95%", cache=TRUE, warning=FALSE, message=FALSE}
load(here("Data/Multiview_forecast_data/dd_choose_k.Rdata"))

rmsemax <- dd_choose_k %>%
  group_by(target,ID) %>%
  summarize(min=min(rmse), k = k[which.min(rmse)])
rmsemaxvalue <- max(dd_choose_k$rmse)

choose_k_list <- split(dd_choose_k, dd_choose_k$target)

choose_k_list <- lapply(1:length(choose_k_list), function(i){
  df <- choose_k_list[[i]]
  df <-
  	df %>%
  	dplyr::filter(abs(perc_change)<6)%>%
  	ggplot(aes(k,perc_change,col=ID))+
  	geom_hline(yintercept = 1, col="black", linetype=2)+
  	geom_hline(yintercept = 0, col="black", linetype=2)+
  	geom_vline(xintercept = 100, col="black", linetype=2) +
  	geom_line(na.rm = T)+
    labs(subtitle = label[unique(df$target)], y="Forecast skill\npercentage change", x="k-value",
    		 col="Bottle", tag = tag[i]) +
    theme_bw() +
    standard_theme() +
    scale_color_brewer(palette = "Dark2")+
    theme(legend.position = "none",
          panel.spacing =  unit(0, "lines"),
          strip.text.x = element_blank(),
    			plot.subtitle = ggtext::element_markdown())
  if(i==1){
  	df <- df + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x=element_blank(),
  									 legend.position = "bottom") + guides(col=guide_legend(ncol=6))
  }
  if(i %in% c(2,3,4)){
  	df <- df + theme(axis.title = element_blank(), axis.text.x = element_blank(), axis.ticks.x=element_blank())
  }
  if(i %in% c(6,7,8)){
  	df <- df + theme(axis.title.y = element_blank())
  }
  df
  })

plot_kplot_leg <- get_legend(choose_k_list[[1]])
choose_k_list[[1]] <- choose_k_list[[1]] + theme(legend.position = "none")

(Reduce("+", choose_k_list) + plot_layout(ncol = 4))/(plot_kplot_leg) + plot_layout(heights = c(11,1))
```

### The number of multiview models fitted (main text)

```{r model.tab, cache=TRUE}
model.table <- data.frame(number_of_predictors=c(1,2,3,4,6,8,10,13))
model.table$choose_n_from_13 <- choose(13,model.table$number_of_predictors)
model.table$number_of_predictor_combos <- ifelse(model.table$choose_n_from_13>200,200,model.table$choose_n_from_13)
model.table$number_of_lagged_predictors_for_n_predictors <- choose(3*model.table$number_of_predictors,3)
model.table$number_of_different_k_values <- sapply(model.table$number_of_lagged_predictors_for_n_predictors,
                                                   function(x){sum(ks<=x)})
model.table$number_of_predictor_combos_TIMES_number_of_different_k_values <-
  model.table$number_of_predictor_combos*model.table$number_of_different_k_values
number_of_models <- sum(model.table$number_of_predictor_combos_TIMES_number_of_different_k_values)*8*18

colnames(model.table) <- c("Nr. of\npredictors $n$","Nr. of combinations\n$\\binom{13}{n}$",
																"Used nr. of\ncombinations","Nr. of different\nembeddings $m=\\binom{n l}{E}$",
																"Nr. of used\n embedings ($k$)","Nr. of\nmodels")
kable(model.table,
			booktabs = T, escape = F,
			col.names = linebreak(colnames(model.table)),
			label="model", align = "c", caption = "Table listing the number of predictors and the respective number of different combinations, the number of used combinations, the number of different possible embeddings, the number of used embeddings and the number of fitted models. The last column (number of fitted models for a given number of predictors) is calculated by multiplying the number of used predictor combinations with the number of used embeddings ($k$). The total number of fitted models is calculated by summing the last column and multiplying the result by 8 (number of targets), 18 (number or bottles) and 2 (the prediction is repetead with temperature included as a predictor) and then adding 1 (the model with only temperature as a predictor). See the main text for more information.")  %>%
	# column_spec(1:6, width = "2.4cm") %>%
  kable_styling(font_size = 8)
```


### Forecast skill maxima vs number of predictors

```{r num_pred_vs_min_rmse, fig.width=13, fig.height=6, out.width="95%", cache=TRUE, message=FALSE}
ddrq1_summarized %>%
  ggplot(aes(num_pred, min_rmse,
             group=interaction(ID,interaction),
             col=interaction))+
  geom_point(na.rm = T, size=0.8)+
  geom_line(size=0.5, alpha=0.35)+
  standard_theme2()+
  theme(legend.position = "bottom", strip.text = ggtext::element_markdown())+
  scale_color_manual(values = cbbPalette, aesthetics = c("col","fill"),
                    labels = c("Constant & Not a predictor","Constant & Predictor",
                    					 "Fluctuating & Not a predictor","Fluctuating & Predictor")) +
  facet_wrap(~Target2, ncol = 4) +
  labs(y="Lowest achieved RMSE",x="Number of predictors used", col="Temperature") +
  guides(col=guide_legend(nrow=2,byrow=TRUE))
```


### Forecast skill across bottles

```{r bottle_id_plot, fig.width=12, fig.height=10, out.width="95%", cache=TRUE, message=FALSE}
Reduce("+", ranef.plot.list) + bottle.mean.plot + plot_annotation(tag_levels = 'A') 
```

## Number of interactions per target per bottle

```{r number_of_int_spec, fig.width=12, fig.height=4, out.width="95%"}
num_int_plot
```

## Distribution of pairwise mean interaction strengths

```{r is_distr, cache=TRUE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="95%"}
dd_mean_is %>%
	ggplot(aes(abs(mean)))+
	geom_histogram(bins = 15)+
	standard_theme2()+
	labs(x="Absolute values of pairwise mean interaction strengths", y="Count")+
	facet_wrap(~ID, ncol = 4)
```


## Post-hoc test to investigate the effect of temperature fluctuations on forecast skill

```{r, fig.height=6, fig.width=10, cache=TRUE}
m.mv2.emm <- emmeans(m.mv2, c("treat"), by="Target")
contrasts.tab <- as.data.frame(pairs(m.mv2.emm))
contrasts.tab$contrast <- "Constant - Fluctuating"
contrasts.tab$Target <- c("Bacteria","\\textit{C. reinhardtii}",
                      "\\textit{C. striatum}", "\\textit{D. campylum}",
                      "\\textit{E. gracilis}", "\\textit{E. daidaleos}", 
                      "\\textit{P. caudatum}", "\\textit{Rotifer} sp.")

facet.labs <- c("Bacteria","*Chlamydomonas reinhardtii*","*Colpidium striatum*",
                "*Dexiostoma campylum*", "*Euglena gracilis*", "*Euplotes daidaleos*",
                "*Paramecium caudatum*", "*Rotifer* sp.")
names(facet.labs) <- c("bacteria","chlamydomonas_reinhardtii","colpidium_striatum",
                       "dexiostomata_campylum","euglena_gracilis","euplotes_daidaleos",
                       "paramecium_caudatum","rotifer_sp")

contrast.plot <- plot(m.mv2.emm, comparisons = TRUE)
contrast.plot +
  standard_theme() +
  labs(x="Mean RMSE", y="Temperature") +
  scale_y_discrete(breaks=c("treat","const"), labels=c("Fluctuating","Constant"))+
  facet_wrap(~Target, ncol = 2, labeller = labeller(Target = facet.labs)) +
  theme(strip.text = ggtext::element_markdown())
```

```{r contrast_tab, cache=TRUE}
contrasts.tab$p.value <- ifelse(contrasts.tab$p.value<0.001, "<0.001",
														 sprintf("%.3f", round(contrasts.tab$p.value,3)))
options(knitr.kable.NA = '-')
rownames(contrasts.tab) <- NULL 
contrasts.tab %>%
	mutate_all(linebreak, align="l") %>%
	kable(booktabs = T, digits = 3,
				col.names = c("Constant", "Target", "Estimate" ,"Std. Err.", "DF", "\\textit{t}-value", "\\textit{p}-value"),
				caption = "contrast table. caption to be done",
				align = c("llllrrlrr"), escape = F,
				label = "contrasts") %>%
	kable_styling(font_size = 7)
```


## Predictor importance: further analyses

```{r pred_imp_plot_13, fig.width=13, fig.height=9, out.width="95%", cache=TRUE, message=FALSE, warning=FALSE}
dd_forecast13_list <- split(dd_forecast13, dd_forecast13$Target)

dd_forecast13_list <- lapply(1:length(dd_forecast13_list), function(i){
	df <- dd_forecast13_list[[i]]
	plot <- df %>%
		ggplot(aes(log10.mean.abs, shape=treat, RMSE_dif))+
		geom_point(aes(fill=interactor),size=2, col="black")+ 
		facet_wrap(~treat, ncol = 4) +
		labs(subtitle = unique(df$Target), tag=tag[i], x=expression('log'[10]~"(Mean interaction strength)")) +
		scale_shape_manual(values=c(21,23))+
		scale_color_manual(breaks = levels(ddrq1_importance$interactor),
											 values = palette2, aesthetics = c("fill","color"))+
		standard_theme() +
		theme(legend.position = "none",
					panel.spacing =  unit(0, "lines"),
					axis.title = element_blank(),
					strip.text.x = element_blank(),
					legend.text = ggtext::element_markdown(),
					plot.subtitle = ggtext::element_markdown()) +
    guides(col=guide_legend(ncol=2))

	plot
})

m.pred.imp.plot.leg <- dd_forecast13 %>%
	ggplot(aes(log10.mean.abs,RMSE_dif,shape=treat))+
	geom_point(aes(col=interactor,fill=interactor),size=2,)+
	facet_wrap(~treat, ncol = 4) +
	scale_color_manual(breaks = levels(dd_forecast13$interactor),
										 values = palette2, aesthetics = c("fill","color"))+
	standard_theme() +
	scale_shape_manual(values=c(21,23))+
	theme(legend.position = "right",
				panel.spacing =  unit(0, "lines"),
				strip.text.x = element_blank(),
				legend.text = ggtext::element_markdown(size = 11),
				plot.subtitle = ggtext::element_markdown()) +
	labs(shape="Temperature", fill= "Interactor/Predictor", col="Interactor/Predictor") +
	guides(col=guide_legend(ncol=2))

m.pred.imp.plot.leg <- get_legend(m.pred.imp.plot.leg)

ylab <- ggplot(data.frame(l = "    Predictor importance", x = 1, y = 1)) +
	geom_text(aes(x, y, label = l), angle = 90, size=6) +
	theme_void() +
	coord_cartesian(clip = "off")

xlab <- ggplot(data.frame(x = 1, y = 1)) +
	geom_text(aes(x, y), label = expression('log'[10]~"(Mean interaction strength)"), size=6) +
	theme_void() +
	coord_cartesian(clip = "off")

plot4_13 <- ((ylab + ((Reduce("+", dd_forecast13_list) + plot_layout(ncol = 2)) / xlab + plot_layout(heights = c(50,1))) + m.pred.imp.plot.leg + plot_layout(widths = c(2,80,20))))
plot4_13
```


### Predictor importance for targets Euglena and Chlamydomonas

```{r tab.eug.chlam.importance, fig.width=13, fig.height=4, out.width="95%", cache=TRUE, message=FALSE}
predimport.eug.chla.tab$p.value <- ifelse(predimport.eug.chla.tab$p.value<0.001, "<0.001",
																 sprintf("%.3f", round(predimport.eug.chla.tab$p.value,3)))
options(knitr.kable.NA = '-')
predimport.eug.chla.tab %>%
	mutate_all(linebreak, align="l") %>%
	kable(booktabs = T, digits = 3,
				col.names = c("Target", "Covariate" ,"Type", "Coefficient", "Std. Err.", "Test", "Value", "\\textit{p}-value"),
				caption = "Caption to be added.",
				align = c("lllrrlrr"), escape = F,
				label = "rq1tab") %>%
	collapse_rows(columns = 1, latex_hline ='custom', custom_latex_hline = 1,
								valign = "middle")%>%
	kable_styling(font_size = 7,latex_options = "hold_position")
```


### CCM vs mean interaction strength

```{r ccm.int.strength.plot, fig.width=13, fig.height=9, echo=FALSE, out.width="95%", cache=TRUE, message=FALSE, warning=FALSE}
ccm.int.strength.plot 
```



## Species interactions robustness analyses

### Sensitivity analysis for the parameter $\theta$

```{r mean_int_rmse_plot_thetas, fig.width=13, fig.height=4, out.width="95%", cache=TRUE, message=FALSE}
thetaplot1 + thetaplot2 + thetaplot3
```

```{r rq1tab_sens, cache=TRUE}
tab.rq1.theta3$theta <- "$\\theta=3$"
tab.rq1.theta7$theta <- "$\\theta=7$"
tab.rq1.theta <- rbind(tab.rq1.theta3,tab.rq1.theta7)
tab.rq1.theta$p.value <- ifelse(tab.rq1.theta$p.value<0.001, "<0.001",
																sprintf("%.3f", round(tab.rq1.theta$p.value,3)))
options(knitr.kable.NA = '-')
tab.rq1.theta %>%
	mutate_all(linebreak, align="l") %>%
	kable(booktabs = T, digits = 3,
				col.names = c("Theta", "Response", "Covariate" ,"Type", "Coefficient", "Std. Err.", "Test", "Value", "\\textit{p}-value"),
				caption = "The same as Table \\ref{tab:rq1tab}, but for the analysis redone with the parameter $\\theta$ respectively set to 3 and 7, instead of 5 (i.e. the sensitivity analysis).",
				align = c("llllrrlrr"), escape = F,
				label = "rq1tab.sens") %>%
	collapse_rows(columns = 1:2, latex_hline ='custom', custom_latex_hline = 1:2,
								valign = "middle")%>%
	kable_styling(font_size = 7)
```

### Using Regularized S-map

```{r regsmap_figure, fig.width=13, fig.height=6, out.width="95%", cache=TRUE, message=FALSE}
plotregsmap <- ((plotregsmap1 + plotregsmap2 + plot_layout(ncol = 1)) | plot_leg_regsmap ) +
  plot_layout(widths = c(3,1))
plotregsmap
```

```{r regsmap_tab, cache=TRUE}
tab.rq1.ELNET0.9 <- cbind(Regularization="ELNET0.9",tab.rq1.ELNET0.9)
tab.rq1.ridge <- cbind(Regularization="Ridge Regr.",tab.rq1.ridge)
tab.rq1.tikhonov <- cbind(Regularization="Tikhonov",tab.rq1.tikhonov)
tab.rq1.regsmap <- rbind(tab.rq1.ELNET0.9,tab.rq1.ridge,tab.rq1.tikhonov)
tab.rq1.regsmap <- tab.rq1.regsmap[c(6:15,26:35,46:55),]

tab.rq1.regsmap$p.value <- ifelse(tab.rq1.regsmap$p.value<0.001, "<0.001",
														 sprintf("%.3f", round(tab.rq1.regsmap$p.value,3)))
options(knitr.kable.NA = '-')
rownames(tab.rq1.regsmap) <- NULL 
tab.rq1.regsmap %>%
	mutate_all(linebreak, align="l") %>%
	kable(booktabs = T, digits = 3,
				col.names = c("Regularization", "Response", "Covariate" ,"Type", "Coefficient", "Std. Err.", "Test", "Value", "\\textit{p}-value"),
				caption = "to be done",
				align = c("llllrrlrr"), escape = F,
				label = "robust") %>%
	collapse_rows(columns = 1:2, latex_hline ='custom', custom_latex_hline = 1:2,
								valign = "middle")%>%
	kable_styling(font_size = 7)
```



## General robustness figures

### Robustness plot 1

```{r mean_int_rmse_plot_robustness, fig.width=13, fig.height=6, out.width="95%", cache=TRUE, message=FALSE}
plot.robust1 + plot.robust2 + plot.robust3 + plot.robust.leg
```

```{r robust_tab, cache=TRUE}
tab.robust$p.value <- ifelse(tab.robust$p.value<0.001, "<0.001",
														 sprintf("%.3f", round(tab.robust$p.value,3)))
options(knitr.kable.NA = '-')
rownames(tab.robust) <- NULL 
tab.robust %>%
	mutate_all(linebreak, align="l") %>%
	kable(booktabs = T, digits = 3,
				col.names = c("Robustness model", "Response", "Covariate" ,"Type", "Coefficient", "Std. Err.", "Test", "Value", "\\textit{p}-value"),
				caption = "Similar to Table \\ref{tab:rq1tab} (i.e., showing the results of the mixed effects model), but for the different robust analyses (see the corresponding sections for more information).",
				align = c("llllrrlrr"), escape = F,
				label = "robust") %>%
	collapse_rows(columns = 1:2, latex_hline ='custom', custom_latex_hline = 1:2,
								valign = "middle")%>%
	kable_styling(font_size = 7)
```

### The effect of variation in the recorded data

```{r mean_int_rmse_cv, fig.width=13, fig.height=4, out.width="95%", cache=TRUE, message=FALSE}
plot1aCV + plot1bCV + plot1cCV 
```

### The effects of different measurement methods

```{r meas_method_plot1, fig.width=13, fig.height=6, out.width="95%", cache=TRUE, message=FALSE}
(boxplot1+boxplot2)/(boxplot3+boxplot_legend)
```

```{r meas_method_plot2, fig.width=13, fig.height=4, out.width="95%", cache=TRUE, message=FALSE}
meas.plot1+meas.plot2+meas.plot3
```

## Forecasting robustness analyses

### Sensitivity analysis for E

```{r fig1_allEs, fig.width=13, fig.height=6.5, out.width="95%", cache=TRUE, message=FALSE}
plot1_allEs
```

```{r e.sens.tab, cache=TRUE}
tab.rq1.allEs <- rbind(tab.rq1.E2[1:10,],tab.rq1.E4[1:10,])
tab.rq1.allEs$p.value <- ifelse(tab.rq1.allEs$p.value<0.001, "<0.001",
														 sprintf("%.3f", round(tab.rq1.allEs$p.value,3)))
options(knitr.kable.NA = '-')
rownames(tab.rq1.allEs) <- NULL 
tab.rq1.allEs %>%
	mutate_all(linebreak, align="l") %>%
	kable(booktabs = T, digits = 3,
				col.names = c("E", "Response", "Covariate" ,"Type", "Coefficient", "Std. Err.", "Test", "Value", "\\textit{p}-value"),
				caption = "caption to be done",
				align = c("llllrrlrr"), escape = F,
				label = "robust") %>%
	collapse_rows(columns = 1:2, latex_hline ='custom', custom_latex_hline = 1:2,
								valign = "middle")%>%
	kable_styling(font_size = 7)
```


```{r num_pred_distr_allEs, fig.width=14, fig.height=7.5, out.width="95%", cache=TRUE, message=FALSE}
mvForecast_best_allEs %>%
	ggplot(aes(count,num_pred, group=treat)) +
	geom_point(aes(fill=Target),size=2.5,col="black", alpha=0.5, shape=21)+
	scale_fill_brewer(palette = "Dark2")+
	facet_grid(E_char~Treat) + 
	standard_theme() +
	labs(x=expression("Number of interactions"~italic(N[T])), y="Number of predictors\nin best model",
			 tag="A")+
	theme(legend.position = "none", legend.box="vertical",
				axis.title = element_text(size=12),
				axis.text = element_text(size=11),
				strip.text = element_text(size=12, hjust = 0, vjust = 1.8, 
																	margin = margin(t = 2, r = 2, b = 0, l = 0, unit = "pt"))) +

mvForecast_best_allEs %>%
	ggplot(aes(num_pred, fill=Target)) +
	geom_bar() +
	scale_fill_brewer(palette = "Dark2")+
	standard_theme()+
	facet_grid(E_char~Treat) + 
	scale_x_continuous(breaks = seq(1,13,by = 2)) +
	labs(x="Number of predictors in best model", y="Count", tag="B")+
	theme(legend.position = "right", 
				legend.text = ggtext::element_markdown(size = 11),
				legend.title = element_text(size=12),
				axis.title = element_text(size=12),
				axis.text = element_text(size=11),
				strip.text = element_text(size=12, hjust = 0, vjust = 1.8, 
																	margin = margin(t = 2, r = 2, b = 0, l = 0, unit = "pt")))
```


### EDM forecasting robustness analyses

```{r forecast_robust_plot, fig.width=13, fig.height=6, out.width="95%", cache=TRUE, message=FALSE, warning=FALSE}
(forecast_boxplot + forecast_corr)/(plot.simplexbest1 + plot.simplexbest2 + plot.simplexbest.leg)
```

```{r forecast_rob_tab, cache=TRUE}
tab.model <- tab.model[c(6:15,21:30),]
tab.model$p.value <- ifelse(tab.model$p.value<0.001, "<0.001",
														 sprintf("%.3f", round(tab.model$p.value,3)))
options(knitr.kable.NA = '-')
rownames(tab.model) <- NULL 
tab.model %>%
	mutate_all(linebreak, align="l") %>%
	kable(booktabs = T, digits = 3,
				col.names = c("Forecast model", "Response", "Covariate" ,"Type", "Coefficient", "Std. Err.", "Test", "Value", "\\textit{p}-value"),
				caption = "Similar to Table \\ref{tab:rq1tab} (i.e., showing the results of the mixed effects model), but for the different EDM forecast models used (see the corresponding sections for more information).",
				align = c("llllrrlrr"), escape = F,
				label = "robust") %>%
	collapse_rows(columns = 1:2, latex_hline ='custom', custom_latex_hline = 1:2,
								valign = "middle")%>%
	kable_styling(font_size = 7)
```


## The analysis redone with different estimation methodologies

### Forecasting using other methods

```{r forecast_ARIMA_RNN, fig.width=13, fig.height=6, out.width="95%", cache=TRUE, message=FALSE, warning=FALSE}
(forecast_boxplot2 + forecast_corr2)/(plot.ARIMARNN1 + plot.ARIMARNN2 + plot.ARIMARNN.leg)
```

```{r forecast_arima_rnn_tab, cache=TRUE}
tab.model2 <- tab.model2[c(6:15,21:30),-2]
tab.model2$p.value <- ifelse(tab.model2$p.value<0.001, "<0.001",
														 sprintf("%.3f", round(tab.model2$p.value,3)))
options(knitr.kable.NA = '-')
rownames(tab.model2) <- NULL 
tab.model2 %>%
	mutate_all(linebreak, align="l") %>%
	kable(booktabs = T, digits = 3,
				col.names = c("Forecast model", "Response", "Covariate" ,"Type", "Coefficient", "Std. Err.", "Test", "Value", "\\textit{p}-value"),
				caption = "Similar to Table \\ref{tab:rq1tab} (i.e., showing the results of the mixed effects model), but for the different forecast models used, i.e. ARIMA and RNN (see the corresponding sections for more information).",
				align = c("llllrrlrr"), escape = F,
				label = "arimarnn") %>%
	collapse_rows(columns = 1:2, latex_hline ='custom', custom_latex_hline = 1:2,
								valign = "middle")%>%
	kable_styling(font_size = 7)
```

### permutation entropy and MARSS estimates

```{r marss_and_pe_plot, fig.width=13, fig.height=6, out.width="95%", cache=TRUE, message=FALSE}
(plot1aPE + plot1bPE + plot1cPE) / (marsplot1 + marsplot2) 
```


